### 2019-09-20 doc/manuscript.tex
Simplfying the proof and uploading the doc sources

\documentclass[a4paper,UKenglish,cleveref, autoref]{lipics-v2019}
%This is a template for producing LIPIcs articles.
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling cleveref support, use "autoref"

\usepackage{url}
\usepackage{algpseudocode}
\usepackage{algorithm}
\algrenewcommand{\algorithmiccomment}[1]{\State /*#1*/}
\algnewcommand\algorithmicto{$\textbf{to}$}
\algrenewtext{For}[3]{\algorithmicfor\ #1 $\gets$ #2 \algorithmicto\ #3 \algorithmicdo}
\newtheorem{hypothesis}[theorem]{Hypothesis}

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

\bibliographystyle{plainurl}% the mandatory bibstyle

\title{Logarithmic Space Verifiers on NP-complete} %TODO Please add

%\titlerunning{P vs NP}%optional, please use if title is longer than one line

\author{Frank Vega}{Joysonic, Uzun Mirkova 5, Belgrade, 11000, Serbia} {vega.frank@gmail.com}{https://orcid.org/0000-0001-8210-4126}{}

\authorrunning{F. Vega}%TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

%\Copyright{John Q. Public and Joan R. Public}%TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\ccsdesc[500]{Theory of computation~Complexity classes}
\ccsdesc[300]{Theory of computation~Problems, reductions and completeness}
%\ccsdesc[100]{Mathematics of computing~Number-theoretic computations}%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

\keywords{complexity classes, completeness, verifier, reduction, polynomial time, logarithmic space}%TODO mandatory; please add comma-separated list of keywords

%\category{}%optional, e.g. invited paper

%\relatedversion{}%optional, e.g. full version hosted on arXiv, HAL, or other respository/website
%\relatedversion{A full version of the paper is available at \url{https://www.academia.edu/39721020/Solution_of_the_P_versus_NP_Problem}.}

%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...

%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

%\acknowledgements{I want to thank \dots}%optional

\nolinenumbers %uncomment to disable line numbering

\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\EventEditors{John Q. Open and Joan R. Access}
%\EventNoEds{2}
%\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
%\EventShortTitle{CVIT 2016}
%\EventAcronym{CVIT}
%\EventYear{2016}
%\EventDate{December 24--27, 2016}
%\EventLocation{Little Whinging, United Kingdom}
%\EventLogo{}
%\SeriesVolume{42}
%\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? A precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. NP is the complexity class of languages defined by polynomial time verifiers M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in P. Another major complexity classes are L and NL. The certificate-based definition of NL is based on logarithmic space Turing machine with an additional special read-once input tape: This is called a logarithmic space verifier. NL is the complexity class of languages defined by logarithmic space verifiers M such that when the input is an element of the language with its certificate, then M outputs 1. To attack the P versus NP problem, the NP-completeness is a useful concept. We demonstrate there is an NP-complete language defined by a logarithmic space verifier M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in L.
\end{abstract}

\section{Introduction}

The $P$ versus $NP$ problem is a major unsolved problem in computer science \cite{CS00}. This is considered by many to be the most important open problem in the field \cite{CS00}. It is one of the seven Millennium Prize Problems selected by the Clay Mathematics Institute to carry a US\$1,000,000 prize for the first correct solution \cite{CS00}. It was essentially mentioned in 1955 from a letter written by John Nash to the United States National Security Agency \cite{AS17}. However, the precise statement of the $P=NP$ problem was introduced in 1971 by Stephen Cook in a seminal paper \cite{CS00}. In 2012, a poll of 151 researchers showed that 126 (83\%) believed the answer to be no, 12 (9\%) believed the answer is yes, 5 (3\%) believed the question may be independent of the currently accepted axioms and therefore impossible to prove or disprove, 8 (5\%) said either do not know or do not care or don't want the answer to be yes nor the problem to be resolved \cite{GA12}. It is fully expected that $P \neq NP$ \cite{Pap03}. Indeed, if $P = NP$ then there are stunning practical consequences \cite{Pap03}. For that reason, $P = NP$ is considered as a very unlikely event \cite{Pap03}. Certainly, $P$ versus $NP$ is one of the greatest open problems in science and a correct solution for this incognita will have a great impact not only in computer science, but for many other fields as well \cite{AS17}. Whether $P = NP$ or not is still a controversial and unsolved problem \cite{AS17}. In this work, we show some results that might be helpful in facing one of the most important open problems in computer science.

\section{Preliminaries}

In 1936, Turing developed his theoretical computational model \cite{MS06}. The deterministic and nondeterministic Turing machines have become in two of the most important definitions related to this theoretical model for computation \cite{MS06}. A deterministic Turing machine has only one next action for each step defined in its program or transition function \cite{MS06}. A nondeterministic Turing machine could contain more than one action defined for each step of its program, where this one is no longer a function, but a relation \cite{MS06}.

Let $\Sigma$ be a finite alphabet with at least two elements, and let $\Sigma^{*}$ be the set of finite strings over $\Sigma$ \cite{AB09}. A Turing machine $M$ has an associated input alphabet $\Sigma$ \cite{AB09}. For each string $w$ in $\Sigma^{*}$ there is a computation associated with $M$ on input $w$ \cite{AB09}. We say that $M$ accepts $w$ if this computation terminates in the accepting state, that is $M(w)=1$ (when $M$ outputs 1 on the input $w$) \cite{AB09}. Note that $M$ fails to accept $w$ either if this computation ends in the rejecting state, that is $M(w)=0$, or if the computation fails to terminate, or the computation ends in the halting state with some output, that is $M(w)=y$ (when $M$ outputs the string $y$ on the input $w$) \cite{AB09}.

Another relevant advance in the last century has been the definition of a complexity class. A language over an alphabet is any set of strings made up of symbols from that alphabet \cite{CLRS01}. A complexity class is a set of problems, which are represented as a language, grouped by measures such as the running time, memory, etc \cite{CLRS01}. The language accepted by a Turing machine $M$, denoted $L(M)$, has an associated alphabet $\Sigma$ and is defined by:
\[L(M) = \{w \in \Sigma^{*}: M(w)=1 \}.\]
We denote by $t_{M}(w)$ the number of steps in the computation of $M$ on input $w$ \cite{AB09}. For $n \in \mathbb{N}$ we denote by $T_{M}(n)$ the worst case run time of $M$; that is:
\[T_{M}(n) = max\{t_{M}(w): w \in \Sigma^{n} \}\]
where $\Sigma^{n}$ is the set of all strings over $\Sigma$ of length $n$ \cite{AB09}. We say that $M$ runs in polynomial time if there is a constant $k$ such that for all $n$, $T_{M}(n) \leq n^{k} + k$ \cite{AB09}. In other words, this means the language $L(M)$ can be decided by the Turing machine $M$ in polynomial time. Therefore, $P$ is the complexity class of languages that can be decided by deterministic Turing machines in polynomial time \cite{CLRS01}. A verifier for a language $L_{1}$ is a deterministic Turing machine $M$, where:
\[L_{1} = \{w: M(w, c) = 1 \textit{ for some string } c\}.\]
We measure the time of a verifier only in terms of the length of $w$, so a polynomial time verifier runs in polynomial time in the length of $w$ \cite{AB09}. A verifier uses additional information, represented by the symbol $c$, to verify that a string $w$ is a member of $L_{1}$. This information is called certificate. $NP$ is the complexity class of languages defined by polynomial time verifiers \cite{Pap03}.

\begin{lemma}
\label{verifier}
Given a language $L_{1} \in P$, a language $L_{2}$ is in $NP$ if there is a deterministic Turing machine $M$, where:
\[L_{2} = \{w: M(w, c) = y \textit{ for some string } c \textit{ such that } y \in L_{1}\}\]
and $M$ runs in polynomial time in the length of $w$. In this way, $NP$ is the complexity class of languages defined by polynomial time verifiers $M$ such that when the input is an element of the language with its certificate, then $M$ outputs a string which belongs to a single language in $P$.
\end{lemma}

\begin{proof}
If $L_{1}$ can be decided by the Turing machine $M'$ in polynomial time, then the deterministic Turing machine $M''(w, c) = M'(M(w, c))$ will output 1 when $w \in L_{2}$. Consequently, $M''$ is a polynomial time verifier of $L_{2}$ and thus, $L_{2}$ is in $NP$.
\end{proof}

\section{Hypothesis}

A function $f : \Sigma^{*} \rightarrow \Sigma^{*}$ is a polynomial time computable function if some deterministic Turing machine $M$, on every input $w$, halts in polynomial time with just $f(w)$ on its tape \cite{MS06}. Let $\{0, 1\}^{*}$ be the infinite set of binary strings, we say that a language $L_{1} \subseteq \{0, 1\}^{*}$ is polynomial time reducible to a language $L_{2} \subseteq \{0, 1\}^{*}$, written $L_{1} \leq_{p} L_{2}$, if there is a polynomial time computable function $f : \{0, 1\}^{*} \rightarrow \{0, 1\}^{*}$ such that for all $x \in \{0, 1\}^{*}$:
\[x \in L_{1} \textit{ if and only if } f(x) \in L_{2}.\]
An important complexity class is $\textit{NP--complete}$ \cite{OG10}. A language $L_{1} \subseteq \{0, 1\}^{*}$ is $\textit{NP--complete}$ if:

\begin{itemize}
\item $L_{1} \in NP$, and
\item $L' \leq_{p} L_{1}$ for every $L' \in NP$.
\end{itemize}

If $L_{1}$ is a language such that $L' \leq_{p} L_{1}$ for some $L' \in \textit{NP--complete}$, then $L_{1}$ is $\textit{NP--hard}$ \cite{CLRS01}. Moreover, if $L_{1} \in NP$, then $L_{1} \in \textit{NP--complete}$ \cite{CLRS01}. A principal $\textit{NP--complete}$ problem is $SAT$ \cite{GJ79}. An instance of $SAT$ is a Boolean formula $\phi$ which is composed of:

\begin{enumerate}
\item Boolean variables: $x_{1}, x_{2},\ldots, x_{n}$;
\item Boolean connectives: Any Boolean function with one or two inputs and one output, such as $\wedge$(AND), $\vee$(OR), $\rightharpoondown$(NOT), $\Rightarrow$(implication), $\Leftrightarrow$(if and only if);
\item and parentheses.
\end{enumerate}

A truth assignment for a Boolean formula $\phi$ is a set of values for the variables in $\phi$. A satisfying truth assignment is a truth assignment that causes $\phi$ to be evaluated as true. A formula with a satisfying truth assignment is a satisfiable formula. The problem $SAT$ asks whether a given Boolean formula is satisfiable \cite{GJ79}. We define a $CNF$ Boolean formula using the following terms:

A literal in a Boolean formula is an occurrence of a variable or its negation \cite{CLRS01}. A Boolean formula is in conjunctive normal form, or $CNF$, if it is expressed as an AND of clauses, each of which is the OR of one or more literals \cite{CLRS01}. A Boolean formula is in 3-conjunctive normal form or $3CNF$, if each clause has exactly three distinct literals \cite{CLRS01}.

For example, the Boolean formula:
\[(x_{1} \vee \rightharpoondown x_{1} \vee \rightharpoondown x_{2}) \wedge (x_{3} \vee x_{2} \vee x_{4}) \wedge (\rightharpoondown x_{1} \vee \rightharpoondown x_{3} \vee \rightharpoondown x_{4})\]
is in $3CNF$. The first of its three clauses is $(x_{1} \vee \rightharpoondown x_{1} \vee \rightharpoondown x_{2})$, which contains the three literals $x_{1}$, $\rightharpoondown x_{1}$, and $\rightharpoondown x_{2}$. Another relevant $\textit{NP--complete}$ language is $3CNF$ satisfiability, or $3SAT$ \cite{CLRS01}. In $3SAT$, it is asked whether a given Boolean formula $\phi$ in $3CNF$ is satisfiable.

A logarithmic space Turing machine has a read-only input tape, a write-only output tape, and read/write work tapes \cite{MS06}. The work tapes may contain at most $O(\log n)$ symbols \cite{MS06}. In computational complexity theory, $L$ is the complexity class containing those decision problems that can be decided by a deterministic logarithmic space Turing machine \cite{Pap03}. $NL$ is the complexity class containing the decision problems that can be decided by a nondeterministic logarithmic space Turing machine \cite{Pap03}.

A logarithmic space transducer is a Turing machine with a read-only input tape, a write-only output tape, and read/write work tapes \cite{MS06}. The work tapes must contain at most $O(\log n)$ symbols \cite{MS06}. A logarithmic space transducer $M$ computes a function $f : \Sigma^{*} \rightarrow \Sigma^{*}$, where $f(w)$ is the string remaining on the output tape after $M$ halts when it is started with $w$ on its input tape \cite{MS06}. We call $f$ a logarithmic space computable function \cite{MS06}. We say that a language $L_{1} \subseteq \{0, 1\}^{*}$ is logarithmic space reducible to a language $L_{2} \subseteq \{0, 1\}^{*}$, written $L_{1} \leq_{l} L_{2}$, if there exists a logarithmic space computable function $f : \{0, 1\}^{*} \rightarrow \{0, 1\}^{*}$ such that for all $x \in \{0, 1\}^{*}$,
\[x \in L_{1} \textit{ if and only if } f(x) \in L_{2}.\]
The logarithmic space reduction is frequently used for $L$ and $NL$ \cite{Pap03}. A Boolean formula is in 2-conjunctive normal form, or $2CNF$, if it is in $CNF$ and each clause has exactly two distinct literals. There is a problem called $2SAT$, where we asked whether a given Boolean formula $\phi$ in $2CNF$ is satisfiable. $2SAT$ is complete for $NL$ \cite{Pap03}. Another special case is the class of problems where each clause contains $XOR$ (i.e. exclusive or) rather than (plain) $OR$ operators. This is in $P$, since an $\textit{XOR SAT}$ formula can also be viewed as a system of linear equations mod $2$, and can be solved in cubic time by Gaussian elimination \cite{MM11}. We denote the $XOR$ function as $\oplus$. The $\textit{XOR 2SAT}$ problem will be equivalent to $\textit{XOR SAT}$, but the clauses in the formula have exactly two distinct literals. $\textit{XOR 2SAT}$ is in $L$ \cite{AR00}, \cite{RM08}.

We can give a certificate-based definition for $NL$ \cite{AB09}. The certificate-based definition of $NL$ assumes that a logarithmic space Turing machine has another separated read-only tape \cite{AB09}. On each step of the machine the machine's head on that tape can either stay in place or move to the right \cite{AB09}. In particular, it cannot reread any bit to the left of where the head currently is \cite{AB09}. For that reason this kind of special tape is called ``read once" \cite{AB09}.

\begin{definition}
A language $L_{1}$ is in $NL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$,
\[x \in L_{1} \Leftrightarrow \exists u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = 1 \]
where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function \cite{AB09}. $M$ is called a logarithmic space verifier \cite{AB09}.
\end{definition}

We state the following Hypothesis:

\begin{hypothesis}
\label{hypothesis}
Given a language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
\[L_{2} = \{w: M(w, u) = y \textit{ for some string } u \textit{ such that } y \in L_{1}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$. In this way, there is an $\textit{NP--complete}$ language defined by a logarithmic space verifier $M$ such that when the input is an element of the language with its certificate, then $M$ outputs a string which belongs to a single language in $L$.
\end{hypothesis}

\section{Results}

We show a previous known $\textit{NP--complete}$ problem:

\begin{definition}
$\textbf{MONOTONE NAE 3SAT}$

INSTANCE: A Boolean formula $\phi$ in $3CNF$ such that each clause has no negation variables.

QUESTION: Is there a truth assignment for $\phi$ such that each clause has at least one true literal and at least one false literal?

REMARKS: This is equivalent to the special case of the $\textit{NP--complete}$ problem known as $\textit{SET SPLITTING}$ when the sets in the input have exactly three elements and therefore, $\textit{MONOTONE NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}.
\end{definition}

We define a new problem:

\begin{definition}
$\textbf{MINIMUM EXCLUSIVE-OR 2-SATISFIABILITY}$

INSTANCE: A positive integer $K$ and a Boolean formula $\phi$ that is an instance of $\textit{XOR 2SAT}$ such that each clause has no negation variables.

QUESTION: Is there a truth assignment in $\phi$ such that exactly $K$ clauses are unsatisfiable?

REMARKS: We denote this problem as $MIN\oplus2SAT$.
\end{definition}

\begin{theorem}
\label{completeness}
$MIN\oplus2SAT \in \textit{NP--complete}$.
\end{theorem}

\begin{proof}
It is trivial to see $MIN\oplus2SAT \in NP$ \cite{Pap03}. Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses such that each clause has no negation variables, we create three new variables $a_{c_{i}}$, $b_{c_{i}}$ and $d_{c_{i}}$ for each clause $c_{i} = (x \vee y \vee z)$ in $\phi$, where $x$, $y$ and $z$ are positive literals, in the following formula:
\[P_{i} = (a_{c_{i}} \oplus b_{c_{i}}) \wedge (b_{c_{i}} \oplus d_{c_{i}}) \wedge (a_{c_{i}} \oplus d_{c_{i}}) \wedge (x \oplus a_{c_{i}}) \wedge (y \oplus b_{c_{i}}) \wedge (z \oplus d_{c_{i}}).\]
We can see $P_{i}$ has exactly one unsatisfiable clause for some truth assignment if and only if at least one member of $\{x,y,z\}$ is true and at least one member of $\{x,y,z\}$ is false for the same truth assignment. Hence, we can create the Boolean formula $\psi$ as the conjunction of the $P_{i}$ formulas for every clause $c_{i}$ in $\phi$, such that $\psi = P_{1} \wedge \ldots \wedge P_{m}$. Finally, we obtain that
\[\phi \in \textit{MONOTONE NAE 3SAT} \textit{ if and only if } (\psi, m) \in MIN\oplus2SAT.\]
Consequently, we prove $\textit{MONOTONE NAE 3SAT} \leq_{p} MIN\oplus2SAT$ where we already know the language $\textit{MONOTONE NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}. To sum up, we show $MIN\oplus2SAT \in \textit{NP--hard}$ and $MIN\oplus2SAT \in NP$ and thus, $MIN\oplus2SAT \in \textit{NP--complete}$.
\end{proof}

\begin{theorem}
\label{proof}
There is a deterministic Turing machine $M$, where:
\[MIN\oplus2SAT = \{w: M(w, u) = y \textit{ for some string } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
\end{theorem}

\begin{proof}
Given a valid instance $(\psi, K)$ for $MIN\oplus2SAT$ when $\psi$ has $m$ clauses, we can create a certificate array $A$ which contains $K$ different natural numbers in ascending order which represents the indexes of the clauses in $\psi$ that we are going to remove from the instance. We read at once the elements of the array $A$ and we reject whether this is not a valid certificate: That is when the numbers are not sorted in ascending order, or the array $A$ does not contain exactly $K$ elements, or the array $A$ contains a number that is not between $1$ and $m$. While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MIN\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$. Therefore, we obtain that:
\[(\psi, K) \in MIN\oplus2SAT \textit{ if and only if } \phi \in \textit{XOR 2SAT}.\]
Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right. Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is a valid certificate and also remove the $K$ different clauses from the Boolean formula $\psi$ when we write the final clauses to the output. This logarithmic space verification will be the Algorithm \ref{2-algorithm}. We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = undefined$. In addition, we reject immediately when the following comparisons
\[A[i] \leq max \vee A[i] < 1 \vee A[i] > m\]
hold at least into one single binary digit. Note, in the loop $j$ from $min$ to $max - 1$, we do not output any clause when $max - 1 < min$.

\begin{algorithm}
\caption{Logarithmic space verifier}\label{2-algorithm}
\begin{algorithmic}[1]
\Comment{A valid instance for $MIN\oplus2SAT$ with its certificate}
\Procedure{$\textit{VERIFIER}$}{$(\psi, K), A$}
\Comment{Initialize minimum and maximum values}
\State $min \gets 1$
\State $max \gets 0$
\Comment{Iterate for the elements of the certificate array $A$}
\For{$i$}{$1$}{$K + 1$}
\If{$i = K+1$}
\Comment{There exists a $K+1$ element in the array}
\If{$A[i] \neq undefined$}
\Comment{Reject the certificate}
\State \textbf{return} $0$
\EndIf
\Comment{$m$ is the number of clauses in $\psi$}
\State $max \gets m + 1$
\ElsIf{$A[i] = undefined \vee A[i] \leq max \vee A[i] < 1 \vee A[i] > m$}
\Comment{Reject the certificate}
\State \textbf{return} $0$
\Else
\State $max \gets A[i]$
\EndIf
\Comment{Iterate for the clauses of the Boolean formula $\psi$}
\For{$j$}{$min$}{$max - 1$}
\Comment{Output the indexed $j$ clause in $\psi$}
\State \textbf{output} $``\wedge c_{j}"$
\EndFor
\State $min \gets max + 1$
\EndFor
\EndProcedure
\end{algorithmic}
\end{algorithm}
\end{proof}

\begin{theorem}
The Hypothesis \ref{hypothesis} is true.
\end{theorem}

\begin{proof}
This is a consequence of Theorems \ref{completeness} and \ref{proof}.
\end{proof}

\section{Materials and Methods}

This work is implemented into a GitHub Project programmed in Scala \cite{FV19}. In this GitHub Project, we use the Assertion on the properties of the instances of each problem and the Unit Test for checking the correctness of every reduction \cite{FV19}. We need to install JDK 8 in order to test the Scala Project \cite{OD16}. In addition, we need to install SBT to run the unit test (we could run the unit test with the $\textbf{sbt test}$ command) \cite{OD16}.

\bibliography{manuscript}

\end{document}

### 2019-09-20 src/main/scala/frank/problems/Instance.scala

@@ -34,62 +34,15 @@ case class MinXor2Sat(K: Int, formula: Formula) extends Instance{
 
 }
 
+
 /**
-  * A positive integer K, a “universe" set U of natural numbers and a family
-  * of n sets Si is a subset of U with the property that every element in U appears at most twice in the list
-  * S1, . . . , Sn.
-  * Question: Is it the case there is a subfamily S1 , . . . , Sm with m <= n after removing K
-  * different numbers in U from the whole list S1, . . . , Sn, such that Si intersect Sj = empty set
-  * for 1 <= i != j <= m and S1 union . . . union Sm = U where U is equal to the set U without the removed K different numbers?
+  * An instance of XOR 2SAT such that each clause has no negation variables.
+  * Question: Is there a satisfying truth assignment for the Boolean formula?
   * This problem is in NP-complete.
   */
-case class KExactCover2(K: Int, U: Set[Int], family: List[Set[Int]]) extends Instance{
-  assert(K > 0, "K should be a positive integer")
-  assert(K <= U.size, "K should be at most all the elements in the universe")
-  assert(family.forall(s => s.intersect(U) == s), "Si should be a subset of U")
-  assert(family.flatten.toSet == U, "U should be the universe set")
-  assert((family.map(_.toList).flatten.groupBy(identity).collect { case (x, List(_,_,_,_*)) => x }).size == 0, "Should every element in U appears at most twice in the list")
-
+case class MonotoneXor2Sat(formula: Formula) extends Instance{
+  assert(formula.isExactlyKSat(2), "Should be in 2CNF")
+  assert(formula.isMonotoneSat, "Should be Monotone")
 }
 
-
-/**
-  * A positive integer m, a family of disjoint sets U1, . . . ,Uk from a “universe" set
-  * U1 union . . . union Uk = U and a collection of n pairs Ti = (x, Si) such that x is a positive integer
-  * and Si is a subset of U is a set with the property that every element in U appears at most twice in the
-  * list S1, . . . , Sn from the pairs T1, . . . , Tn. For every pair Tj = (x, Sj), the positive integer x
-  * appears exactly once in a single pair Ti = (x, Si) for i <= m. We assume the elements in the
-  * set Si of each pair Ti appear sorted in the input with ascending order. Moreover, a set Si
[…]

### 2019-09-20 src/main/scala/frank/problems/Reduction.scala

@@ -11,7 +11,7 @@ trait Reduction[U<:Instance, V<:Instance, C] {
 }
 
 /**
-  * Theorem 9 in paper https://www.preprints.org/manuscript/201908.0037/v1
+  * Theorem 6 in paper https://www.preprints.org/manuscript/201908.0037/v1
   */
 object ReductionKnownNPComplete extends Reduction[MonotoneNaeSat, MinXor2Sat, Any]{
   override def reduction(input: MonotoneNaeSat, certificate: Option[Any] = None): MinXor2Sat = {
@@ -31,87 +31,33 @@ object ReductionKnownNPComplete extends Reduction[MonotoneNaeSat, MinXor2Sat, An
 }
 
 /**
-  * Theorem 10 in paper https://www.preprints.org/manuscript/201908.0037/v1
+  * Theorem 7 in paper https://www.preprints.org/manuscript/201908.0037/v1
   */
-object ReductionNewNPComplete extends Reduction[MinXor2Sat, KExactCover2, Any]{
-  override def reduction(input: MinXor2Sat, certificate: Option[Any] = None): KExactCover2 = {
-
-    val family: Seq[List[(Int, Int)]] = for {(clause, index) <- input.formula.clauses.zipWithIndex} yield {
-      List((clause.literals.zipWithIndex.find(_._2 == 0).get._1, index + 1),
-        (clause.literals.zipWithIndex.find(_._2 == 1).get._1, index + 1))
-    }
-    KExactCover2(input.K, (1 to input.formula.clauseCount).toSet, family.flatten.groupBy(_._1).map(g => g._2.map(_._2).toSet).toList)
-  }
-}
-
-/**
-  * Theorem 11 in paper https://www.preprints.org/manuscript/201908.0037/v1
-  */
-object ReductionInLogarithmicSpace extends Reduction[ExactSeparateCover2, ExactCover2, Any]{
-  override def reduction(input: ExactSeparateCover2, certificate: Option[Any] = None): ExactCover2 = {
-    // Output the “universe" set U
-    val universe: List[Int] = input.universe.flatten
-    if (universe.size != universe.toSet.size) throw new IllegalArgumentException("The input is not a valid instance")
-    // Output the family of sets Si
-    val family: IndexedSeq[Set[Int]] = for (i <- 1 to input.m) yield {
-      val pairI = input.pairs.zipWithIndex.find(z => z._2 == i - 1).get._1
-      var list = pairI._2
[…]

### 2019-09-20 src/test/scala/frank/problems/Common.scala

@@ -15,21 +15,9 @@ trait Common extends Matchers {
     }
   }
 
-  def composeReduceSat(reducer: Reduction[MonotoneNaeSat, MinXor2Sat, Any], composer: Reduction[MinXor2Sat, KExactCover2, Any], input: Formula) = {
-    composer.reduction(reducer.reduction(MonotoneNaeSat(input))) should matchPattern {
-      case output:KExactCover2 =>
-    }
-  }
-
-  def reduceLogarithmic(reducer: Reduction[ExactSeparateCover2, ExactCover2, Any], input: ExactSeparateCover2) = {
-    reducer.reduction(input) should matchPattern {
-      case output:ExactCover2 =>
-    }
-  }
-
-  def verifySat(logarithmic: Reduction[ExactSeparateCover2, ExactCover2, Any], verifier: Reduction[KExactCover2, ExactSeparateCover2, Array[Int]], reducer: Reduction[MonotoneNaeSat, MinXor2Sat, Any], composer: Reduction[MinXor2Sat, KExactCover2, Any], input: Formula, certificate: Array[Int]) = {
-    logarithmic.reduction(verifier.reduction(composer.reduction(reducer.reduction(MonotoneNaeSat(input))), Some(certificate))) should matchPattern {
-      case output:ExactCover2 =>
+  def verifySat(verifier: Reduction[MinXor2Sat, MonotoneXor2Sat, Array[Int]], reducer: Reduction[MonotoneNaeSat, MinXor2Sat, Any], input: Formula, certificate: Array[Int]) = {
+    verifier.reduction(reducer.reduction(MonotoneNaeSat(input)), Some(certificate)) should matchPattern {
+      case output:MonotoneXor2Sat =>
     }
   }
 }

### 2019-09-20 src/test/scala/frank/problems/ReductionLogarithmic$Test.scala

@@ -1,24 +1,0 @@
-package frank.problems
-
-import org.scalatest.FlatSpec
-
-/**
-  * Created by frank on 8/7/2019.
-  */
-class ReductionLogarithmic$Test extends FlatSpec with Common {
-  private val reducer = ReductionInLogarithmicSpace
-
-  behavior of "ReductionLogarithmic$"
-
-  it should "reduce in logarithmic space" in {
-
-    reduceLogarithmic(reducer, ExactSeparateCover2(m = 1, universe = List(Set(1)), pairs = List((1, List(1)))))
-    reduceLogarithmic(reducer, ExactSeparateCover2(m = 2, universe = List(Set(2, 3), Set(1), Set(4, 5)), pairs = List((1, List(1, 2)), (2, List(2, 3, 4)), (2, List(5)), (1, List(3)))))
-    reduceLogarithmic(reducer, ExactSeparateCover2(m = 3, universe = List(Set(2, 3), Set(1), Set(4, 5)), pairs = List((1, List(1, 2)), (2, List(2, 3, 4)), (3, List(5)), (1, List(3, 4, 5)))))
-    reduceLogarithmic(reducer, ExactSeparateCover2(m = 2, universe = List(Set(2, 3), Set(1), Set(4, 5)), pairs = List((1, List(1, 2)), (2, List(2, 3, 4)), (2, List(5)), (1, List(3)), (1, List(4, 5)))))
-
-
-  }
-
-
-}

### 2019-09-20 src/test/scala/frank/problems/ReductionSat$Test.scala

@@ -7,9 +7,7 @@ import frank.sat._
   */
 class ReductionSat$Test extends FlatSpec with Common {
   private val reducer = ReductionKnownNPComplete
-  private val composer = ReductionNewNPComplete
   private val verifier = ReductionWithVerification
-  private val logarithmic = ReductionInLogarithmicSpace
   behavior of "ReductionSat$"
 
   val formula1 = Formula(Clause(1, 2, 3))
@@ -26,21 +24,11 @@ class ReductionSat$Test extends FlatSpec with Common {
 
   }
 
-  it should "compose reduce 3CNF formulas" in {
-
-    composeReduceSat(reducer, composer, formula1)
-    composeReduceSat(reducer, composer, formula2)
-    composeReduceSat(reducer, composer, formula3)
-    composeReduceSat(reducer, composer, formula4)
-
-
-  }
-
   it should "verify 3CNF formulas" in {
 
     val array = Array(4, 7, 10)
-    verifySat(logarithmic, verifier, reducer, composer, formula3, array)
-    verifySat(logarithmic, verifier, reducer, composer, formula4, array)
+    verifySat(verifier, reducer, formula3, array)
+    verifySat(verifier, reducer, formula4, array)
 
 
   }

### 2019-09-20 doc/manuscript.tex
Fixed flaw in doc proof

@@
 
-QUESTION: Is there a truth assignment in $\phi$ such that exactly $K$ clauses are unsatisfiable?
+QUESTION: Is there a truth assignment in $\phi$ such that at most $K$ clauses are unsatisfiable?
 
@@
 \[P_{i} = (a_{c_{i}} \oplus b_{c_{i}}) \wedge (b_{c_{i}} \oplus d_{c_{i}}) \wedge (a_{c_{i}} \oplus d_{c_{i}}) \wedge (x \oplus a_{c_{i}}) \wedge (y \oplus b_{c_{i}}) \wedge (z \oplus d_{c_{i}}).\]
-We can see $P_{i}$ has exactly one unsatisfiable clause for some truth assignment if and only if at least one member of $\{x,y,z\}$ is true and at least one member of $\{x,y,z\}$ is false for the same truth assignment.
+We can see $P_{i}$ has at most one unsatisfiable clause for some truth assignment if and only if at least one member of $\{x,y,z\}$ is true and at least one member of $\{x,y,z\}$ is false for the same truth assignment.
 Hence, we can create the Boolean formula $\psi$ as the conjunction of the $P_{i}$ formulas for every clause $c_{i}$ in $\phi$, such that $\psi = P_{1} \wedge \ldots \wedge P_{m}$.

### 2019-10-26 doc/manuscript.tex
Fixed a content doc detail
Updated content doc

@@
 We demonstrate there is an NP-complete language defined by a logarithmic space verifier M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in L.
+In this way, there is an NP-complete language which complies with an equivalent certificate-based definition of NL, and therefore P = NP.
 \end{abstract}
@@
 \section{Introduction}
+
+In previous years there has been great interest in the verification or checking of computations \cite{LIP90}.
+Interactive proofs introduced by Goldwasser, Micali and Rackoff and Babi can be viewed as a model of the verification process \cite{LIP90}.
+Dwork and Stockmeyer and Condon have studied interactive proofs where the verifier is a space bounded computation instead of the original model where the verifer is a time bounded computation \cite{LIP90}.
+In addition, Blum and Kannan has studied another model where the goal is to check a computation based solely on the final answer \cite{LIP90}.
+Besides, a probabilistic logarithmic space verifiers have been shown for $NP$ such that these are based on a technique of Lipton \cite{LIP90}.
+In this work, we show some results about the logarithmic space verifiers applied to the class $NP$ which solve one of the most important open problems in computer science, that is $P$ versus $NP$.
+
+\section{Motivation}
 
@@
 Whether $P = NP$ or not is still a controversial and unsolved problem \cite{AS17}.
-In this work, we show some results that might be helpful in facing one of the most important open problems in computer science.
 
@@
 
+\begin{theorem}
+\label{argument}
+If the Hypothesis \ref{hypothesis} is true, then there is an $\textit{NP--complete}$ language which complies with an equivalent certificate-based definition of $NL$, and therefore $P = NP$.
+\end{theorem}
+
+\begin{proof}
+From the early days of automata and complexity  theory,  two  different  models  of  Turing  machines  are  considered, the offline and online machines \cite{KU15}.
+Each model is deterministic and has a read-only input tape and some infinite work tapes \cite{KU15}.
+The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left \cite{KU15}.
+In the terminology of the (generalized) Turing machine models are called two-way and one-way deterministic Turing machines respectively \cite{KU15}.
+
+The languages accepted by one-way deterministic logarithmic space Turing machine coincide with the class $L$ \cite{KU15}.
+The reason is because the classes of languages accepted by restricted and strongly $f$ space-bounded one-way deterministic Turing machine coincide, for any space constructible function $f$ on deterministic Turing machines \cite{KU15}.
+A function $f$ is space constructible if there exists a Turing machine $M$ which, given a string $1^{n}$ consisting of $n$ ones, outputs the binary (or unary) representation of $f(n)$, while using only $O(f(n))$ space \cite{KU15}.
+For the restricted and strongly mode, the space is bounded by the condition that,  given a function $f$, the Turing machine uses at most $f(i)$ cells of the work tapes in any configuration with input head at position $i$, occurring in any accepting computation \cite{KU15}.
+In this way, a logarithmic space computable function $f$ complies with the definition above \cite{MS06}.
+
+In this way, we can accept the elements of the language $L_{1} \in L$ by a one-way deterministic logarithmic space Turing machine $M'$ \cite{KU15}.
+In addition, we can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis} by a nondeterministic logarithmic space Turing machine $N$, such that $N(w) = y$ since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$ \cite{Pap03}.
+Certainly, we can simulate the reading of one symbol from the string $u$ into the read-once tape just nondeterministically generating the same symbol in the work tapes using a logarithmic space \cite{Pap03}.
+At the same time, there is a nondeterministic logarithmic space Turing machine $M''(w) = M'(N(w))$ which will output 1 when $w \in L_{2}$.
+Consequently, $M''$ is a nondeterministic logarithmic space Turing machine which accepts the language $L_{2}$.
+
+The reason is because we can simulate the output string of $N(w)$ within a read-once output tape and thus, we can compute in logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}.
+Certainly, we do not need to reset the computation of $N(w)$ for the reading at once of a symbol in the output string of $N(w)$ by the one-way deterministic logarithmic space Turing machine $M'$.
+Therefore, $L_{2}$ is in $NL$ and thus, $L_{2} \in P$ due to $NL \subseteq P$ \cite{Pap03}.
+If any single $\textit{NP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{CLRS01}.
+Since $L_{2} \in P$ and $L_{2} \in \textit{NP--complete}$, then we obtain the complexity class $P$ is equal to $NP$.
+\end{proof}
+
 \section{Results}
@@
 While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MIN\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$.
-Therefore, we obtain that:
+Therefore, we obtain the array $A$ is also a valid certificate when:
 \[(\psi, K) \in MIN\oplus2SAT \textit{ if and only if } \phi \in \textit{XOR 2SAT}.\]
@@
 \begin{theorem}
+\label{result}
 The Hypothesis \ref{hypothesis} is true.
@@
 
+\begin{theorem}
+$P = NP$.
+\end{theorem}
+
+\begin{proof}
+This is a direct consequence of Theorems \ref{argument} and \ref{result}.
+\end{proof}
+
 \section{Materials and Methods}
 
-This work is implemented into a GitHub Project programmed in Scala \cite{FV19}.
-In this GitHub Project, we use the Assertion on the properties of the instances of each problem and the Unit Test for checking the correctness of every reduction \cite{FV19}.
+This work is implemented into a Project programmed in Scala \cite{FV19}.
+In this Project, we use the Assertion on the properties of the instances of each problem and the Unit Test for checking the correctness of every reduction \cite{FV19}.
 We need to install JDK 8 in order to test the Scala Project \cite{OD16}.
 In addition, we need to install SBT to run the unit test (we could run the unit test with the $\textbf{sbt test}$ command) \cite{OD16}.
+
+\section{Conclusion}
+
+No one has been able to find a polynomial time algorithm for any of more than $300$ important known $\textit{NP--complete}$ problems \cite{GJ79}.
+A proof of $P = NP$ will have stunning practical consequences, because it leads to efficient methods for solving some of the important problems in $NP$ \cite{CS00}.
+The consequences, both positive and negative, arise since various $\textit{NP--complete}$ problems are fundamental in many fields \cite{CS00}.
+This result explicitly concludes supporting the existence of a practical solution for the $\textit{NP--complete}$ problems with a $P = NP$ proof that is actually nonconstructive.
+All the following consequences are assuming that we have a practical solution for the $\textit{NP--complete}$ problems where such existence was proven with our result:
+
+Cryptography, for example, relies on certain problems being difficult.
+A constructive and efficient solution to an $\textit{NP--complete}$ problem such as $3SAT$ will break most existing cryptosystems including: Public-key cryptography \cite{HW97}, symmetric ciphers \cite{MM00} and one-way functions used in cryptographic hashing \cite{DKV07}.
+These would need to be modified or replaced by information-theoretically secure solutions not inherently based on $\textit{P--NP}$ equivalence.
+
+There are enormous positive consequences that will follow from rendering tractable many currently mathematically intractable problems.
+For instance, many problems in operations research are $\textit{NP--complete}$, such as some types of integer programming and the traveling salesman problem \cite{GJ79}.
+Efficient solutions to these problems have enormous implications for logistics \cite{CS00}.
+Many other important problems, such as some problems in protein structure prediction, are also $\textit{NP--complete}$, so this will spur considerable advances in biology \cite{BL98}.
+
+Moreover, Learning becomes easy by using the principle of Occam's razor: We simply find the smallest program consistent with the data \cite{LF09}.
+Near perfect vision recognition, language comprehension and translation and all other learning tasks become trivial \cite{LF09}.
+We will also have much better predictions of weather and earthquakes and other natural phenomenon \cite{LF09}.
+
+But such changes may pale in significance compared to the revolution an efficient method for solving $\textit{NP--complete}$ problems will cause in mathematics itself.
+Research mathematicians spend their careers trying to prove theorems, and some proofs have taken decades or even centuries to find after problems have been stated.
+For instance, Fermat's Last Theorem took over three centuries to prove.
+A method that is guaranteed to find proofs to theorems, should one exist of a $``$reasonable$"$ size, would essentially end this struggle \cite{CS00}.
 

### 2019-10-26 doc/manuscript.tex
Improved content doc

@@
 We demonstrate there is an NP-complete language defined by a logarithmic space verifier M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in L.
-In this way, there is an NP-complete language which complies with an equivalent certificate-based definition of NL, and therefore P = NP.
+In this way, there is an NP-complete language which complies with the definition of NL, and therefore P = NP.
 \end{abstract}
@@
 \label{argument}
-If the Hypothesis \ref{hypothesis} is true, then there is an $\textit{NP--complete}$ language which complies with an equivalent certificate-based definition of $NL$, and therefore $P = NP$.
+If the Hypothesis \ref{hypothesis} is true, then there is an $\textit{NP--complete}$ language which complies with the definition of $NL$, and therefore $P = NP$.
 \end{theorem}
@@
 The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left \cite{KU15}.
-In the terminology of the (generalized) Turing machine models are called two-way and one-way deterministic Turing machines respectively \cite{KU15}.
+In the terminology of the (generalized) Turing machine models are called deterministic two-way and one-way Turing machines respectively \cite{KU15}.
 
-The languages accepted by one-way deterministic logarithmic space Turing machine coincide with the class $L$ \cite{KU15}.
-The reason is because the classes of languages accepted by restricted and strongly $f$ space-bounded one-way deterministic Turing machine coincide, for any space constructible function $f$ on deterministic Turing machines \cite{KU15}.
+The languages accepted by a deterministic one-way logarithmic space Turing machine coincide with the class $L$ \cite{KU15}.
+The reason is because every function $f$ that is space constructible by a deterministic two-way Turing machine, is space constructible by a strongly $f$ space-bounded deterministic one-way Turing machine as well \cite{KU15}.
 A function $f$ is space constructible if there exists a Turing machine $M$ which, given a string $1^{n}$ consisting of $n$ ones, outputs the binary (or unary) representation of $f(n)$, while using only $O(f(n))$ space \cite{KU15}.
-For the restricted and strongly mode, the space is bounded by the condition that,  given a function $f$, the Turing machine uses at most $f(i)$ cells of the work tapes in any configuration with input head at position $i$, occurring in any accepting computation \cite{KU15}.
+For the strongly mode, the space is bounded by the condition that,  given a function $f$, the Turing machine uses at most $f(i)$ cells of the work tapes in any configuration with input head at position $i$, occurring in any accepting computation \cite{KU15}.
 In this way, a logarithmic space computable function $f$ complies with the definition above \cite{MS06}.
 
-In this way, we can accept the elements of the language $L_{1} \in L$ by a one-way deterministic logarithmic space Turing machine $M'$ \cite{KU15}.
+In this way, we can accept the elements of the language $L_{1} \in L$ by a deterministic one-way logarithmic space Turing machine $M'$ \cite{KU15}.
 In addition, we can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis} by a nondeterministic logarithmic space Turing machine $N$, such that $N(w) = y$ since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$ \cite{Pap03}.
@@
 The reason is because we can simulate the output string of $N(w)$ within a read-once output tape and thus, we can compute in logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}.
-Certainly, we do not need to reset the computation of $N(w)$ for the reading at once of a symbol in the output string of $N(w)$ by the one-way deterministic logarithmic space Turing machine $M'$.
+Certainly, we do not need to reset the computation of $N(w)$ for the reading at once of a symbol in the output string of $N(w)$ by the deterministic one-way logarithmic space Turing machine $M'$.
 Therefore, $L_{2}$ is in $NL$ and thus, $L_{2} \in P$ due to $NL \subseteq P$ \cite{Pap03}.

### 2019-10-31 doc/manuscript.tex
Improved the content doc
Fixed the proof

--- 2019-09-20 doc/manuscript.tex
@@
 We demonstrate there is an NP-complete language defined by a logarithmic space verifier M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in L.
+In this way, we obtain that L = NL and P = NP cannot be both true or false at the same time and thus, the complexity class L is not equal to NP.
 \end{abstract}
@@
 \section{Introduction}
+
+In previous years there has been great interest in the verification or checking of computations \cite{LIP90}.
+Interactive proofs introduced by Goldwasser, Micali and Rackoff and Babi can be viewed as a model of the verification process \cite{LIP90}.
+Dwork and Stockmeyer and Condon have studied interactive proofs where the verifier is a space bounded computation instead of the original model where the verifer is a time bounded computation \cite{LIP90}.
+In addition, Blum and Kannan has studied another model where the goal is to check a computation based solely on the final answer \cite{LIP90}.
+More about probabilistic logarithmic space verifiers have been shown on a technique of Lipton \cite{LIP90}.
+In this work, we show some results about the logarithmic space verifiers applied to the class $NP$ which solve one of the most important open problems in computer science, that is $L$ versus $NP$.
+
+\section{Motivation}
 
@@
 Whether $P = NP$ or not is still a controversial and unsolved problem \cite{AS17}.
-In this work, we show some results that might be helpful in facing one of the most important open problems in computer science.
+We show some results that are a breakthrough in the future path of solving this outstanding problem.
 
@@
 
+From the early days of automata and complexity  theory,  two  different  models  of  Turing  machines  are  considered, the offline and online machines \cite{KU15}.
+Each model has a read-only input tape and some work tapes \cite{KU15}.
+The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left \cite{KU15}.
+In the terminology of the (generalized) Turing machine models are called two-way and one-way Turing machines respectively \cite{KU15}.
+
+Hartmanis and Mahaney have investigated the classes $1L$ and $1NL$ of languages recognizable by deterministic one-way logarithmic space Turing machine and nondeterministic one-way logarithmic space Turing machine, respectively \cite{HM81}.
+They have shown that $1L \neq 1NL$ (by looking at a uniform variant of the string non-equality problem from communication complexity theory) and have defined a natural complete problem for $1NL$ under deterministic one-way logarithmic space reductions \cite{HM81}.
+Furthermore, they have proven that $1NL \subseteq L$ if and only if $L=NL$ \cite{HM81}.
+
+\begin{theorem}
+\label{argument}
+If the Hypothesis \ref{hypothesis} is true, then $L = NL$ and $P = NP$ cannot be both true or false at the same time and thus, $L \neq NP$.
+\end{theorem}
+
+\begin{proof}
+We can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis} by a nondeterministic logarithmic space Turing machine $N$, such that $N(w) = y$ since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$ \cite{Pap03}.
+Certainly, we can simulate the reading of one symbol from the string $u$ into the read-once tape just nondeterministically generating the same symbol in the work tapes using a logarithmic space \cite{Pap03}.
+
+If we suppose that $L \subset 1NL$, then we can accept the elements of the language $L_{1} \in L$ by a nondeterministic one-way logarithmic space Turing machine $M'$.
+In this way, there is a nondeterministic logarithmic space Turing machine $M''(w) = M'(N(w))$ which will output 1 when $w \in L_{2}$.
+Consequently, $M''$ is a nondeterministic logarithmic space Turing machine which decides the language $L_{2}$.
+The reason is because we can simulate the output string of $N(w)$ within a read-once tape and thus, we can compute in a nondeterministic logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}.
+Certainly, we do not need to reset the computation of $N(w)$ for the reading at once of a symbol in the output string of $N(w)$ by the nondeterministic one-way logarithmic space Turing machine $M'$.
+Therefore, $L_{2}$ is in $NL$ and thus, $L_{2} \in P$ due to $NL \subseteq P$ \cite{Pap03}.
+If any single $\textit{NP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{CLRS01}.
+Since $L_{2} \in P$ and $L_{2} \in \textit{NP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption of $L \subset 1NL$.
+
+Hartmanis and Mahaney have also shown with their result that if $1NL \subseteq L$ or even $1NL \subset L$, then $L=NL$, because they proved there is a complete problem for both $1NL$ and $NL$ at the same time \cite{HM81}.
+If this way, if $L \neq NL$, then $L \subset 1NL$ by contraposition \cite{Pap03}.
+Since we already obtained that $P = NP$ under the assumption of $L \subset 1NL$, therefore if $L \neq NL$, then $P = NP$.
+Hence, if $P \neq NP$, then $L = NL$ by contraposition \cite{Pap03}.
+Consequently, $L = NL$ and $P = NP$ cannot be both true or false at the same time and thus, $L \neq NP$.
+\end{proof}
+
 \section{Results}
@@
 While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MIN\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$.
-Therefore, we obtain that:
+Therefore, we obtain the array $A$ should be valid according to the Theorem \ref{proof} when:
 \[(\psi, K) \in MIN\oplus2SAT \textit{ if and only if } \phi \in \textit{XOR 2SAT}.\]
@@
 
+\begin{theorem}
+$L = NL$ and $P = NP$ cannot be both true or false at the same time and thus, $L \neq NP$.
+\end{theorem}
+
+\begin{proof}
+This is a direct consequence of Theorems \ref{argument} and \ref{result}.
+\end{proof}
+
 \section{Materials and Methods}
 
-This work is implemented into a GitHub Project programmed in Scala \cite{FV19}.
-In this GitHub Project, we use the Assertion on the properties of the instances of each problem and the Unit Test for checking the correctness of every reduction \cite{FV19}.
+This work is implemented into a Project programmed in Scala \cite{FV19}.
+In this Project, we use the Assertion on the properties of the instances of each problem and the Unit Test for checking the correctness of every reduction \cite{FV19}.
 We need to install JDK 8 in order to test the Scala Project \cite{OD16}.

### 2019-10-31 doc/manuscript.tex
Fixed the doc content

@@
 We demonstrate there is an NP-complete language defined by a logarithmic space verifier M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in L.
-In this way, we obtain that L = NL and P = NP cannot be both true or false at the same time and thus, the complexity class L is not equal to NP.
+In this way, we obtain that L = NL and P = NP cannot be both false at the same time.
 \end{abstract}
@@
 More about probabilistic logarithmic space verifiers have been shown on a technique of Lipton \cite{LIP90}.
-In this work, we show some results about the logarithmic space verifiers applied to the class $NP$ which solve one of the most important open problems in computer science, that is $L$ versus $NP$.
+In this work, we show some results about the logarithmic space verifiers applied to the class $NP$ which impact into one of the most important open problems in computer science, that is $P$ versus $NP$.
 
@@
 \label{argument}
-If the Hypothesis \ref{hypothesis} is true, then $L = NL$ and $P = NP$ cannot be both true or false at the same time and thus, $L \neq NP$.
+If the Hypothesis \ref{hypothesis} is true, then $L = NL$ and $P = NP$ cannot be both false at the same time.
 \end{theorem}
@@
 Hence, if $P \neq NP$, then $L = NL$ by contraposition \cite{Pap03}.
-Consequently, $L = NL$ and $P = NP$ cannot be both true or false at the same time and thus, $L \neq NP$.
+Consequently, $L = NL$ and $P = NP$ cannot be both false at the same time.
 \end{proof}
@@
 \begin{theorem}
-$L = NL$ and $P = NP$ cannot be both true or false at the same time and thus, $L \neq NP$.
+$L = NL$ and $P = NP$ cannot be both false at the same time.
 \end{theorem}

### 2019-11-03 doc/manuscript.tex
Updated the proof doc

@@
 We demonstrate there is an NP-complete language defined by a logarithmic space verifier M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in L.
-In this way, we obtain that L = NL and P = NP cannot be both false at the same time.
+In this way, we obtain if L is not equal to NL, then P = NP.
+In addition, we show that L is not equal to NL.
+Hence, we prove the complexity class P is equal to NP.
 \end{abstract}
@@
 More about probabilistic logarithmic space verifiers have been shown on a technique of Lipton \cite{LIP90}.
-In this work, we show some results about the logarithmic space verifiers applied to the class $NP$ which impact into one of the most important open problems in computer science, that is $P$ versus $NP$.
+In this work, we show some results about the logarithmic space verifiers applied to the class $NP$ which solve one of the most important open problems in computer science, that is $P$ versus $NP$.
 
@@
 Whether $P = NP$ or not is still a controversial and unsolved problem \cite{AS17}.
-We show some results that are a breakthrough in the future path of solving this outstanding problem.
+We show some results that prove this outstanding problem with the unexpected solution of $P = NP$.
 
@@
 The logarithmic space reduction is frequently used for $L$ and $NL$ \cite{Pap03}.
+On the one hand, we call the deterministic logarithmic space reduction as $\textit{L-reduction}$.
+On the other hand, we call the nondeterministic logarithmic space reduction as $\textit{NL-reduction}$.
+
 A Boolean formula is in 2-conjunctive normal form, or $2CNF$, if it is in $CNF$ and each clause has exactly two distinct literals.
@@
 
+\section{Consequences}
+
 From the early days of automata and complexity  theory,  two  different  models  of  Turing  machines  are  considered, the offline and online machines \cite{KU15}.
@@
 The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left \cite{KU15}.
-In the terminology of the (generalized) Turing machine models are called two-way and one-way Turing machines respectively \cite{KU15}.
+In the terminology of the (generalized) Turing machine models are called two-way and one-way Turing machines, respectively \cite{KU15}.
 
@@
 \begin{theorem}
-\label{argument}
-If the Hypothesis \ref{hypothesis} is true, then $L = NL$ and $P = NP$ cannot be both false at the same time.
+\label{implication}
+If the Hypothesis \ref{hypothesis} is true, therefore if $L \neq NL$, then $P = NP$.
 \end{theorem}
@@
 If any single $\textit{NP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{CLRS01}.
-Since $L_{2} \in P$ and $L_{2} \in \textit{NP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption of $L \subset 1NL$.
+Since $L_{2} \in P$ and $L_{2} \in \textit{NP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that $L \subset 1NL$.
 
@@
 If this way, if $L \neq NL$, then $L \subset 1NL$ by contraposition \cite{Pap03}.
-Since we already obtained that $P = NP$ under the assumption of $L \subset 1NL$, therefore if $L \neq NL$, then $P = NP$.
-Hence, if $P \neq NP$, then $L = NL$ by contraposition \cite{Pap03}.
-Consequently, $L = NL$ and $P = NP$ cannot be both false at the same time.
+Since we already obtained that $P = NP$ under the assumption that $L \subset 1NL$, therefore if $L \neq NL$, then $P = NP$.
+\end{proof}
+
+Now, we define two classes defined under $\textit{L-reduction}$ and $\textit{NL-reduction}$, respectively.
+
+\begin{definition}
+The class $2L$ contains those languages that are deterministic logarithmic space reduced to a language in $1L$.
+The class $2NL$ consists in those languages that are nondeterministic logarithmic space reduced to a language in $1NL$.
+\end{definition}
+
+\begin{theorem}
+\label{negation}
+$L \neq NL$.
+\end{theorem}
+
+\begin{proof}
+ We obtain that $2L \subseteq L$ and $2NL \subseteq NL$ by the definition of $L$ and $NL$ under the $\textit{L-reduction}$ and $\textit{NL-reduction}$, respectively.
+Certainly, since the output string will be in $1L$ or $1NL$, then we do not need to reset the computation of the $\textit{L-reduction}$ or $\textit{NL-reduction}$ in order to be decided by a deterministic or nondeterministic logarithmic space Turing machine under logarithmic space composition, respectively.
+
+On the one hand, every language in $L_{1} \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$.
+The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read continuously in the input tape during the whole computation in case of acceptance.
+Indeed, for every read symbol in the input tape in $M$, then this is written to the output tape in a sequential way.
+In this way, the output string could be accepted by a deterministic one-way logarithmic space Turing machine, that would be the same Turing machine $M$ where this one will always read on the input tape from left-to-right.
+Certainly, when $M$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right.
+Consequently, $M$ in case of acceptance will output the strings that consist in a language in $1L$.
+Hence, we obtain that $L \subseteq 2L$.
+Since we already know that $2L \subseteq L$, then $L = 2L$.
+
+On the other hand, every language in $L_{2} \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$.
+The reason is simple, because the Turing machine $N$ could output the sequence of symbols that is read continuously in the input tape during the whole computation in case of acceptance.
+Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way.
+In this way, the output string could be accepted by a nondeterministic one-way logarithmic space Turing machine, that would be the same Turing machine $N$ where this one will always read on the input tape from left-to-right.
+Certainly, when $N$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right.
+Consequently, $N$ in case of acceptance will output the strings that consist in a language in $1NL$.
+Hence, we obtain that $NL \subseteq 2NL$.
+Since we already know that $2NL \subseteq NL$, then $NL = 2NL$.
+
+In this way, if $L = NL$ then $2L = 2NL$. However, we know that $2L \neq 2NL$ because of $1L \neq 1NL$ \cite{HM81}. Therefore, we prove the complexity class $L$ is not equal to $NL$.
+\end{proof}
+
+\begin{theorem}
+\label{argument}
+If the Hypothesis \ref{hypothesis} is true, then $P = NP$.
+\end{theorem}
+
+\begin{proof}
+This is a direct consequence of Theorems \ref{implication} and \ref{negation}.
 \end{proof}
@@
 \begin{definition}
-$\textbf{MONOTONE NAE 3SAT}$
+$\textbf{NAE 3SAT}$
 
-INSTANCE: A Boolean formula $\phi$ in $3CNF$ such that each clause has no negation variables.
+INSTANCE: A Boolean formula $\phi$ in $3CNF$.
 
@@
 
-REMARKS: This is equivalent to the special case of the $\textit{NP--complete}$ problem known as $\textit{SET SPLITTING}$ when the sets in the input have exactly three elements and therefore, $\textit{MONOTONE NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}.
+REMARKS: $\textit{NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}.
 \end{definition}
@@
 
-INSTANCE: A positive integer $K$ and a Boolean formula $\phi$ that is an instance of $\textit{XOR 2SAT}$ such that each clause has no negation variables.
+INSTANCE: A positive integer $K$ and a Boolean formula $\phi$ that is an instance of $\textit{XOR 2SAT}$.
 
@@
 It is trivial to see $MIN\oplus2SAT \in NP$ \cite{Pap03}.
-Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses such that each clause has no negation variables, we create three new variables $a_{c_{i}}$, $b_{c_{i}}$ and $d_{c_{i}}$ for each clause $c_{i} = (x \vee y \vee z)$ in $\phi$, where $x$, $y$ and $z$ are positive literals, in the following formula:
+Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we create three new variables $a_{c_{i}}$, $b_{c_{i}}$ and $d_{c_{i}}$ for each clause $c_{i} = (x \vee y \vee z)$ in $\phi$, where $x$, $y$ and $z$ are literals, in the following formula:
 \[P_{i} = (a_{c_{i}} \oplus b_{c_{i}}) \wedge (b_{c_{i}} \oplus d_{c_{i}}) \wedge (a_{c_{i}} \oplus d_{c_{i}}) \wedge (x \oplus a_{c_{i}}) \wedge (y \oplus b_{c_{i}}) \wedge (z \oplus d_{c_{i}}).\]
@@
 Finally, we obtain that
-\[\phi \in \textit{MONOTONE NAE 3SAT} \textit{ if and only if } (\psi, m) \in MIN\oplus2SAT.\]
-Consequently, we prove $\textit{MONOTONE NAE 3SAT} \leq_{p} MIN\oplus2SAT$ where we already know the language $\textit{MONOTONE NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}.
+\[\phi \in \textit{NAE 3SAT} \textit{ if and only if } (\psi, m) \in MIN\oplus2SAT.\]
+Consequently, we prove $\textit{NAE 3SAT} \leq_{p} MIN\oplus2SAT$ where we already know the language $\textit{NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}.
 To sum up, we show $MIN\oplus2SAT \in \textit{NP--hard}$ and $MIN\oplus2SAT \in NP$ and thus, $MIN\oplus2SAT \in \textit{NP--complete}$.
@@
 Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is a valid certificate and also remove the $K$ different clauses from the Boolean formula $\psi$ when we write the final clauses to the output.
-This logarithmic space verification will be the Algorithm \ref{2-algorithm}.
+This logarithmic space verification will be the Algorithm \ref{algorithm}.
 We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = undefined$.
@@
 \begin{algorithm}
-\caption{Logarithmic space verifier}\label{2-algorithm}
+\caption{Logarithmic space verifier}\label{algorithm}
 \begin{algorithmic}[1]
@@
 \begin{theorem}
-$L = NL$ and $P = NP$ cannot be both false at the same time.
+$P = NP$.
 \end{theorem}
@@
 
+\section{Conclusion}
+
+No one has been able to find a polynomial time algorithm for any of more than $300$ important known $\textit{NP--complete}$ problems \cite{GJ79}.
+A proof of $P = NP$ will have stunning practical consequences, because it leads to efficient methods for solving some of the important problems in $NP$ \cite{CS00}.
+The consequences, both positive and negative, arise since various $\textit{NP--complete}$ problems are fundamental in many fields \cite{CS00}.
+All the following consequences are assuming that we have a practical solution for the $\textit{NP--complete}$ problems where such existence was proven with our result:
+
+Cryptography, for example, relies on certain problems being difficult.
+A constructive and efficient solution to an $\textit{NP--complete}$ problem such as $3SAT$ will break most existing cryptosystems including: Public-key cryptography \cite{HW97}, symmetric ciphers \cite{MM00} and one-way functions used in cryptographic hashing \cite{DKV07}.
+These would need to be modified or replaced by information-theoretically secure solutions not inherently based on $\textit{P--NP}$ equivalence.
+
+There are enormous positive consequences that will follow from rendering tractable many currently mathematically intractable problems.
+For instance, many problems in operations research are $\textit{NP--complete}$, such as some types of integer programming and the traveling salesman problem \cite{GJ79}.
+Efficient solutions to these problems have enormous implications for logistics \cite{CS00}.
+Many other important problems, such as some problems in protein structure prediction, are also $\textit{NP--complete}$, so this will spur considerable advances in biology \cite{BL98}.
+
+Moreover, Learning becomes easy by using the principle of Occam's razor: We simply find the smallest program consistent with the data \cite{LF09}.
+Near perfect vision recognition, language comprehension and translation and all other learning tasks become trivial \cite{LF09}.
+We will also have much better predictions of weather and earthquakes and other natural phenomenon \cite{LF09}.
+
+But such changes may pale in significance compared to the revolution an efficient method for solving $\textit{NP--complete}$ problems will cause in mathematics itself.
+Research mathematicians spend their careers trying to prove theorems, and some proofs have taken decades or even centuries to find after problems have been stated.
+For instance, Fermat's Last Theorem took over three centuries to prove.
+A method that is guaranteed to find proofs to theorems, should one exist of a $``$reasonable$"$ size, would essentially end this struggle \cite{CS00}.
+
 \bibliography{manuscript}

### 2019-11-04 src/main/scala/frank/problems/Instance.scala
Removed the monotone versions

@@ -9,26 +9,22 @@ import frank.sat.Formula
 sealed trait Instance
 
 /**
-  * A Boolean formula in 3CNF such that each clause has no negation
-  * variables.
+  * A Boolean formula in 3CNF.
   * Question: Is there a truth assignment for the formula such that each clause has at least one true
   * literal and at least one false literal?
   * This problem is a known NP-complete language.
   */
-case class MonotoneNaeSat(formula: Formula) extends Instance{
+case class NaeSat(formula: Formula) extends Instance{
   assert(formula.isExactlyKSat(3), "Should be in 3CNF")
-  assert(formula.isMonotoneSat, "Should be Monotone")
 }
 
 /**
-  * A positive integer K and a Boolean formula that is an instance of
-  * XOR 2SAT such that each clause has no negation variables.
+  * A positive integer K and a Boolean formula that is an instance of XOR 2SAT.
   * Question: Is there a truth assignment in the formula such that at most K clauses are unsatisfiable?
   * This problem is in NP-complete.
   */
 case class MinXor2Sat(K: Int, formula: Formula) extends Instance{
   assert(formula.isExactlyKSat(2), "Should be in 2CNF")
-  assert(formula.isMonotoneSat, "Should be Monotone")
   assert(K > 0, "K should be a positive integer")
   assert(K <= formula.variableCount, "K should be at most all the clauses")
 
@@ -36,13 +32,12 @@ case class MinXor2Sat(K: Int, formula: Formula) extends Instance{
 
 
 /**
-  * An instance of XOR 2SAT such that each clause has no negation variables.
+  * An instance of XOR 2SAT.
   * Question: Is there a satisfying truth assignment for the Boolean formula?
   * This problem is in NP-complete.
   */
-case class MonotoneXor2Sat(formula: Formula) extends Instance{
+case class Xor2Sat(formula: Formula) extends Instance{
   assert(formula.isExactlyKSat(2), "Should be in 2CNF")
-  assert(formula.isMonotoneSat, "Should be Monotone")
 }
 
 

### 2019-11-04 src/main/scala/frank/problems/Reduction.scala

@@ -13,8 +13,8 @@ trait Reduction[U<:Instance, V<:Instance, C] {
 /**
   * Theorem 6 in paper https://www.preprints.org/manuscript/201908.0037/v1
   */
-object ReductionKnownNPComplete extends Reduction[MonotoneNaeSat, MinXor2Sat, Any]{
-  override def reduction(input: MonotoneNaeSat, certificate: Option[Any] = None): MinXor2Sat = {
+object ReductionKnownNPComplete extends Reduction[NaeSat, MinXor2Sat, Any]{
+  override def reduction(input: NaeSat, certificate: Option[Any] = None): MinXor2Sat = {
 
     val clauses: Seq[List[Clause]] = for {(clause, index) <- input.formula.clauses.zipWithIndex
                                      variable = input.formula.variables.max + 3*index} yield {
@@ -33,8 +33,8 @@ object ReductionKnownNPComplete extends Reduction[MonotoneNaeSat, MinXor2Sat, An
 /**
   * Theorem 7 in paper https://www.preprints.org/manuscript/201908.0037/v1
   */
-object ReductionWithVerification extends Reduction[MinXor2Sat, MonotoneXor2Sat, Array[Int]]{
-  override def reduction(input: MinXor2Sat, certificate: Option[Array[Int]] = None): MonotoneXor2Sat = {
+object ReductionWithVerification extends Reduction[MinXor2Sat, Xor2Sat, Array[Int]]{
+  override def reduction(input: MinXor2Sat, certificate: Option[Array[Int]] = None): Xor2Sat = {
     if (certificate.isEmpty) throw new IllegalArgumentException("The certificate is not valid")
     val array: Array[Int] = certificate.get
     // Output the value of m
@@ -58,6 +58,6 @@ object ReductionWithVerification extends Reduction[MinXor2Sat, MonotoneXor2Sat, 
       }
       min = max + 1
     }
-    MonotoneXor2Sat(Formula(clauses: _*))
+    Xor2Sat(Formula(clauses: _*))
   }
 }

### 2019-11-04 src/test/scala/frank/problems/Common.scala

@@ -11,19 +11,19 @@ import org.scalatest.Inside._
 
 trait Common extends Matchers {
 
-  def reduceSat(reducer: Reduction[MonotoneNaeSat, MinXor2Sat, Any], input: Formula) = {
-    reducer.reduction(MonotoneNaeSat(input)) should matchPattern {
+  def reduceSat(reducer: Reduction[NaeSat, MinXor2Sat, Any], input: Formula) = {
+    reducer.reduction(NaeSat(input)) should matchPattern {
       case output:MinXor2Sat =>
     }
   }
 
-  def verifySat(verifier: Reduction[MinXor2Sat, MonotoneXor2Sat, Array[Int]], reducer: Reduction[MonotoneNaeSat, MinXor2Sat, Any], input: Formula, certificate: Array[Int]) = {
-    val value = verifier.reduction(reducer.reduction(MonotoneNaeSat(input)), Some(certificate))
+  def verifySat(verifier: Reduction[MinXor2Sat, Xor2Sat, Array[Int]], reducer: Reduction[NaeSat, MinXor2Sat, Any], input: Formula, certificate: Array[Int]) = {
+    val value = verifier.reduction(reducer.reduction(NaeSat(input)), Some(certificate))
     value should matchPattern {
-      case output: MonotoneXor2Sat =>
+      case output: Xor2Sat =>
     }
     inside(value) {
-      case output: MonotoneXor2Sat => XORSolver.solve(output.formula) should matchPattern {
+      case output: Xor2Sat => XORSolver.solve(output.formula) should matchPattern {
         case Satisfiable() =>
         case Satisfiable(literals@_*) if !literals.isEmpty =>
       }

### 2019-11-04 src/test/scala/frank/problems/ReductionSat$Test.scala

@@ -14,13 +14,14 @@ class ReductionSat$Test extends FlatSpec with Common {
   val formula2 = Formula(Clause(1, 2, 3), Clause(2, 5, 6))
   val formula3 = Formula(Clause(1, 2, 3), Clause(2, 5, 6), Clause(1, 3, 4))
   val formula4 = Formula(Clause(1, 2, 3), Clause(2, 5, 6), Clause(1, 3, 5))
+  val formula5 = Formula(Clause(-1, -2, -3))
 
   it should "reduce 3CNF formulas" in {
     reduceSat(reducer, formula1)
     reduceSat(reducer, formula2)
     reduceSat(reducer, formula3)
     reduceSat(reducer, formula4)
-
+    reduceSat(reducer, formula5)
 
   }
 
@@ -28,6 +29,7 @@ class ReductionSat$Test extends FlatSpec with Common {
 
     verifySat(verifier, reducer, formula3, Array(1, 9, 15))
     verifySat(verifier, reducer, formula4, Array(3, 8, 14))
+    verifySat(verifier, reducer, formula5, Array(1))
 
 
   }

### 2019-11-05 doc/presentation.tex
Added a presentation pdf

\documentclass[11pt]{beamer}

%%%%%%%% tema e cor %%%%%%%%
\mode<presentation> {
\usetheme{Madrid}
%\usecolortheme{albatross}
}

\usepackage{url}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algpseudocode}
\usepackage{algorithm}
\algrenewcommand{\algorithmiccomment}[1]{\State /*#1*/}
\algnewcommand\algorithmicto{$\textbf{to}$}
\algrenewtext{For}[3]{\algorithmicfor\ #1 $\gets$ #2 \algorithmicto\ #3 \algorithmicdo}
%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{definition}[theorem]{Definition}
\setbeamertemplate{theorems}[numbered]

\begin{document}

\title{$P$ versus $NP$}

\subtitle{The proof on \url{https://www.preprints.org/manuscript/201908.0037/v1} \cite{PFV19}}

\author{Frank Vega}

%\address{Copsonic, 1471 Route de St-Nauphary, 82000 Montauban, France}

%\email{vega.frank@gmail.com}

%\subjclass[2000]{Primary 68Q15}

\keywords{complexity classes, completeness, verifier, reduction, polynomial time, logarithmic space}

\maketitle

\begin{frame}{Open Problem}

$P$ versus $NP$ is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is $P$ equal to $NP$? A precise statement of the $P$ versus $NP$ problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. We show some results that prove this outstanding problem with the unexpected solution of $P = NP$.

\end{frame}

\begin{frame}{Another definition of $NP$}

We can define an $NP$ problem as

\[L2 = \{w: M(w, c) = y \textit{ where } y \in L1\} (\textit{y is the output in the halting state})\]

when $L1$ is a language in $P$, $M$ is a deterministic Turing machine that runs in polynomial time in the length of $w$ and $c$ (the certificate) is polynomially bounded by $w$.

\end{frame}

\begin{frame}{Equivalent definition}

This is easy to prove since the polynomial time composition reduction can be done in polynomial time. Therefore, the previous definition complies with the existence of a polynomial time verifier $M’$ such that the $NP$ problem $L2$ is defined as

\[L2 = \{w: M'(w, c) = ``yes"\} (\textit{``yes" is the acceptance state})\]

where the computation of $M'(w, c)$ is equal to $N(M(w, c))$ when $N$ is the Turing machine which accepts $L1$ in polynomial time.

\end{frame}

\begin{frame}{The logarithmic space verifier}

On the other hand, the verifier for a language in $NL$ (nondeterministic logarithmic space class) has as premise that the certificate c is placed in a special tape that is read only and read at once (that means we cannot read to the left).

\end{frame}

\begin{frame}{Our result}

\begin{theorem}
\label{result}
In our work was proved that we can define a $\textit{NP--complete}$ problem as

\[L2 = \{w: M(w, c) = y \textit{ where } y \in L1\} (\textit{y is the output in the halting state})\]

when $L1$ is a language in $L$ (deterministic logarithmic space class), $M$ is a deterministic Turing machine that runs in logarithmic space in the length of $w$ and $c$ (the certificate) is polynomially bounded by $w$ such that $c$ is placed in the special tape in $M$ that is read only and read at once.
\end{theorem}

\end{frame}

\begin{frame}{Converting the verifier}

We can simulate the computation $M(w, c) = y$ by a nondeterministic logarithmic space Turing machine $N$, such that $N(w) = y$ since we can read the certificate string $c$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $c$. Certainly, we can simulate the reading of one symbol from the string $c$ into the read-once tape just nondeterministically generating the same symbol in the work tapes using a logarithmic space.

\end{frame}

\begin{frame}{The classes $1L$ and $1NL$}

\begin{definition}
Hartmanis and Mahaney have investigated the classes 1L and 1NL of languages recognizable by deterministic one-way logarithmic space Turing machine and nondeterministic one-way logarithmic space Turing machine, respectively. The one-way machines are not allowed to move the input head to the left.
\end{definition}

\end{frame}

\begin{frame}{Supposition}

If we suppose that $L \subset 1NL$, then we can accept the elements of the language $L1 \in L$ by a nondeterministic one-way logarithmic space Turing machine $M'$. In this way, there is a nondeterministic logarithmic space Turing machine $M''(w) = M'(N(w))$ which will halt in the acceptance state when $w \in L2$. Consequently, $M''$ is a nondeterministic logarithmic space Turing machine which decides the language $L2$.

\end{frame}

\begin{frame}{The arguments}

The reason is because we can simulate the output string of $N(w)$ within a read-once tape and thus, we can compute in a nondeterministic logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation. Certainly, we do not need to reset the computation of $N(w)$ for the reading at once of a symbol in the output string of $N(w)$ by the nondeterministic one-way logarithmic space Turing machine $M'$.

\end{frame}

\begin{frame}{Consequences}

Therefore, $L2 \in NL$ and thus, $L2 \in P$ due to $NL \subseteq P$. If any single $\textit{NP--complete}$ problem can be solved in polynomial time, then $P = NP$. Since $L2 \in P$ and $L2 \in \textit{NP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that $L \subset 1NL$. Hartmanis and Mahaney have also shown with their result that if $1NL$ is a subset of $L$, then $L=NL$, because they proved there is a complete problem for both $1NL$ and $NL$ at the same time. If this way, if $L \neq NL$, then $L \subset 1NL$ by contraposition. Since we already obtained that $P = NP$ under the assumption that $L \subset 1NL$, therefore if $L \neq NL$, then $P = NP$.

\end{frame}

\begin{frame}{The classes $2L$ and $2NL$}

\begin{definition}
The class 2L contains those languages that are deterministic logarithmic space reduced to a language in 1L. The class 2NL consists in those languages that are nondeterministic logarithmic space reduced to a language in 1NL.
\end{definition}

\end{frame}

\begin{frame}{Inclusion}

We obtain that $2L \subseteq L$ and $2NL \subseteq NL$ by the definition of $L$ and $NL$ under the $\textit{L--reduction}$ and $\textit{NL--reduction}$, respectively. Certainly, since the output string will be in $1L$ or $1NL$, then we do not need to reset the computation of the $\textit{L--reduction}$ or $\textit{NL--reduction}$ in order to be decided by a deterministic or nondeterministic logarithmic space Turing machine under logarithmic space composition, respectively.

\end{frame}

\begin{frame}{Proof of $L = 2L$: First part}

On the one hand, every language in $L' \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$. The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read continuously in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $M$, then this is written to the output tape in a sequential way.
\end{frame}

\begin{frame}{Proof of $L = 2L$: Second part}

In this way, the output string could be accepted by a deterministic one-way logarithmic space Turing machine, that would be the same Turing machine $M$ where this one will always read on the input tape from left-to-right. Certainly, when $M$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $M$ in case of acceptance will output the strings that consist in a language in $1L$. Hence, we obtain that $L \subseteq 2L$. Since we already know that $2L \subseteq L$, then $L = 2L$.

\end{frame}

\begin{frame}{Proof of $NL = 2NL$: First part}

On the other hand, every language in $L'' \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$. The reason is simple, because the Turing machine $N$ could output the sequence of symbols that is read continuously in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way.

\end{frame}

\begin{frame}{Proof of $NL = 2NL$: Second part}

In this way, the output string could be accepted by a nondeterministic one-way logarithmic space Turing machine, that would be the same Turing machine $N$ where this one will always read on the input tape from left-to-right. Certainly, when $N$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $N$ in case of acceptance will output the strings that consist in a language in $1NL$. Hence, we obtain that $NL \subseteq 2NL$. Since we already know that $2NL \subseteq NL$, then $NL = 2NL$.

\end{frame}

\begin{frame}{Conclusion: $P = NP$}

In this way, if $L = NL$ then $2L = 2NL$. However, we know that $2L \neq 2NL$ because of $1L \neq 1NL$ since Hartmanis and Mahaney have shown that $1L \neq 1NL$ by looking at a uniform variant of the string non-equality problem from communication complexity theory. Therefore, we prove the complexity class $L$ is not equal to $NL$. Since we show that $L \neq NL$, then we prove the complexity class $P$ is equal to $NP$.

\end{frame}

\begin{frame}{Code}

In this Scala Project \cite{GFV19}, we use the Assertion on the properties of the instances of each problem and the Unit Test for checking the correctness of the Theorem \ref{result}. We need to install JDK 8 in order to test the Scala Project. In addition, we need to install SBT to run the unit test (we could run the unit test with the $\textbf{sbt test}$ command).

\end{frame}

\begin{frame}{References}

\begin{thebibliography}{1}

\bibitem{PFV19}
Frank Vega.
\newblock Logarithmic Space Verifiers on NP-complete.
\newblock In {\em Preprints}, 2019, 2019080037.
\newblock \href {https://doi.org/10.20944/preprints201908.0037.v1}
  {\path{doi:10.20944/preprints201908.0037.v1}}.

\bibitem{GFV19}
Frank Vega.
\newblock Verify{R}eduction, August 2019.
\newblock In a GitHub repository at
  \url{https://github.com/frankvegadelgado/VerifyReduction}.

\end{thebibliography}

\end{frame}

\end{document}

### 2019-11-12 doc/manuscript.tex
Updated the content proof

@@
 
-\section{Motivation}
-
 The $P$ versus $NP$ problem is a major unsolved problem in computer science \cite{CS00}.
@@
 
-\section{Preliminaries}
+\section{Materials and Methods}
+
+\subsection{Preliminaries}
 
@@
 
-\section{Hypothesis}
+\subsection{Hypothesis}
 
@@
 The logarithmic space reduction is frequently used for $L$ and $NL$ \cite{Pap03}.
-On the one hand, we call the deterministic logarithmic space reduction as $\textit{L-reduction}$.
-On the other hand, we call the nondeterministic logarithmic space reduction as $\textit{NL-reduction}$.
+On the one hand, we call the deterministic logarithmic space reduction as $\textit{L--reduction}$.
+On the other hand, we call the nondeterministic logarithmic space reduction as $\textit{NL--reduction}$.
 
@@
 
-\section{Consequences}
+\subsection{Consequences}
 
@@
 
-Now, we define two classes defined under $\textit{L-reduction}$ and $\textit{NL-reduction}$, respectively.
+Now, we define two classes defined under $\textit{L--reduction}$ and $\textit{NL--reduction}$, respectively.
 
@@
 \end{definition}
+
+Let $\textit{1TAPE}[T(n)]$ denote the family of languages accepted by deterministic one-way Turing machines with $T(n)$ work tape \cite{HM81}.
+
+\begin{theorem}
+\label{closed}
+If $T(n)$ is such that
+\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
+then $\textit{1TAPE}[T(n)]$ is closed under deterministic two-way logarithmic space reduction.
+\end{theorem}
+
+\begin{proof}
+Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some $T'(n)$ when
+\[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\] 
+Hence, the family of languages $\textit{1TAPE}[T'(n)]$ is two-way logarithmic space reduced to the another family of languages $\textit{1TAPE}[T'(n) - H(n)]$ where the deterministic two-way logarithmic space reduction consumes less than $H(n)$ in the work tapes.
+Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $k \times n$ symbols for some arbitrary number $k > 1$ which mostly depends from the original instance, that is the result of reading consecutively the symbols in the input tape in a sequential way.
+This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $k \times n$.
+However, we know in that instance of size at most $k \times n$, we can replace the deterministic two-way logarithmic space reduction by a deterministic one-way logarithmic space reduction that read contiguously from left-to-right.
+Therefore, the instance of size at most $k \times n$ could be decided by a deterministic one-way logarithmic space Turing machine that simulates the two-way logarithmic space reduction with less than $H(n)$ in the work tapes within the composition on the another deterministic one-way logarithmic space Turing machine which is used in $\textit{1TAPE}[T'(n) - H(n)]$ after the deterministic two-way logarithmic space reduction of the original language.
+In this way, we obtain that the family of languages of $\textit{1TAPE}[T'(n)]$ is contained into the family of languages $\textit{1TAPE}[T'(\frac{n}{k})]$ for some arbitrary number $k > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction.
+As result, we obtain that $\textit{1TAPE}[T'(n)] = \textit{1TAPE}[T'(\frac{n}{k})]$ since we previously know that $\textit{1TAPE}[T'(\frac{n}{k})] \subseteq \textit{1TAPE}[T'(n)]$ and we show that $\textit{1TAPE}[T'(n)] \subseteq \textit{1TAPE}[T'(\frac{n}{k})]$ under our supposition.
+Since $T'(n)$ is not equal to $T'(\frac{n}{k})$ for some arbitrary number $k > 1$, then we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}.
+In general, we can assume the same result for every sparse function $T(n)$.
+\end{proof}
+
+\begin{theorem}
+\label{partially}
+$1L \neq 1NL$ under deterministic two-way logarithmic space reduction.
+\end{theorem}
+
+\begin{proof} 
+Hartmanis and Mahaney have shown that $1NL \varsubsetneq \textit{1TAPE}[T(n)]$ when 
+\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
+in their paper \cite{HM81}. Consequently, this is a direct result of Theorem \ref{closed}.
+\end{proof}
 
@@
 \begin{proof}
- We obtain that $2L \subseteq L$ and $2NL \subseteq NL$ by the definition of $L$ and $NL$ under the $\textit{L-reduction}$ and $\textit{NL-reduction}$, respectively.
-Certainly, since the output string will be in $1L$ or $1NL$, then we do not need to reset the computation of the $\textit{L-reduction}$ or $\textit{NL-reduction}$ in order to be decided by a deterministic or nondeterministic logarithmic space Turing machine under logarithmic space composition, respectively.
+ We obtain that $2L \subseteq L$ and $2NL \subseteq NL$ by the definition of $L$ and $NL$ under the $\textit{L--reduction}$ and $\textit{NL--reduction}$, respectively.
+Certainly, since the output string will be in $1L$ or $1NL$, then we do not need to reset the computation of the $\textit{L--reduction}$ or $\textit{NL--reduction}$ in order to be decided by a deterministic or nondeterministic logarithmic space Turing machine under logarithmic space composition, respectively.
 
 On the one hand, every language in $L_{1} \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$.
-The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read continuously in the input tape during the whole computation in case of acceptance.
+The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance.
 Indeed, for every read symbol in the input tape in $M$, then this is written to the output tape in a sequential way.
@@
 On the other hand, every language in $L_{2} \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$.
-The reason is simple, because the Turing machine $N$ could output the sequence of symbols that is read continuously in the input tape during the whole computation in case of acceptance.
+The reason is simple, because the Turing machine $N$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance.
 Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way.
@@
 
-In this way, if $L = NL$ then $2L = 2NL$. However, we know that $2L \neq 2NL$ because of $1L \neq 1NL$ \cite{HM81}. Therefore, we prove the complexity class $L$ is not equal to $NL$.
+In this way, if $L = NL$ then $2L = 2NL$.
+However, we know that $2L \neq 2NL$ because of $1L \neq 1NL$ under deterministic two-way logarithmic space reduction according to the Theorem \ref{partially}.
+Indeed, in case of $2L = 2NL$, then every language in $1NL$ is deterministic two-way logarithmic space reduced to a language in $1L$ and viceversa.
+Consequently, we prove the complexity class $L$ is not equal to $NL$.
 \end{proof}
@@
 \end{proof}
+
+\subsection{Codes}
+
+This work is implemented into a Project programmed in Scala \cite{FV19}.
+We need to install JDK 8 in order to test the Scala Project \cite{OD16}.
+In addition, we need to install SBT to run the unit test (we could run the unit test with the $\textbf{sbt test}$ command) \cite{OD16}.
 
@@
 
-\section{Materials and Methods}
-
-This work is implemented into a Project programmed in Scala \cite{FV19}.
-In this Project, we use the Assertion on the properties of the instances of each problem and the Unit Test for checking the correctness of every reduction \cite{FV19}.
-We need to install JDK 8 in order to test the Scala Project \cite{OD16}.
-In addition, we need to install SBT to run the unit test (we could run the unit test with the $\textbf{sbt test}$ command) \cite{OD16}.
-
-\section{Conclusion}
+\section{Conclusions}
 
@@
 
-Moreover, Learning becomes easy by using the principle of Occam's razor: We simply find the smallest program consistent with the data \cite{LF09}.
+Since all the $\textit{NP--complete}$ optimization problems become easy, everything will be much more efficient \cite{LF09}.
+Transportation of all forms will be scheduled optimally to move people and goods around quicker and cheaper \cite{LF09}.
+Manufacturers can improve their production to increase speed and create less waste \cite{LF09}.
+
+Learning becomes easy by using the principle of Occam's razor: We simply find the smallest program consistent with the data \cite{LF09}.
 Near perfect vision recognition, language comprehension and translation and all other learning tasks become trivial \cite{LF09}.
 We will also have much better predictions of weather and earthquakes and other natural phenomenon \cite{LF09}.
+
+The economy would become vastly more efficient.
+There would be disruption, including maybe displacing programmers \cite{IMP95}.
+The practice of programming itself would be more about gathering training data and less about writing code \cite{IMP95}.
+Google would have the resources to excel in such a world \cite{IMP95}.
 

### 2019-11-12 doc/manuscript.tex
Updated the content proof

@@
 Hence, the family of languages $\textit{1TAPE}[T'(n)]$ is two-way logarithmic space reduced to the another family of languages $\textit{1TAPE}[T'(n) - H(n)]$ where the deterministic two-way logarithmic space reduction consumes less than $H(n)$ in the work tapes.
-Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $k \times n$ symbols for some arbitrary number $k > 1$ which mostly depends from the original instance, that is the result of reading consecutively the symbols in the input tape in a sequential way.
+Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $k \times n$ symbols for some constant $k > 1$, that is the result of reading consecutively the symbols in the input tape in a sequential way.
 This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $k \times n$.
@@
 Therefore, the instance of size at most $k \times n$ could be decided by a deterministic one-way logarithmic space Turing machine that simulates the two-way logarithmic space reduction with less than $H(n)$ in the work tapes within the composition on the another deterministic one-way logarithmic space Turing machine which is used in $\textit{1TAPE}[T'(n) - H(n)]$ after the deterministic two-way logarithmic space reduction of the original language.
-In this way, we obtain that the family of languages of $\textit{1TAPE}[T'(n)]$ is contained into the family of languages $\textit{1TAPE}[T'(\frac{n}{k})]$ for some arbitrary number $k > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction.
+In this way, we obtain that the family of languages of $\textit{1TAPE}[T'(n)]$ is contained into the family of languages $\textit{1TAPE}[T'(\frac{n}{k})]$ for some constant $k > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction.
 As result, we obtain that $\textit{1TAPE}[T'(n)] = \textit{1TAPE}[T'(\frac{n}{k})]$ since we previously know that $\textit{1TAPE}[T'(\frac{n}{k})] \subseteq \textit{1TAPE}[T'(n)]$ and we show that $\textit{1TAPE}[T'(n)] \subseteq \textit{1TAPE}[T'(\frac{n}{k})]$ under our supposition.
-Since $T'(n)$ is not equal to $T'(\frac{n}{k})$ for some arbitrary number $k > 1$, then we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}.
+Since $T'(n)$ is not equal to $T'(\frac{n}{k})$ for some constant $k > 1$, then we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}.
 In general, we can assume the same result for every sparse function $T(n)$.

### 2019-11-12 doc/manuscript.tex
Updated the content proof

@@
 \[x \in L_{1} \textit{ if and only if } f(x) \in L_{2}.\]
-An important complexity class is $\textit{NP--complete}$ \cite{OG10}. A language $L_{1} \subseteq \{0, 1\}^{*}$ is $\textit{NP--complete}$ if:
+An important complexity class is $\textit{NP--complete}$ \cite{GJ79}. A language $L_{1} \subseteq \{0, 1\}^{*}$ is $\textit{NP--complete}$ if:
 
@@
 \[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\]
-Hence, the family of languages $\textit{1TAPE}[T'(n)]$ is two-way logarithmic space reduced to the another family of languages $\textit{1TAPE}[T'(n) - H(n)]$ where the deterministic two-way logarithmic space reduction consumes less than $H(n)$ in the work tapes.
-Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $k \times n$ symbols for some constant $k > 1$, that is the result of reading consecutively the symbols in the input tape in a sequential way.
-This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $k \times n$.
-However, we know in that instance of size at most $k \times n$, we can replace the deterministic two-way logarithmic space reduction by a deterministic one-way logarithmic space reduction that read contiguously from left-to-right.
-Therefore, the instance of size at most $k \times n$ could be decided by a deterministic one-way logarithmic space Turing machine that simulates the two-way logarithmic space reduction with less than $H(n)$ in the work tapes within the composition on the another deterministic one-way logarithmic space Turing machine which is used in $\textit{1TAPE}[T'(n) - H(n)]$ after the deterministic two-way logarithmic space reduction of the original language.
-In this way, we obtain that the family of languages of $\textit{1TAPE}[T'(n)]$ is contained into the family of languages $\textit{1TAPE}[T'(\frac{n}{k})]$ for some constant $k > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction.
-As result, we obtain that $\textit{1TAPE}[T'(n)] = \textit{1TAPE}[T'(\frac{n}{k})]$ since we previously know that $\textit{1TAPE}[T'(\frac{n}{k})] \subseteq \textit{1TAPE}[T'(n)]$ and we show that $\textit{1TAPE}[T'(n)] \subseteq \textit{1TAPE}[T'(\frac{n}{k})]$ under our supposition.
-Since $T'(n)$ is not equal to $T'(\frac{n}{k})$ for some constant $k > 1$, then we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}.
+Hence, the family of languages $\textit{1TAPE}[T'(n)]$ is two-way logarithmic space reduced to the another family of languages $\textit{1TAPE}[T'(n) - H(n)]$ where the deterministic two-way logarithmic space reduction consumes at most $H(n)$ in the work tapes.
+Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $G(n) \times n$ symbols for some function $G(n) > 1$, that is the result of reading consecutively the symbols in the input tape in a sequential way.
+This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $G(n) \times n$.
+However, we know in that instance of size at most $G(n) \times n$, we can replace the deterministic two-way logarithmic space reduction by a deterministic one-way logarithmic space reduction that read contiguously from left-to-right.
+Therefore, the instance of size at most $G(n) \times n$ could be decided by a deterministic one-way logarithmic space Turing machine that simulates the two-way logarithmic space reduction with at most $H(n)$ in the work tapes within the composition on the another deterministic one-way logarithmic space Turing machine which is used in $\textit{1TAPE}[T'(n) - H(n)]$ after the deterministic two-way logarithmic space reduction of the original language.
+In this way, we obtain that the family of languages of $\textit{1TAPE}[T'(n)]$ is contained into the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction.
+As result, we obtain that $\textit{1TAPE}[T'(n)] = \textit{1TAPE}[T'(\frac{n}{G(n)})]$ since we previously know that $\textit{1TAPE}[T'(\frac{n}{G(n)})] \subseteq \textit{1TAPE}[T'(n)]$ and we show that $\textit{1TAPE}[T'(n)] \subseteq \textit{1TAPE}[T'(\frac{n}{G(n)})]$ under our supposition.
+Since $\textit{1TAPE}[T'(n)]$ is not equal to $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$, then we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}.
 In general, we can assume the same result for every sparse function $T(n)$.

### 2019-11-12 doc/manuscript.tex
Updated the content proof

@@
 In this work, we show some results about the logarithmic space verifiers applied to the class $NP$ which solve one of the most important open problems in computer science, that is $P$ versus $NP$.
+
+\section{Motivation}
 
@@
 Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $G(n) \times n$ symbols for some function $G(n) > 1$, that is the result of reading consecutively the symbols in the input tape in a sequential way.
+The existence of such function $G(n) > 1$ is possible because the family of languages $\textit{1TAPE}[T'(n)]$ is a subset of $P$ and thus $G(n) < 2^{n}$ \cite{Pap03}.
 This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $G(n) \times n$.
@@
 Therefore, the instance of size at most $G(n) \times n$ could be decided by a deterministic one-way logarithmic space Turing machine that simulates the two-way logarithmic space reduction with at most $H(n)$ in the work tapes within the composition on the another deterministic one-way logarithmic space Turing machine which is used in $\textit{1TAPE}[T'(n) - H(n)]$ after the deterministic two-way logarithmic space reduction of the original language.
-In this way, we obtain that the family of languages of $\textit{1TAPE}[T'(n)]$ is contained into the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction.
-As result, we obtain that $\textit{1TAPE}[T'(n)] = \textit{1TAPE}[T'(\frac{n}{G(n)})]$ since we previously know that $\textit{1TAPE}[T'(\frac{n}{G(n)})] \subseteq \textit{1TAPE}[T'(n)]$ and we show that $\textit{1TAPE}[T'(n)] \subseteq \textit{1TAPE}[T'(\frac{n}{G(n)})]$ under our supposition.
-Since $\textit{1TAPE}[T'(n)]$ is not equal to $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$, then we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}.
+In this way, we obtain that the family of languages of $\textit{1TAPE}[T'(n)]$ has a projection to the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction.
+As result, we obtain that the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$.
+Recursively, we obtain that the family of languages of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ has a projection to the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)^{2}})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction.
+Consequently, we obtain that the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)^{2}})]$.
+If we recursively continue so forth, then we obtain that the cardinality of the family of languages $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)^{j}})]$ for every natural number $j$.
+However, if we follow this assumption, then we obtain that
+\[\lim_{j\to\infty} T'(\frac{n}{G(n)^{j}}) = T'(0).\]
+has a cardinality greater than or equal to $\textit{1TAPE}[T'(n)]$.
+Nevertheless, the cardinality of the family of languages $\textit{1TAPE}[T'(n)]$ cannot be lesser than or equal to the cardinality of family of languages $\textit{1TAPE}[T'(0)]$.
+Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}.
 In general, we can assume the same result for every sparse function $T(n)$.
@@
 \[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
-in their paper \cite{HM81}. Consequently, this is a direct result of Theorem \ref{closed}.
+in their paper \cite{HM81}. Consequently, this is a consequence of Theorem \ref{closed} because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
 \end{proof}
@@
 \end{proof}
-
-\subsection{Codes}
-
-This work is implemented into a Project programmed in Scala \cite{FV19}.
-We need to install JDK 8 in order to test the Scala Project \cite{OD16}.
-In addition, we need to install SBT to run the unit test (we could run the unit test with the $\textbf{sbt test}$ command) \cite{OD16}.
 
@@
 
+\subsection{Programming Codes}
+
+This work is implemented into a Project programmed in Scala \cite{FV19}.
+In this Project, we use the Assertion on the properties of the instances of each problem and the Unit Test for checking the correctness of every reduction \cite{FV19}.
+We need to install JDK 8 in order to test the Scala Project \cite{OD16}.
+In addition, we need to install SBT to run the unit test (we could run the unit test with the $\textbf{sbt test}$ command) \cite{OD16}.
+
 \section{Conclusions}

### 2019-11-12 doc/manuscript.tex
Updated the content proof

@@
 \begin{proof}
-Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some $T'(n)$ when
+Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some $T'(n)$ that is not a constant when
 \[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\]
@@
 has a cardinality greater than or equal to $\textit{1TAPE}[T'(n)]$.
-Nevertheless, the cardinality of the family of languages $\textit{1TAPE}[T'(n)]$ cannot be lesser than or equal to the cardinality of family of languages $\textit{1TAPE}[T'(0)]$.
+Nevertheless, the cardinality of the family of languages $\textit{1TAPE}[T'(n)]$ cannot be lesser than or equal to the cardinality of family of languages $\textit{1TAPE}[T'(0)]$ just assuming that $T'(n)$ is not a constant.
 Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}.
@@
 \[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
-in their paper \cite{HM81}. Consequently, this is a consequence of Theorem \ref{closed} because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
+in their paper \cite{HM81}. Consequently, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
 \end{proof}

### 2019-11-12 doc/manuscript.tex
Updated the content proof

@@
 \[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
-then $\textit{1TAPE}[T(n)]$ is closed under deterministic two-way logarithmic space reduction.
+and is not a constant, then $\textit{1TAPE}[T(n)]$ is closed under deterministic two-way logarithmic space reduction.
 \end{theorem}
@@
 \[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
-in their paper \cite{HM81}. Consequently, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
+in their paper \cite{HM81}. Consequently, this is a result of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
 \end{proof}

### 2019-11-12 doc/manuscript.tex
Updated the content proof

@@
 However, if we follow this assumption, then we obtain that
-\[\lim_{j\to\infty} T'(\frac{n}{G(n)^{j}}) = T'(0).\]
+\[\lim_{j\to\infty} T'(\frac{n}{G(n)^{j}}) = T'(0)\]
 has a cardinality greater than or equal to $\textit{1TAPE}[T'(n)]$.
@@
 Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}.
-In general, we can assume the same result for every sparse function $T(n)$.
+In general, we can assume the same result for every sparse function $T(n)$ when $T(n)$ is not a constant.
 \end{proof}

### 2019-11-12 doc/manuscript.tex
Updated the content proof

@@
 \[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
-in their paper \cite{HM81}. Consequently, this is a result of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
+in their paper \cite{HM81}.
+We can extend this result when $T(n)$ is not a constant \cite{HM81}.
+Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
 \end{proof}
@@
 
-On the one hand, every language in $L_{1} \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$.
+On the one hand, every language in $L' \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$.
 The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance.
@@
 
-On the other hand, every language in $L_{2} \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$.
+On the other hand, every language in $L'' \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$.
 The reason is simple, because the Turing machine $N$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance.

### 2019-11-13 doc/manuscript.tex
Updated the content proof

@@
 
-\section{Materials and Methods}
-
-\subsection{Preliminaries}
+\section{Preliminaries}
 
@@
 
-\subsection{Hypothesis}
+\section{Hypothesis}
 
@@
 
-\subsection{Consequences}
+\section{Consequences}
 
@@
 \[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
-and is not a constant, then $\textit{1TAPE}[T(n)]$ is closed under deterministic two-way logarithmic space reduction.
+then $\textit{1TAPE}[T(n)]$ is closed under deterministic two-way logarithmic space reduction.
 \end{theorem}
@@
 \begin{proof}
-Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some $T'(n)$ that is not a constant when
+Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some $T'(n)$ when
 \[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\]
@@
 This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $G(n) \times n$.
+
 However, we know in that instance of size at most $G(n) \times n$, we can replace the deterministic two-way logarithmic space reduction by a deterministic one-way logarithmic space reduction that read contiguously from left-to-right.
 Therefore, the instance of size at most $G(n) \times n$ could be decided by a deterministic one-way logarithmic space Turing machine that simulates the two-way logarithmic space reduction with at most $H(n)$ in the work tapes within the composition on the another deterministic one-way logarithmic space Turing machine which is used in $\textit{1TAPE}[T'(n) - H(n)]$ after the deterministic two-way logarithmic space reduction of the original language.
-In this way, we obtain that the family of languages of $\textit{1TAPE}[T'(n)]$ has a projection to the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction.
+
+In this way, we obtain that the languages in $\textit{1TAPE}[T'(n)]$ have a projection to the languages in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction.
 As result, we obtain that the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$.
-Recursively, we obtain that the family of languages of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ has a projection to the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)^{2}})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction.
-Consequently, we obtain that the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)^{2}})]$.
-If we recursively continue so forth, then we obtain that the cardinality of the family of languages $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)^{j}})]$ for every natural number $j$.
-However, if we follow this assumption, then we obtain that
-\[\lim_{j\to\infty} T'(\frac{n}{G(n)^{j}}) = T'(0)\]
-has a cardinality greater than or equal to $\textit{1TAPE}[T'(n)]$.
-Nevertheless, the cardinality of the family of languages $\textit{1TAPE}[T'(n)]$ cannot be lesser than or equal to the cardinality of family of languages $\textit{1TAPE}[T'(0)]$ just assuming that $T'(n)$ is not a constant.
+However, we already know that $\textit{1TAPE}[T'(\frac{n}{G(n)})] \subseteq \textit{1TAPE}[T'(n)]$ and thus, if the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$, then we have that $\textit{1TAPE}[T'(\frac{n}{G(n)})] = \textit{1TAPE}[T'(n)]$.
+Nevertheless, we know that the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ cannot be equal to the family of languages $\textit{1TAPE}[T'(n)]$ for some function $G(n) > 1$.
 Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}.
-In general, we can assume the same result for every sparse function $T(n)$ when $T(n)$ is not a constant.
+In general, we can assume the same result for every function $T(n)$ with small amount of work tape.
 \end{proof}
@@
 \[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
-in their paper \cite{HM81}.
-We can extend this result when $T(n)$ is not a constant \cite{HM81}.
-Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
+in their paper \cite{HM81}. Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
 \end{proof}
@@
 
-\subsection{Programming Codes}
+\section{Codes}
 

### 2019-11-14 doc/manuscript.tex
Updated finally the content proof
Updated the content proof

@@
 \label{closed}
-If $T(n)$ is such that
+If $T(n)$ is a monotone increasing function such that
 \[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
@@
 \begin{proof}
-Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some $T'(n)$ when
+Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some monotone increasing function $T'(n)$ when
 \[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\]
@@
 As result, we obtain that the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$.
-However, we already know that $\textit{1TAPE}[T'(\frac{n}{G(n)})] \subseteq \textit{1TAPE}[T'(n)]$ and thus, if the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$, then we have that $\textit{1TAPE}[T'(\frac{n}{G(n)})] = \textit{1TAPE}[T'(n)]$.
-Nevertheless, we know that the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ cannot be equal to the family of languages $\textit{1TAPE}[T'(n)]$ for some function $G(n) > 1$.
+However, we already know that $\textit{1TAPE}[T'(\frac{n}{G(n)})] \subseteq \textit{1TAPE}[T'(n)]$ since $T'(n)$ is a monotone increasing function and thus, if the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$, then we have that $\textit{1TAPE}[T'(\frac{n}{G(n)})] = \textit{1TAPE}[T'(n)]$.
+
+Nevertheless, the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ cannot be equal to the family of languages $\textit{1TAPE}[T'(n)]$ for some function $G(n) > 1$.
+Certainly, for a sufficiently large instance of size $n$, then we could finish all the amount of possible configurations during the computation in a deterministic one-way Turing machines with $T'(\frac{n}{G(n)})$ work tape, whereas we could still compute more configurations in a deterministic one-way Turing machines with $T'(n)$ work tape for the same instance because of $T'(\frac{n}{G(n)}) < T'(n)$.
+Indeed, there are languages in $\textit{1TAPE}[T'(n)]$ that cannot be decided in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ due to the lack of computational space for the acceptance or rejection of the instances.
 Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}.
-In general, we can assume the same result for every function $T(n)$ with small amount of work tape.
+In general, we can assume the same result for every small amount of work tape $T(n)$ when $T(n)$ is a monotone increasing function.
 \end{proof}
@@
 \[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
-in their paper \cite{HM81}. Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
+in their paper \cite{HM81}.
+We can use this result when $T(n)$ is a monotone increasing function as well \cite{HM81}.
+Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
 \end{proof}

### 2019-11-14 doc/manuscript.tex
Updated the content proof

--- 2019-11-13 doc/manuscript.tex
@@
 Let $\textit{1TAPE}[T(n)]$ denote the family of languages accepted by deterministic one-way Turing machines with $T(n)$ work tape \cite{HM81}.
+A monotonically increasing function $f$ is not a constant and for every two values $x < y$ in the domain of $f$, then we obtain that $f(x) \leq f(y)$.
 
@@
 \label{closed}
-If $T(n)$ is such that
+If $T(n)$ is a monotonically increasing function such that
 \[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
@@
 \begin{proof}
-Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some $T'(n)$ when
+Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some monotonically increasing function $T'(n)$ when
 \[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\]
@@
 This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $G(n) \times n$.
+We could complete the end of the instance of size at most $G(n) \times n$ with the symbols that were not read during the deterministic two-way logarithmic space reduction just in the same order that appear in the original instance of size $n$.
 
@@
 
-In this way, we obtain that the languages in $\textit{1TAPE}[T'(n)]$ have a projection to the languages in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction.
+In this way, we obtain that every language in $\textit{1TAPE}[T'(n)]$ has a mapping to a corresponding language in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction.
 As result, we obtain that the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$.
-However, we already know that $\textit{1TAPE}[T'(\frac{n}{G(n)})] \subseteq \textit{1TAPE}[T'(n)]$ and thus, if the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$, then we have that $\textit{1TAPE}[T'(\frac{n}{G(n)})] = \textit{1TAPE}[T'(n)]$.
-Nevertheless, we know that the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ cannot be equal to the family of languages $\textit{1TAPE}[T'(n)]$ for some function $G(n) > 1$.
+However, we already know that $\textit{1TAPE}[T'(\frac{n}{G(n)})] \subseteq \textit{1TAPE}[T'(n)]$ since $T'(n)$ is a monotonically increasing function and thus, if the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$, then we have that $\textit{1TAPE}[T'(\frac{n}{G(n)})] = \textit{1TAPE}[T'(n)]$.
+
+Nevertheless, the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ cannot be equal to the family of languages $\textit{1TAPE}[T'(n)]$ for some function $G(n) > 1$.
+Certainly, for a sufficiently large instance of size $n$, then we can consume all the amount of possible configurations during the computation in a deterministic one-way Turing machines with $T'(\frac{n}{G(n)})$ work tape, whereas we could still compute more configurations in a deterministic one-way Turing machines with $T'(n)$ work tape for the same instance because of $T'(\frac{n}{G(n)}) < T'(n)$.
+Indeed, there are languages in $\textit{1TAPE}[T'(n)]$ that cannot be decided in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ due to the lack of computational space for the acceptance or rejection of the instances.
 Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}.
-In general, we can assume the same result for every function $T(n)$ with small amount of work tape.
+In general, we can assume the same result for every small amount of work tape $T(n)$ when $T(n)$ is a monotonically increasing function.
 \end{proof}
@@
 \[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
-in their paper \cite{HM81}. Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
+in their paper \cite{HM81}.
+We can use this result when $T(n)$ is a monotonically increasing function as well \cite{HM81}.
+Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
 \end{proof}
@@
 
-\section{Codes}
+\section{Programming Codes}
 

### 2019-11-14 doc/manuscript.tex
Updated the content proof

@@
 Nevertheless, the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ cannot be equal to the family of languages $\textit{1TAPE}[T'(n)]$ for some function $G(n) > 1$.
-Certainly, for a sufficiently large instance of size $n$, then we can consume all the amount of possible configurations during the computation in a deterministic one-way Turing machines with $T'(\frac{n}{G(n)})$ work tape, whereas we could still compute more configurations in a deterministic one-way Turing machines with $T'(n)$ work tape for the same instance because of $T'(\frac{n}{G(n)}) < T'(n)$.
+Certainly, for a sufficiently large instance of size $n$, then we can consume all the amount of possible configurations during the computation in a deterministic one-way Turing machines with $T'(\frac{n}{G(n)})$ work tape, whereas we could still compute more configurations in a deterministic one-way Turing machines with $T'(n)$ work tape for the same instance.
 Indeed, there are languages in $\textit{1TAPE}[T'(n)]$ that cannot be decided in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ due to the lack of computational space for the acceptance or rejection of the instances.

### 2019-11-14 doc/manuscript.tex
Updated the content proof

--- 2019-11-14 doc/manuscript.tex
@@
 Let $\textit{1TAPE}[T(n)]$ denote the family of languages accepted by deterministic one-way Turing machines with $T(n)$ work tape \cite{HM81}.
-A monotonically increasing function $f$ is not a constant and for every two values $x < y$ in the domain of $f$, then we obtain that $f(x) \leq f(y)$.
+A strictly monotonically increasing function $f$ complies for every two values $x < y$ in the domain of $f$, then we obtain that $f(x) < f(y)$.
 
@@
 \label{closed}
-If $T(n)$ is a monotonically increasing function such that
+If $T(n)$ is a strictly monotonically increasing function such that
 \[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
@@
 \begin{proof}
-Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some monotonically increasing function $T'(n)$ when
+Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some strictly monotonically increasing function $T'(n)$ when
 \[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\]
@@
 As result, we obtain that the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$.
-However, we already know that $\textit{1TAPE}[T'(\frac{n}{G(n)})] \subseteq \textit{1TAPE}[T'(n)]$ since $T'(n)$ is a monotonically increasing function and thus, if the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$, then we have that $\textit{1TAPE}[T'(\frac{n}{G(n)})] = \textit{1TAPE}[T'(n)]$.
+However, we already know that $\textit{1TAPE}[T'(\frac{n}{G(n)})] \subseteq \textit{1TAPE}[T'(n)]$ since $T'(n)$ is a strictly monotonically increasing function and thus, if the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$, then we have that $\textit{1TAPE}[T'(\frac{n}{G(n)})] = \textit{1TAPE}[T'(n)]$.
 
@@
 Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}.
-In general, we can assume the same result for every small amount of work tape $T(n)$ when $T(n)$ is a monotonically increasing function.
+In general, we can assume the same result for every small amount of work tape $T(n)$ when $T(n)$ is a strictly monotonically increasing function.
 \end{proof}
@@
 in their paper \cite{HM81}.
-We can use this result when $T(n)$ is a monotonically increasing function as well \cite{HM81}.
+We can use this result when $T(n)$ is a strictly monotonically increasing function as well \cite{HM81}.
 Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.

### 2019-11-14 doc/manuscript.tex
Fixed the content proof

--- 2019-11-14 doc/manuscript.tex
@@
 
+\begin{definition}
+The class $1LNL$ contains those languages that are decided by a nondeterministic one-way logarithmic space Turing machine $N$ such that for every instance $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves deterministically on $y$ and nondeterministically on $z$.
+\end{definition}
+
+\begin{theorem}
+\label{partially}
+$|1LNL|_{c} > |1L|_{c}$ where $|\ldots|_{c}$ denotes the cardinality. 
+\end{theorem}
+
+\begin{proof}
+On the one hand, if we suppose that $|1NL|_{c} \neq |1L|_{c}$, then we obtain directly that $|1LNL|_{c} > |1L|_{c}$ since $1L \varsubsetneq 1NL$ and $1LNL$ contains $1NL$, because the prefix $y$ of the instance $x = yz$ could be the empty string.
+On the other hand, if we suppose that $|1NL|_{c} = |1L|_{c}$, then we can make a bijective relation between a language $L' \in 1L$ and another language $L'' \in 1NL$.
+Hence, we can create the languages $L''' \in 1LNL$ such that
+\[L''' =\{yz: y \in L' \textit{ and } z \in L''\}\]
+where  $L' \in 1L$ and $L'' \in 1NL$ are the languages that are linked in our bijective relation.
+In this way, we can create a bijective relation between these languages $L''' \in 1LNL$ and the corresponding language $L' \in 1L$.
+However, the set $S$ of all these languages $L''' \in 1LNL$ is a proper subset of $1LNL$, because there are languages in $1LNL$ such that they are not in $S$.
+Nevertheless, we have that $|S|_{c} = |1L|_{c}$ since there is a bijective relation between these two sets, but we know that $S \varsubsetneq 1LNL$ and thus, $|1LNL|_{c} > |1L|_{c}$.
+\end{proof}
+
 Now, we define two classes defined under $\textit{L--reduction}$ and $\textit{NL--reduction}$, respectively.
@@
 \end{definition}
-
-Let $\textit{1TAPE}[T(n)]$ denote the family of languages accepted by deterministic one-way Turing machines with $T(n)$ work tape \cite{HM81}.
-A monotonically increasing function $f$ is not a constant and for every two values $x < y$ in the domain of $f$, then we obtain that $f(x) \leq f(y)$.
-
-\begin{theorem}
-\label{closed}
-If $T(n)$ is a monotonically increasing function such that
-\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
-then $\textit{1TAPE}[T(n)]$ is closed under deterministic two-way logarithmic space reduction.
-\end{theorem}
-
-\begin{proof}
-Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some monotonically increasing function $T'(n)$ when
-\[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\]
-Hence, the family of languages $\textit{1TAPE}[T'(n)]$ is two-way logarithmic space reduced to the another family of languages $\textit{1TAPE}[T'(n) - H(n)]$ where the deterministic two-way logarithmic space reduction consumes at most $H(n)$ in the work tapes.
-Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $G(n) \times n$ symbols for some function $G(n) > 1$, that is the result of reading consecutively the symbols in the input tape in a sequential way.
-The existence of such function $G(n) > 1$ is possible because the family of languages $\textit{1TAPE}[T'(n)]$ is a subset of $P$ and thus $G(n) < 2^{n}$ \cite{Pap03}.
-This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $G(n) \times n$.
-We could complete the end of the instance of size at most $G(n) \times n$ with the symbols that were not read during the deterministic two-way logarithmic space reduction just in the same order that appear in the original instance of size $n$.
-
-However, we know in that instance of size at most $G(n) \times n$, we can replace the deterministic two-way logarithmic space reduction by a deterministic one-way logarithmic space reduction that read contiguously from left-to-right.
-Therefore, the instance of size at most $G(n) \times n$ could be decided by a deterministic one-way logarithmic space Turing machine that simulates the two-way logarithmic space reduction with at most $H(n)$ in the work tapes within the composition on the another deterministic one-way logarithmic space Turing machine which is used in $\textit{1TAPE}[T'(n) - H(n)]$ after the deterministic two-way logarithmic space reduction of the original language.
-
-In this way, we obtain that every language in $\textit{1TAPE}[T'(n)]$ has a mapping to a corresponding language in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction.
-As result, we obtain that the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$.
-However, we already know that $\textit{1TAPE}[T'(\frac{n}{G(n)})] \subseteq \textit{1TAPE}[T'(n)]$ since $T'(n)$ is a monotonically increasing function and thus, if the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$, then we have that $\textit{1TAPE}[T'(\frac{n}{G(n)})] = \textit{1TAPE}[T'(n)]$.
-
-Nevertheless, the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ cannot be equal to the family of languages $\textit{1TAPE}[T'(n)]$ for some function $G(n) > 1$.
-Certainly, for a sufficiently large instance of size $n$, then we can consume all the amount of possible configurations during the computation in a deterministic one-way Turing machines with $T'(\frac{n}{G(n)})$ work tape, whereas we could still compute more configurations in a deterministic one-way Turing machines with $T'(n)$ work tape for the same instance.
-Indeed, there are languages in $\textit{1TAPE}[T'(n)]$ that cannot be decided in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ due to the lack of computational space for the acceptance or rejection of the instances.
-Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}.
-In general, we can assume the same result for every small amount of work tape $T(n)$ when $T(n)$ is a monotonically increasing function.
-\end{proof}
-
-\begin{theorem}
-\label{partially}
-$1L \neq 1NL$ under deterministic two-way logarithmic space reduction.
-\end{theorem}
-
-\begin{proof}
-Hartmanis and Mahaney have shown that $1NL \varsubsetneq \textit{1TAPE}[T(n)]$ when
-\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
-in their paper \cite{HM81}.
-We can use this result when $T(n)$ is a monotonically increasing function as well \cite{HM81}.
-Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
-\end{proof}
 
@@
 On the other hand, every language in $L'' \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$.
-The reason is simple, because the Turing machine $N$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance.
+The reason is also simple, because the Turing machine $N$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance.
 Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way.
@@
 
-In this way, if $L = NL$ then $2L = 2NL$.
-However, we know that $2L \neq 2NL$ because of $1L \neq 1NL$ under deterministic two-way logarithmic space reduction according to the Theorem \ref{partially}.
-Indeed, in case of $2L = 2NL$, then every language in $1NL$ is deterministic two-way logarithmic space reduced to a language in $1L$ and viceversa.
+As result, $L = NL$ if and only if $2L = 2NL$. We define the class $LNL$ as the languages
+\[L' =\{yz: y \in L \textit{ and } z \in NL\}.\]
+Therefore, we can deterministic logarithmic space reduce every language $L' \in LNL$ to a language $L_{1} \in 1LNL$ or to a language in $L_{2} \in 1L$ when $L = NL$.
+In this way, we can make a relation between every language $L_{1} \in 1LNL$ to another language $L_{2} \in 1L$.
+We can slightly modify this relation to create a new bijective relation just enumerating the languages $L_{i} \in 1LNL$ with a unique and natural number $i$ such that the relation is now with the corresponding language $L_{2, i}$ where
+\[L_{2, i} = \{i \sqcup j: j \in L_{2}\}\]
+and $\sqcup$ is the blank symbol \cite{Pap03}.
+We can make this because $1LNL$ is enumerable due to $P$ is enumerable and $1LNL \subseteq P$ \cite{Pap03}.
+However, we know for every natural number $i$ that $L_{2, i}$ belongs to $1L$, since $L_{2} \in 1L$ and we can check in a deterministic one-way computation the nonempty prefix substring $i$ without using any amount of space in the work tapes.
+Hence, we obtain that $|1LNL|_{c} < |1L|_{c}$ using this modified relation.
+However, this is not possible according to the Theorem \ref{partially}.
 Consequently, we prove the complexity class $L$ is not equal to $NL$.
@@
 
-The economy would become vastly more efficient.
-There would be disruption, including maybe displacing programmers \cite{IMP95}.
-The practice of programming itself would be more about gathering training data and less about writing code \cite{IMP95}.
-Google would have the resources to excel in such a world \cite{IMP95}.
-
 But such changes may pale in significance compared to the revolution an efficient method for solving $\textit{NP--complete}$ problems will cause in mathematics itself.

### 2019-11-15 doc/manuscript.tex
Fixed the content proof

@@
 On the one hand, if we suppose that $|1NL|_{c} \neq |1L|_{c}$, then we obtain directly that $|1LNL|_{c} > |1L|_{c}$ since $1L \varsubsetneq 1NL$ and $1LNL$ contains $1NL$, because the prefix $y$ of the instance $x = yz$ could be the empty string.
-On the other hand, if we suppose that $|1NL|_{c} = |1L|_{c}$, then we can make a bijective relation between a language $L' \in 1L$ and another language $L'' \in 1NL$.
+On the other hand, if we suppose that $|1NL|_{c} = |1L|_{c}$, then we can make a bijective relation between a language $L' \in 1L$ and a language $L'' \in 1NL$.
 Hence, we can create the languages $L''' \in 1LNL$ such that
@@
 As result, $L = NL$ if and only if $2L = 2NL$. We define the class $LNL$ as the languages
-\[L' =\{yz: y \in L \textit{ and } z \in NL\}.\]
-Therefore, we can deterministic logarithmic space reduce every language $L' \in LNL$ to a language $L_{1} \in 1LNL$ or to a language in $L_{2} \in 1L$ when $L = NL$.
-In this way, we can make a relation between every language $L_{1} \in 1LNL$ to another language $L_{2} \in 1L$.
+\[L''' =\{yz: y \in L' \textit{ and } z \in L'' \textit{ such that } L' \in L \textit{ and } L'' \in NL\}.\]
+Therefore, we can deterministic logarithmic space reduce every language $L''' \in LNL$ to a language $L_{1} \in 1LNL$ or to a language in $L_{2} \in 1L$ when $L = NL$.
+In this way, we can make a relation between every language $L_{1} \in 1LNL$ to a language $L_{2} \in 1L$.
 We can slightly modify this relation to create a new bijective relation just enumerating the languages $L_{i} \in 1LNL$ with a unique and natural number $i$ such that the relation is now with the corresponding language $L_{2, i}$ where
@@
 and $\sqcup$ is the blank symbol \cite{Pap03}.
-We can make this because $1LNL$ is enumerable due to $P$ is enumerable and $1LNL \subseteq P$ \cite{Pap03}.
+We can make this because $1LNL$ is enumerable due to $P$ is also enumerable and $1LNL \subseteq P$ \cite{Pap03}.
 However, we know for every natural number $i$ that $L_{2, i}$ belongs to $1L$, since $L_{2} \in 1L$ and we can check in a deterministic one-way computation the nonempty prefix substring $i$ without using any amount of space in the work tapes.
-Hence, we obtain that $|1LNL|_{c} < |1L|_{c}$ using this modified relation.
+Hence, we obtain that $|1LNL|_{c} < |1L|_{c}$ using this modified relation which is bijective, because there are languages in $1L$ such that the instances do not contain the blank symbol.
 However, this is not possible according to the Theorem \ref{partially}.
@@
 
+The economy would become vastly more efficient.
+There would be disruption, including maybe displacing programmers \cite{IMP95}.
+The practice of programming itself would be more about gathering training data and less about writing code \cite{IMP95}.
+Google would have the resources to excel in such a world \cite{IMP95}.
+
 But such changes may pale in significance compared to the revolution an efficient method for solving $\textit{NP--complete}$ problems will cause in mathematics itself.

### 2019-11-15 doc/manuscript.tex
Fixed the content proof

@@
 
-On the one hand, every language in $L' \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$.
+On the one hand, every language $L' \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$.
 The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance.
@@
 
-On the other hand, every language in $L'' \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$.
+On the other hand, every language $L'' \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$.
 The reason is also simple, because the Turing machine $N$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance.
@@
 \[L''' =\{yz: y \in L' \textit{ and } z \in L'' \textit{ such that } L' \in L \textit{ and } L'' \in NL\}.\]
-Therefore, we can deterministic logarithmic space reduce every language $L''' \in LNL$ to a language $L_{1} \in 1LNL$ or to a language in $L_{2} \in 1L$ when $L = NL$.
+Therefore, we can deterministic logarithmic space reduce every language $L''' \in LNL$ to a language $L_{1} \in 1LNL$ or to a language $L_{2} \in 1L$ when $L = NL$.
 In this way, we can make a relation between every language $L_{1} \in 1LNL$ to a language $L_{2} \in 1L$.

### 2019-11-15 doc/manuscript.tex
Finally updated content proof

@@
 \label{partially}
-$|1LNL|_{c} > |1L|_{c}$ where $|\ldots|_{c}$ denotes the cardinality.
+$|1NL|_{c} > |1L|_{c}$ where $|\ldots|_{c}$ denotes the cardinality.
 \end{theorem}
@@
 \begin{proof}
-On the one hand, if we suppose that $|1NL|_{c} \neq |1L|_{c}$, then we obtain directly that $|1LNL|_{c} > |1L|_{c}$ since $1L \varsubsetneq 1NL$ and $1LNL$ contains $1NL$, because the prefix $y$ of the instance $x = yz$ could be the empty string.
+On the one hand, if we suppose that $|1NL|_{c} \neq |1L|_{c}$, then we obtain directly that $|1NL|_{c} > |1L|_{c}$ because of $1L \varsubsetneq 1NL$ \cite{HM81}.
 On the other hand, if we suppose that $|1NL|_{c} = |1L|_{c}$, then we can make a bijective relation between a language $L' \in 1L$ and a language $L'' \in 1NL$.
@@
 Nevertheless, we have that $|S|_{c} = |1L|_{c}$ since there is a bijective relation between these two sets, but we know that $S \varsubsetneq 1LNL$ and thus, $|1LNL|_{c} > |1L|_{c}$.
+
+In addition, we obtain that $1NL \subseteq 1LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string.
+Moreover, we have that $1LNL \subseteq 1NL$, because the languages in $1LNL$ are decided by nondeterministic one-way logarithmic space Turing machines.
+In this way, the complexity class $1LNL$ is equal to $1NL$ and thus, we obtain the contradiction that $|1NL|_{c} > |1L|_{c}$ and $|1NL|_{c} = |1L|_{c}$ at the same time.
+Consequently, the statement $|1NL|_{c} > |1L|_{c}$ must be true by the reductio ad absurdum logic rule \cite{FE16}.
 \end{proof}
@@
 
-As result, $L = NL$ if and only if $2L = 2NL$. We define the class $LNL$ as the languages
-\[L''' =\{yz: y \in L' \textit{ and } z \in L'' \textit{ such that } L' \in L \textit{ and } L'' \in NL\}.\]
-Therefore, we can deterministic logarithmic space reduce every language $L''' \in LNL$ to a language $L_{1} \in 1LNL$ or to a language $L_{2} \in 1L$ when $L = NL$.
-In this way, we can make a relation between every language $L_{1} \in 1LNL$ to a language $L_{2} \in 1L$.
-We can slightly modify this relation to create a new bijective relation just enumerating the languages $L_{i} \in 1LNL$ with a unique and natural number $i$ such that the relation is now with the corresponding language $L_{2, i}$ where
+As result, $L = NL$ if and only if $2L = 2NL$.
+Therefore, we can deterministic logarithmic space reduce every language $L_{1} \in 1NL$ to a language $L_{2} \in 1L$ when $L = NL$.
+In this way, we can make a relation between every language $L_{1} \in 1NL$ to a language $L_{2} \in 1L$.
+We can slightly modify this relation to create a new bijective relation just enumerating the languages $L_{i} \in 1NL$ with a unique and natural number $i$ such that the relation is now with the corresponding language $L_{2, i}$ where
 \[L_{2, i} = \{i \sqcup j: j \in L_{2}\}\]
 and $\sqcup$ is the blank symbol \cite{Pap03}.
-We can make this because $1LNL$ is enumerable due to $P$ is also enumerable and $1LNL \subseteq P$ \cite{Pap03}.
+We can make this because $1NL$ is enumerable due to $P$ is also enumerable and $1NL \subseteq P$ \cite{Pap03}.
 However, we know for every natural number $i$ that $L_{2, i}$ belongs to $1L$, since $L_{2} \in 1L$ and we can check in a deterministic one-way computation the nonempty prefix substring $i$ without using any amount of space in the work tapes.
-Hence, we obtain that $|1LNL|_{c} < |1L|_{c}$ using this modified relation which is bijective, because there are languages in $1L$ such that the instances do not contain the blank symbol.
+Hence, we obtain that $|1NL|_{c} < |1L|_{c}$ using this modified relation which is bijective, because there are languages in $1L$ such that the instances do not contain the blank symbol.
 However, this is not possible according to the Theorem \ref{partially}.

### 2019-11-15 doc/manuscript.tex
Updated amazing result

--- 2019-11-15 doc/manuscript.tex
@@
 
-\section{Preliminaries}
+\section{Theory and Methods}
+
+\subsection{Preliminaries}
 
@@
 \begin{definition}
-The class $1LNL$ contains those languages that are decided by a nondeterministic one-way logarithmic space Turing machine $N$ such that for every instance $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves deterministically on $y$ and nondeterministically on $z$.
+\label{definition}
+The class $LNL$ contains those languages that are decided by a nondeterministic logarithmic space Turing machine $N$ such that for every instance $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves strictly deterministically on $y$ and strictly nondeterministically on $z$ while strictly deterministically means there is no a possible nondeterministic step and strictly nondeterministically means there is at least one nondeterministic step.
 \end{definition}
 
-\begin{theorem}
-\label{partially}
-$|1LNL|_{c} > |1L|_{c}$ where $|\ldots|_{c}$ denotes the cardinality.
-\end{theorem}
-
-\begin{proof}
-On the one hand, if we suppose that $|1NL|_{c} \neq |1L|_{c}$, then we obtain directly that $|1LNL|_{c} > |1L|_{c}$ since $1L \varsubsetneq 1NL$ and $1LNL$ contains $1NL$, because the prefix $y$ of the instance $x = yz$ could be the empty string.
-On the other hand, if we suppose that $|1NL|_{c} = |1L|_{c}$, then we can make a bijective relation between a language $L' \in 1L$ and a language $L'' \in 1NL$.
-Hence, we can create the languages $L''' \in 1LNL$ such that
-\[L''' =\{yz: y \in L' \textit{ and } z \in L''\}\]
-where  $L' \in 1L$ and $L'' \in 1NL$ are the languages that are linked in our bijective relation.
-In this way, we can create a bijective relation between these languages $L''' \in 1LNL$ and the corresponding language $L' \in 1L$.
-However, the set $S$ of all these languages $L''' \in 1LNL$ is a proper subset of $1LNL$, because there are languages in $1LNL$ such that they are not in $S$.
-Nevertheless, we have that $|S|_{c} = |1L|_{c}$ since there is a bijective relation between these two sets, but we know that $S \varsubsetneq 1LNL$ and thus, $|1LNL|_{c} > |1L|_{c}$.
-\end{proof}
-
-Now, we define two classes defined under $\textit{L--reduction}$ and $\textit{NL--reduction}$, respectively.
-
-\begin{definition}
-The class $2L$ contains those languages that are deterministic logarithmic space reduced to a language in $1L$.
-The class $2NL$ consists in those languages that are nondeterministic logarithmic space reduced to a language in $1NL$.
-\end{definition}
+Sauerhoff have shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input (``nondeterminism at the beginning") \cite{MS03}.
 
@@
 \begin{proof}
-We obtain that $2L \subseteq L$ and $2NL \subseteq NL$ by the definition of $L$ and $NL$ under the $\textit{L--reduction}$ and $\textit{NL--reduction}$, respectively.
-Certainly, since the output string will be in $1L$ or $1NL$, then we do not need to reset the computation of the $\textit{L--reduction}$ or $\textit{NL--reduction}$ in order to be decided by a deterministic or nondeterministic logarithmic space Turing machine under logarithmic space composition, respectively.
-
-On the one hand, every language $L' \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$.
-The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance.
-Indeed, for every read symbol in the input tape in $M$, then this is written to the output tape in a sequential way.
-In this way, the output string could be accepted by a deterministic one-way logarithmic space Turing machine, that would be the same Turing machine $M$ where this one will always read on the input tape from left-to-right.
-Certainly, when $M$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right.
-Consequently, $M$ in case of acceptance will output the strings that consist in a language in $1L$.
-Hence, we obtain that $L \subseteq 2L$.
-Since we already know that $2L \subseteq L$, then $L = 2L$.
-
-On the other hand, every language $L'' \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$.
-The reason is also simple, because the Turing machine $N$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance.
-Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way.
-In this way, the output string could be accepted by a nondeterministic one-way logarithmic space Turing machine, that would be the same Turing machine $N$ where this one will always read on the input tape from left-to-right.
-Certainly, when $N$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right.
-Consequently, $N$ in case of acceptance will output the strings that consist in a language in $1NL$.
-Hence, we obtain that $NL \subseteq 2NL$.
-Since we already know that $2NL \subseteq NL$, then $NL = 2NL$.
-
-As result, $L = NL$ if and only if $2L = 2NL$. We define the class $LNL$ as the languages
-\[L''' =\{yz: y \in L' \textit{ and } z \in L'' \textit{ such that } L' \in L \textit{ and } L'' \in NL\}.\]
-Therefore, we can deterministic logarithmic space reduce every language $L''' \in LNL$ to a language $L_{1} \in 1LNL$ or to a language $L_{2} \in 1L$ when $L = NL$.
-In this way, we can make a relation between every language $L_{1} \in 1LNL$ to a language $L_{2} \in 1L$.
-We can slightly modify this relation to create a new bijective relation just enumerating the languages $L_{i} \in 1LNL$ with a unique and natural number $i$ such that the relation is now with the corresponding language $L_{2, i}$ where
-\[L_{2, i} = \{i \sqcup j: j \in L_{2}\}\]
-and $\sqcup$ is the blank symbol \cite{Pap03}.
-We can make this because $1LNL$ is enumerable due to $P$ is also enumerable and $1LNL \subseteq P$ \cite{Pap03}.
-However, we know for every natural number $i$ that $L_{2, i}$ belongs to $1L$, since $L_{2} \in 1L$ and we can check in a deterministic one-way computation the nonempty prefix substring $i$ without using any amount of space in the work tapes.
-Hence, we obtain that $|1LNL|_{c} < |1L|_{c}$ using this modified relation which is bijective, because there are languages in $1L$ such that the instances do not contain the blank symbol.
-However, this is not possible according to the Theorem \ref{partially}.
+We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string.
+Certainly, the languages in the class $L \subseteq NL$ could be decided by nondeterministic logarithmic space Turing machines that exactly do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the instances $x = yz$).
+Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines.
+Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$.
+However, we can state that $BNL \neq LNL$, because there is no possible way for an instance $x = yz$ when the prefix $y$ is the empty string in some languages in $BNL$, such that we could move strictly nondeterministically on $y$ (that would be a ``nondeterminism at the beginning") and move strictly deterministically on the nonempty string $z$ over the Definition \ref{definition} of $LNL$.
+Hence, we obtain that $BNL \neq NL$ by transitivity.
+Nevertheless, Sauerhoff have also shown that $L \subseteq BNL \subseteq NL$ \cite{MS03}.
 Consequently, we prove the complexity class $L$ is not equal to $NL$.
@@
 
-\section{Programming Codes}
+\subsection{Codes}
 

### 2019-11-16 doc/manuscript.tex
Fixed some details in doc

@@
 \label{definition}
-The class $LNL$ contains those languages that are decided by a nondeterministic logarithmic space Turing machine $N$ such that for every instance $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves strictly deterministically on $y$ and strictly nondeterministically on $z$ while strictly deterministically means there is no a possible nondeterministic step and strictly nondeterministically means there is at least one nondeterministic step.
+The class $LNL$ contains those languages that are decided by a nondeterministic logarithmic space Turing machine $N$ such that for every instance $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves strictly deterministically on $y$ and strictly nondeterministically on $z$ when strictly deterministically means there is no a possible nondeterministic step and strictly nondeterministically means there is at least one nondeterministic step on the computation.
 \end{definition}
 
-Sauerhoff have shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input (``nondeterminism at the beginning") \cite{MS03}.
+Sauerhoff has shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input (``nondeterminism at the beginning") \cite{MS03}.
 
@@
 We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string.
-Certainly, the languages in the class $L \subseteq NL$ could be decided by nondeterministic logarithmic space Turing machines that exactly do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the instances $x = yz$).
+Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the instances $x = yz$).
 Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines.
 Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$.
-However, we can state that $BNL \neq LNL$, because there is no possible way for an instance $x = yz$ when the prefix $y$ is the empty string in some languages in $BNL$, such that we could move strictly nondeterministically on $y$ (that would be a ``nondeterminism at the beginning") and move strictly deterministically on the nonempty string $z$ over the Definition \ref{definition} of $LNL$.
+However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an instance $x = yz$ when the prefix $y$ is the empty string in some languages in $BNL$, such that we could move strictly nondeterministically on $y$ (that would be a ``nondeterminism at the beginning") and move strictly deterministically on the nonempty string $z$.
 Hence, we obtain that $BNL \neq NL$ by transitivity.
-Nevertheless, Sauerhoff have also shown that $L \subseteq BNL \subseteq NL$ \cite{MS03}.
+Nevertheless, Sauerhoff has also shown that $L \subseteq BNL \subseteq NL$ \cite{MS03}.
 Consequently, we prove the complexity class $L$ is not equal to $NL$.

### 2019-11-16 doc/manuscript.tex
Updated content proof
Fixed the proof and project doc

@@
 The logarithmic space reduction is frequently used for $L$ and $NL$ \cite{Pap03}.
-On the one hand, we call the deterministic logarithmic space reduction as $\textit{L--reduction}$.
-On the other hand, we call the nondeterministic logarithmic space reduction as $\textit{NL--reduction}$.
-
 A Boolean formula is in 2-conjunctive normal form, or $2CNF$, if it is in $CNF$ and each clause has exactly two distinct literals.
@@
 \label{definition}
-The class $LNL$ contains those languages that are decided by a nondeterministic logarithmic space Turing machine $N$ such that for every instance $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves strictly deterministically on $y$ and strictly nondeterministically on $z$ when strictly deterministically means there is no a possible nondeterministic step and strictly nondeterministically means there is at least one nondeterministic step on the computation.
+The class $LNL$ contains those languages that are decided by a nondeterministic logarithmic space Turing machine $N$ such that for every element $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves strictly deterministically on $y$ and strictly nondeterministically on $z$ when strictly deterministically means there is no a possible nondeterministic step and strictly nondeterministically means there is at least one nondeterministic step on the computation.
 \end{definition}
@@
 We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string.
-Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the instances $x = yz$).
+Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the elements $x = yz$).
 Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines.
 Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$.
-However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an instance $x = yz$ when the prefix $y$ is the empty string in some languages in $BNL$, such that we could move strictly nondeterministically on $y$ (that would be a ``nondeterminism at the beginning") and move strictly deterministically on the nonempty string $z$.
+However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ when the prefix $y$ is the empty string in some languages in $BNL$, such that we could move strictly nondeterministically on $y$ (that would be a ``nondeterminism at the beginning") and move strictly deterministically on the nonempty string $z$.
 Hence, we obtain that $BNL \neq NL$ by transitivity.

### 2019-11-16 doc/manuscript.tex
Fixed style proof doc

@@
 In particular, it cannot reread any bit to the left of where the head currently is \cite{AB09}.
-For that reason this kind of special tape is called ``read once" \cite{AB09}.
+For that reason this kind of special tape is called $``$read once$"$ \cite{AB09}.
 
@@
 
-Sauerhoff has shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input (``nondeterminism at the beginning") \cite{MS03}.
+Sauerhoff has shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input ($``$nondeterminism at the beginning$"$) \cite{MS03}.
 
@@
 Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$.
-However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ when the prefix $y$ is the empty string in some languages in $BNL$, such that we could move strictly nondeterministically on $y$ (that would be a ``nondeterminism at the beginning") and move strictly deterministically on the nonempty string $z$.
+However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ when the prefix $y$ is the empty string in some languages in $BNL$, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$.
 Hence, we obtain that $BNL \neq NL$ by transitivity.

### 2019-11-17 doc/manuscript.tex
Improved the result

@@
 Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$.
-However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ when the prefix $y$ is the empty string in some languages in $BNL$, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$.
+However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ in some languages in $BNL$ when the prefix $y$ is the empty string, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$.
 Hence, we obtain that $BNL \neq NL$ by transitivity.

### 2019-11-17 doc/presentation.tex
Improved the result

@@
 \label{result}
-In our work was proved that we can define a $\textit{NP--complete}$ problem as
+In our work was proved that we can define an $\textit{NP--complete}$ problem as
 
@@
 
-\begin{frame}{The classes $2L$ and $2NL$}
+\begin{frame}{The complexity class $LNL$}
 
 \begin{definition}
-The class 2L contains those languages that are deterministic logarithmic space reduced to a language in 1L.
-The class 2NL consists in those languages that are nondeterministic logarithmic space reduced to a language in 1NL.
+\label{definition}
+The class $LNL$ contains those languages that are decided by a nondeterministic logarithmic space Turing machine $N$ such that for every element $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves strictly deterministically on $y$ and strictly nondeterministically on $z$ when strictly deterministically means there is no a possible nondeterministic step and strictly nondeterministically means there is at least one nondeterministic step on the computation.
 \end{definition}
@@
 
-\begin{frame}{Inclusion}
+\begin{frame}{The class $BNL$}
 
-We obtain that $2L \subseteq L$ and $2NL \subseteq NL$ by the definition of $L$ and $NL$ under the $\textit{L--reduction}$ and $\textit{NL--reduction}$, respectively.
-Certainly, since the output string will be in $1L$ or $1NL$, then we do not need to reset the computation of the $\textit{L--reduction}$ or $\textit{NL--reduction}$ in order to be decided by a deterministic or nondeterministic logarithmic space Turing machine under logarithmic space composition, respectively.
+Sauerhoff has shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input ($``$nondeterminism at the beginning$"$).
 
@@
 
-\begin{frame}{Proof of $L = 2L$: First part}
+\begin{frame}{Proof of $LNL = NL$}
 
-On the one hand, every language in $L' \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$.
-The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read continuously in the input tape during the whole computation in case of acceptance.
-Indeed, for every read symbol in the input tape in $M$, then this is written to the output tape in a sequential way.
+We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string.
+Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the elements $x = yz$).
+Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines.
+Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$.
 \end{frame}
 
-\begin{frame}{Proof of $L = 2L$: Second part}
+\begin{frame}{Proof of $L \neq NL$}
 
-In this way, the output string could be accepted by a deterministic one-way logarithmic space Turing machine, that would be the same Turing machine $M$ where this one will always read on the input tape from left-to-right.
-Certainly, when $M$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right.
-Consequently, $M$ in case of acceptance will output the strings that consist in a language in $1L$.
-Hence, we obtain that $L \subseteq 2L$.
-Since we already know that $2L \subseteq L$, then $L = 2L$.
-
-\end{frame}
-
-\begin{frame}{Proof of $NL = 2NL$: First part}
-
-On the other hand, every language in $L'' \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$.
-The reason is simple, because the Turing machine $N$ could output the sequence of symbols that is read continuously in the input tape during the whole computation in case of acceptance.
-Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way.
-
-\end{frame}
-
-\begin{frame}{Proof of $NL = 2NL$: Second part}
-
-In this way, the output string could be accepted by a nondeterministic one-way logarithmic space Turing machine, that would be the same Turing machine $N$ where this one will always read on the input tape from left-to-right.
-Certainly, when $N$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right.
-Consequently, $N$ in case of acceptance will output the strings that consist in a language in $1NL$.
-Hence, we obtain that $NL \subseteq 2NL$.
-Since we already know that $2NL \subseteq NL$, then $NL = 2NL$.
+However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ in some languages in $BNL$ when the prefix $y$ is the empty string, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$.
+Hence, we obtain that $BNL \neq NL$ by transitivity.
+Nevertheless, Sauerhoff has also shown that $L \subseteq BNL \subseteq NL$.
+Consequently, we prove the complexity class $L$ is not equal to $NL$.
 
@@
 
-In this way, if $L = NL$ then $2L = 2NL$.
-However, we know that $2L \neq 2NL$ because of $1L \neq 1NL$ since Hartmanis and Mahaney have shown that $1L \neq 1NL$ by looking at a uniform variant of the string non-equality problem from communication complexity theory.
-Therefore, we prove the complexity class $L$ is not equal to $NL$.
 Since we show that $L \neq NL$, then we prove the complexity class $P$ is equal to $NP$.

### 2019-11-17 doc/manuscript.tex
Improved the result doc

@@
 In particular, it cannot reread any bit to the left of where the head currently is \cite{AB09}.
-For that reason this kind of special tape is called $``$read once$"$ \cite{AB09}.
+For that reason this kind of special tape is called $``$read-once$"$ \cite{AB09}.
 
@@
 \begin{proof}
-We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string.
-Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the elements $x = yz$).
+We have that $NL \subseteq LNL$, because the prefix substring $y$ of an instance $x = yz$ could be the empty string.
+Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix substring $y$ is the empty string in the elements $x = yz$).
 Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines.
 Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$.
-However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ in some languages in $BNL$ when the prefix $y$ is the empty string, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$.
+However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ in some languages in $BNL$ when the prefix substring $y$ is the empty string, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$.
 Hence, we obtain that $BNL \neq NL$ by transitivity.

### 2019-11-17 doc/presentation.tex
Improved the result doc

@@
 
-We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string.
-Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the elements $x = yz$).
+We have that $NL \subseteq LNL$, because the prefix substring $y$ of an instance $x = yz$ could be the empty string.
+Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix substring $y$ is the empty string in the elements $x = yz$).
 Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines.
@@
 
-However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ in some languages in $BNL$ when the prefix $y$ is the empty string, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$.
+However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ in some languages in $BNL$ when the prefix substring $y$ is the empty string, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$.
 Hence, we obtain that $BNL \neq NL$ by transitivity.

### 2019-11-18 doc/manuscript.tex
Fixing grammar doc

@@
 
-Sauerhoff has shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input ($``$nondeterminism at the beginning$"$) \cite{MS03}.
+Sauerhoff has investigated the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input ($``$nondeterminism at the beginning$"$) \cite{MS03}.
 

### 2019-11-22 doc/presentation.tex
Updated the presentation doc

@@
 
-Sauerhoff has shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input ($``$nondeterminism at the beginning$"$).
+Sauerhoff has investigated the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input ($``$nondeterminism at the beginning$"$).
 

### 2019-11-24 doc/manuscript.tex
Fixed proof doc
Updated finally the proof doc

--- 2019-11-17 doc/manuscript.tex
@@
 
-\title{Logarithmic Space Verifiers on NP-complete} %TODO Please add
+\title{P versus NP} %TODO Please add
 
@@
 
-\keywords{complexity classes, completeness, verifier, reduction, polynomial time, logarithmic space}%TODO mandatory; please add comma-separated list of keywords
+\keywords{complexity classes, completeness, polynomial time, reduction, logarithmic space, one-way}%TODO mandatory; please add comma-separated list of keywords
 
@@
 Since that date, all efforts to find a proof for this problem have failed.
-NP is the complexity class of languages defined by polynomial time verifiers M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in P.
 Another major complexity classes are L and NL.
-The certificate-based definition of NL is based on logarithmic space Turing machine with an additional special read-once input tape: This is called a logarithmic space verifier.
-NL is the complexity class of languages defined by logarithmic space verifiers M such that when the input is an element of the language with its certificate, then M outputs 1.
-To attack the P versus NP problem, the NP-completeness is a useful concept.
-We demonstrate there is an NP-complete language defined by a logarithmic space verifier M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in L.
-In this way, we obtain if L is not equal to NL, then P = NP.
-In addition, we show that L is not equal to NL.
-Hence, we prove the complexity class P is equal to NP.
+We demonstrate if L is not equal to NL, then P = NP.
+In addition, we show if L is equal to NL, then P = NP.
+In this way, we prove the complexity class P is equal to NP.
 \end{abstract}
@@
 In addition, Blum and Kannan has studied another model where the goal is to check a computation based solely on the final answer \cite{LIP90}.
-More about probabilistic logarithmic space verifiers have been shown on a technique of Lipton \cite{LIP90}.
-In this work, we show some results about the logarithmic space verifiers applied to the class $NP$ which solve one of the most important open problems in computer science, that is $P$ versus $NP$.
+More about probabilistic logarithmic space verifiers and the complexity class $NP$ has been investigated on a technique of Lipton \cite{LIP90}.
+In this work, we show some results about the logarithmic space verifiers applied to the class $NP$ and logarithmic space disqualifiers applied to the class $coNP$ which solve one of the most important open problems in computer science, that is $P$ versus $NP$.
 
@@
 For each string $w$ in $\Sigma^{*}$ there is a computation associated with $M$ on input $w$ \cite{AB09}.
-We say that $M$ accepts $w$ if this computation terminates in the accepting state, that is $M(w)=1$ (when $M$ outputs 1 on the input $w$) \cite{AB09}.
-Note that $M$ fails to accept $w$ either if this computation ends in the rejecting state, that is $M(w)=0$, or if the computation fails to terminate, or the computation ends in the halting state with some output, that is $M(w)=y$ (when $M$ outputs the string $y$ on the input $w$) \cite{AB09}.
+We say that $M$ accepts $w$ if this computation terminates in the accepting state, that is $M(w)=``yes"$ \cite{AB09}.
+Note that $M$ fails to accept $w$ either if this computation ends in the rejecting state, that is $M(w)=``no"$, or if the computation fails to terminate, or the computation ends in the halting state with some output, that is $M(w)=y$ (when $M$ outputs the string $y$ on the input $w$) \cite{AB09}.
 
@@
 The language accepted by a Turing machine $M$, denoted $L(M)$, has an associated alphabet $\Sigma$ and is defined by:
-\[L(M) = \{w \in \Sigma^{*}: M(w)=1 \}.\]
+\[L(M) = \{w \in \Sigma^{*}: M(w)=``yes" \}.\]
 We denote by $t_{M}(w)$ the number of steps in the computation of $M$ on input $w$ \cite{AB09}. For $n \in \mathbb{N}$ we denote by $T_{M}(n)$ the worst case run time of $M$; that is:
@@
 A verifier for a language $L_{1}$ is a deterministic Turing machine $M$, where:
-\[L_{1} = \{w: M(w, c) = 1 \textit{ for some string } c\}.\]
+\[L_{1} = \{w: M(w, c) = ``yes" \textit{ for some string } c\}.\]
 We measure the time of a verifier only in terms of the length of $w$, so a polynomial time verifier runs in polynomial time in the length of $w$ \cite{AB09}.
@@
 $NP$ is the complexity class of languages defined by polynomial time verifiers \cite{Pap03}.
+If $NP$ is the class of problems that have succinct certificates, then the complexity class $coNP$ must contain those problems that have succinct disqualifications \cite{Pap03}.
+That is, a $``no"$ instance of a problem in $coNP$ possesses a short proof of its being a $``no"$ instance \cite{Pap03}.
 
@@
 \begin{proof}
-If $L_{1}$ can be decided by the Turing machine $M'$ in polynomial time, then the deterministic Turing machine $M''(w, c) = M'(M(w, c))$ will output 1 when $w \in L_{2}$.
+If $L_{1}$ can be decided by the Turing machine $M'$ in polynomial time, then the deterministic Turing machine $M''(w, c) = M'(M(w, c))$ will accept when $w \in L_{2}$.
 Consequently, $M''$ is a polynomial time verifier of $L_{2}$ and thus, $L_{2}$ is in $NP$.
@@
 
-\subsection{Hypothesis}
+\subsection{First Hypothesis}
 
@@
 A language $L_{1}$ is in $NL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$,
-\[x \in L_{1} \Leftrightarrow \exists u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = 1 \]
-where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function \cite{AB09}.
+\[x \in L_{1} \Leftrightarrow \exists u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = ``yes" \]
+where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the certificate $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function \cite{AB09}.
 $M$ is called a logarithmic space verifier \cite{AB09}.
@@
 \begin{hypothesis}
-\label{hypothesis}
+\label{hypothesis1}
 Given a language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
@@
 \end{hypothesis}
-
-\subsection{Consequences}
 
@@
 \begin{theorem}
-\label{implication}
-If the Hypothesis \ref{hypothesis} is true, therefore if $L \neq NL$, then $P = NP$.
+\label{neg-implication}
+If the Hypothesis \ref{hypothesis1} is true, therefore if $L \neq NL$, then $P = NP$.
 \end{theorem}
@@
 \begin{proof}
-We can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis} by a nondeterministic logarithmic space Turing machine $N$, such that $N(w) = y$ since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$ \cite{Pap03}.
+We can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis1} by a nondeterministic logarithmic space Turing machine $N$, such that $N(w) = y$ since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$ \cite{Pap03}.
 Certainly, we can simulate the reading of one symbol from the string $u$ into the read-once tape just nondeterministically generating the same symbol in the work tapes using a logarithmic space \cite{Pap03}.
@@
 If we suppose that $L \subset 1NL$, then we can accept the elements of the language $L_{1} \in L$ by a nondeterministic one-way logarithmic space Turing machine $M'$.
-In this way, there is a nondeterministic logarithmic space Turing machine $M''(w) = M'(N(w))$ which will output 1 when $w \in L_{2}$.
+In this way, there is a nondeterministic logarithmic space Turing machine $M''(w) = M'(N(w))$ which will accept when $w \in L_{2}$.
 Consequently, $M''$ is a nondeterministic logarithmic space Turing machine which decides the language $L_{2}$.
@@
 
+\subsection{Second Hypothesis}
+
+An important complexity class is $\textit{coNP--complete}$ \cite{GJ79}. A language $L_{1} \subseteq \{0, 1\}^{*}$ is $\textit{coNP--complete}$ if:
+
+\begin{itemize}
+\item $L_{1} \in coNP$, and
+\item $L' \leq_{p} L_{1}$ for every $L' \in coNP$.
+\end{itemize}
+
+If $L_{1}$ is a language such that $L' \leq_{p} L_{1}$ for some $L' \in \textit{coNP--complete}$, then $L_{1}$ is $\textit{coNP--hard}$ \cite{CLRS01}.
+Moreover, if $L_{1} \in coNP$, then $L_{1} \in \textit{coNP--complete}$ \cite{CLRS01}.
+A principal $\textit{coNP--complete}$ problem is $UNSAT$ \cite{GJ79}.
+A formula without any satisfying truth assignment is an unsatisfiable formula.
+The problem $UNSAT$ asks whether a given Boolean formula is unsatisfiable \cite{GJ79}.
+
+$coNL$ is the complexity class containing the languages when their complements belong to $NL$ \cite{Pap03}.
+We can give a disqualification-based definition for $coNL$ \cite{AB09}.
+The disqualification-based definition of $coNL$ assumes that a logarithmic space Turing machine has another separated read-only tape, that is the same kind of special tape called $``$read-once$"$ that we use in the certificate-based definition for $NL$ \cite{AB09}.
+Besides, in the disqualification-based definition of $coNL$, we assume the disqualification string is appropriated for the instance \cite{Pap03}.
+For example, a truth assignment for a Boolean formula $\phi$ in $3CNF$ is appropriated for the instance when every possible variable in $\phi$ could be evaluated in that truth assignment string, but we cannot affirm the same for every possible binary string.
+
 \begin{definition}
-\label{definition}
-The class $LNL$ contains those languages that are decided by a nondeterministic logarithmic space Turing machine $N$ such that for every element $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves strictly deterministically on $y$ and strictly nondeterministically on $z$ when strictly deterministically means there is no a possible nondeterministic step and strictly nondeterministically means there is at least one nondeterministic step on the computation.
+A language $L_{1}$ is in $coNL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$,
+\[x \in L_{1} \Leftrightarrow \forall \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ then } M(x, u) = ``yes" \]
+where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the disqualification $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function \cite{AB09}.
+$M$ is called a logarithmic space disqualifier.
 \end{definition}
 
-Sauerhoff has shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input ($``$nondeterminism at the beginning$"$) \cite{MS03}.
+We state the following Hypothesis:
+
+\begin{hypothesis}
+\label{hypothesis2}
+Given a language $L_{1} \in 1NL$, there is a language $L_{2}$ in $\textit{coNP--complete}$ with a deterministic Turing machine $M$, where:
+\[L_{2} = \{w: M(w, u) = y \textit{ for all the appropriated string } u \textit{ such that } y \in L_{1}\}\]
+when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
+In this way, there is a $\textit{coNP--complete}$ language defined by a logarithmic space disqualifier $M$ such that when the input is an element of the language with any of its appropriated disqualification, then $M$ always outputs a string which belongs to a single language in $1NL$.
+\end{hypothesis}
 
 \begin{theorem}
-\label{negation}
-$L \neq NL$.
+\label{pos-implication}
+If the Hypothesis \ref{hypothesis2} is true, therefore if $L = NL$, then $P = NP$.
 \end{theorem}
@@
 \begin{proof}
-We have that $NL \subseteq LNL$, because the prefix substring $y$ of an instance $x = yz$ could be the empty string.
-Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix substring $y$ is the empty string in the elements $x = yz$).
-Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines.
-Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$.
-However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ in some languages in $BNL$ when the prefix substring $y$ is the empty string, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$.
-Hence, we obtain that $BNL \neq NL$ by transitivity.
-Nevertheless, Sauerhoff has also shown that $L \subseteq BNL \subseteq NL$ \cite{MS03}.
-Consequently, we prove the complexity class $L$ is not equal to $NL$.
-\end{proof}
-
-\begin{theorem}
-\label{argument}
-If the Hypothesis \ref{hypothesis} is true, then $P = NP$.
-\end{theorem}
-
-\begin{proof}
-This is a direct consequence of Theorems \ref{implication} and \ref{negation}.
+We can accept the elements of the language $L_{1} \in 1NL$ by a nondeterministic one-way logarithmic space Turing machine $M'$.
+In this way, there is a nondeterministic logarithmic space Turing machine $M''(w, u) = M'(M(w, u))$ which will accept when $w \in L_{2}$ for all the appropriated disqualification $u$.
+The reason is because we can simulate the output string of $M(w, u)$ within a read-once tape and thus, we can compute in a nondeterministic logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}.
+Certainly, we do not need to reset the computation of $M(w, u)$ for the reading at once of a symbol in the output string of $M(w, u)$ by the nondeterministic one-way logarithmic space Turing machine $M'$.
+Consequently, $M''$ can be converted into a logarithmic space disqualifier for the language $L_{2}$ just assuming that $L = NL$, because of the nondeterministic logarithmic space Turing machine $M''$ could be simulated by a deterministic logarithmic space Turing machine.
+Therefore, $L_{2}$ is in $coNL$ and thus, $L_{2} \in P$ due to $coNL \subseteq P$ \cite{Pap03}.
+If any single $\textit{coNP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{Pap03}.
+Since $L_{2} \in P$ and $L_{2} \in \textit{coNP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that $L = NL$.
 \end{proof}
@@
 \section{Results}
+
+\subsection{First Hypothesis}
 
@@
 Given a valid instance $(\psi, K)$ for $MIN\oplus2SAT$ when $\psi$ has $m$ clauses, we can create a certificate array $A$ which contains $K$ different natural numbers in ascending order which represents the indexes of the clauses in $\psi$ that we are going to remove from the instance.
-We read at once the elements of the array $A$ and we reject whether this is not a valid certificate: That is when the numbers are not sorted in ascending order, or the array $A$ does not contain exactly $K$ elements, or the array $A$ contains a number that is not between $1$ and $m$.
+We read at once the elements of the array $A$ and we reject whether this is not an appropriated certificate: That is when the numbers are not sorted in ascending order, or the array $A$ does not contain exactly $K$ elements, or the array $A$ contains a number that is not between $1$ and $m$.
 While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MIN\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$.
@@
 Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right.
-Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is a valid certificate and also remove the $K$ different clauses from the Boolean formula $\psi$ when we write the final clauses to the output.
-This logarithmic space verification will be the Algorithm \ref{algorithm}.
+Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated certificate and also remove the $K$ different clauses from the Boolean formula $\psi$ when we write the final clauses to the output.
+This logarithmic space verification will be the Algorithm \ref{algorithm1}.
 We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = undefined$.
@@
 \begin{algorithm}
-\caption{Logarithmic space verifier}\label{algorithm}
+\caption{Logarithmic space verifier}\label{algorithm1}
 \begin{algorithmic}[1]
@@
 \Comment{Reject the certificate}
-\State \textbf{return} $0$
+\State \textbf{return} $``no"$
 \EndIf
@@
 \Comment{Reject the certificate}
-\State \textbf{return} $0$
+\State \textbf{return} $``no"$
 \Else
@@
 \For{$j$}{$min$}{$max - 1$}
-\Comment{Output the indexed $j$ clause in $\psi$}
+\Comment{Output the indexed $j^{th}$ clause in $\psi$}
 \State \textbf{output} $``\wedge c_{j}"$
@@
 \begin{theorem}
-\label{result}
-The Hypothesis \ref{hypothesis} is true.
+\label{result1}
+The Hypothesis \ref{hypothesis1} is true.
 \end{theorem}
@@
 This is a consequence of Theorems \ref{completeness} and \ref{proof}.
+\end{proof}
+
+\subsection{Second Hypothesis}
+
+We show a previous known $\textit{coNP--complete}$ problem:
+
+\begin{definition}
+$\textbf{3UNSAT}$
+
+INSTANCE: A Boolean formula $\phi$ in $3CNF$.
+
+QUESTION: Is $\phi$ unsatisfiable?
+
+REMARKS: $3UNSAT \in \textit{coNP--complete}$ \cite{GJ79}.
+\end{definition}
+
+We define a new problem:
+
+\begin{definition}
+$\textbf{SUM ZERO}$
+
+INSTANCE: A collection of integers (positive or negative) $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we fill with zeroes to the left the elements with bit-length lesser than the cardinality of $C$ multiplied by $3$).
+
+QUESTION: Are there two elements $a, b \in C$ such that $a + b = 0$?
+
+REMARKS: We denote this problem as $\textit{SUM--ZERO}$.
+\end{definition}
+
+\begin{theorem}
+\label{1nl}
+$\textit{SUM--ZERO} \in 1NL$.
+\end{theorem}
+
+\begin{proof}
+Given a collection of integers $C$, we can read its elements from left to right, verify that every element is not equal to $0$, check that every element in $C$ has the same bit-length and count the amount of elements in $C$ to finally compare it multiplied by $3$ with the single bit-length from the elements in $C$.
+In addition, we can nondeterministically pick two elements $a$ and $b$ from $C$ and accept in case of $a + b = 0$ otherwise we reject.
+We can make all this computation in a nondeterministically one-way using logarithmic space.
+Certainly, the calculation and store of the bit-length of the elements in $C$ could be done in logarithmic space since this is a unique value.
+On the one hand, we can count and store the number of elements that we read from the input and compare this multiplied by $3$ with the stored bit-length, since the cardinality of $C$ could be stored in a binary number of bit-length that is logarithmic in relation to the encoded length of $C$.
+On the other hand, the two elements $a$ and $b$ that we pick from $C$ have a logarithmic space in relation to the encoded length of $C$, because of every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$.
+Indeed, we never need to read to the left on the input for the acceptance of the elements in $\textit{SUM--ZERO}$ in a nondeterministically logarithmic space.
+\end{proof}
+
+\begin{theorem}
+\label{demonstration}
+There is a deterministic Turing machine $M$, where:
+\[3UNSAT = \{w: M(w, u) = y \textit{ for all the appropriated string } u \textit{ such that } y \in \textit{SUM--ZERO}\}\]
+when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
+\end{theorem}
+
+\begin{proof}
+Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we can create a disqualification array $A$ which contains $m$ positive integers between $1$ and $3$ which represents the literals of the clauses in $\phi$ which appear from left to right.
+We read at once the elements of the array $A$ and we reject whether this is not an appropriated disqualification: That is when the array $A$ does not contain exactly $m$ elements, or the array $A$ contains a number that is not between $1$ and $3$.
+While we read the elements of the array $A$, we select from the clauses $\phi$ the literals such that these ones occupy the position that represents the number between $1$ and $3$, that is the first, second or third place within the clause  from left to right.
+In this way, we output the selected literals that are represented by a positive or negative (in case of a negated variable) integer just creating another instance $C$ for $\textit{SUM--ZERO}$ where the collection $C$ contains those integers which are the selected literals for each clause in $\phi$.
+Therefore, we obtain that all the appropriated array $A$ would be valid according to the Theorem \ref{demonstration} when:
+\[\phi \in 3UNSAT \textit{ if and only if } C \in \textit{SUM--ZERO}\]
+since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value.
+Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$.
+Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated disqualification and pick the $m$ literals from the Boolean formula $\phi$ when we write the final integers that represent these literals to the output.
+This logarithmic space verification will be the Algorithm \ref{algorithm2}.
+We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = undefined$.
+In addition, we reject immediately when the following comparisons
+\[A[i] < 1 \vee A[i] > 3\]
+hold at least into one single binary digit.
+Note, that every possible literal in $\phi$ could have a representation by an integer between $-3 \times m$ and $3 \times m$ with the exception of $0$, where $m$ is the cardinality of the collection $C$.
+In this way, we guarantee the output collection $C$ is an appropriated instance of $\textit{SUM--ZERO}$ just filling with zeroes to the left the elements with bit-length lesser than $3 \times m$.
+
+\begin{algorithm}
+\caption{Logarithmic space disqualifier}\label{algorithm2}
+\begin{algorithmic}[1]
+\Comment{A valid instance for $3UNSAT$ with its disqualification}
+\Procedure{$\textit{DISQUALIFIER}$}{$\phi, A$}
+\Comment{Initialize an index}
+\State $j \gets 0$
+\Comment{$m$ is the number of clauses in $\phi$}
+\Comment{Iterate for the elements of the disqualification array $A$}
+\For{$i$}{$1$}{$m + 1$}
+\If{$i = m+1$}
+\Comment{There exists an $m+1$ element in the array}
+\If{$A[i] \neq undefined$}
+\Comment{Reject the disqualification}
+\State \textbf{return} $``no"$
+\EndIf
+\Comment{Break the for loop}
+\State \textbf{break}
+\ElsIf{$A[i] = undefined \vee A[i] < 1 \vee A[i] > 3$}
+\Comment{Reject the disqualification}
+\State \textbf{return} $``no"$
+\Else
+\State $j \gets A[i]$
+\EndIf
+\Comment{From the indexed $i^{th}$ clause $c_{i} = (x_{j} \vee y_{k} \vee z_{r})$ in $\phi$}
+\Comment{Where $x$, $y$ and $z$ are literals with local indexes $\{j, k, r\} = \{1,2,3\}$ in $c_{i}$}
+\Comment{Output the integer of the $j^{th}$ literal filled with zeroes until $3 \times m$ bits}
+\State \textbf{output} $``x_{j}"$
+\EndFor
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+\end{proof}
+
+\begin{theorem}
+\label{result2}
+The Hypothesis \ref{hypothesis2} is true.
+\end{theorem}
+
+\begin{proof}
+This is a consequence of Theorems \ref{1nl} and \ref{demonstration}.
+\end{proof}
+
+\subsection{Consequences}
+
+\begin{theorem}
+If $L \neq NL$ then $P = NP$.
+\end{theorem}
+
+\begin{proof}
+This is a direct consequence of Theorems \ref{neg-implication} and \ref{result1}.
+\end{proof}
+
+\begin{theorem}
+If $L = NL$ then $P = NP$.
+\end{theorem}
+
+\begin{proof}
+This is a direct consequence of Theorems \ref{pos-implication} and \ref{result2}.
 \end{proof}
@@
 \begin{proof}
-This is a direct consequence of Theorems \ref{argument} and \ref{result}.
+Since we have is true either $L \neq NL$ or $L = NL$, then the complexity class $P$ is equal to $NP$.
 \end{proof}
-
-\subsection{Codes}
-
-This work is implemented into a Project programmed in Scala \cite{FV19}.
-In this Project, we use the Assertion on the properties of the instances of each problem and the Unit Test for checking the correctness of every reduction \cite{FV19}.
-We need to install JDK 8 in order to test the Scala Project \cite{OD16}.
-In addition, we need to install SBT to run the unit test (we could run the unit test with the $\textbf{sbt test}$ command) \cite{OD16}.
 
@@
 The consequences, both positive and negative, arise since various $\textit{NP--complete}$ problems are fundamental in many fields \cite{CS00}.
-All the following consequences are assuming that we have a practical solution for the $\textit{NP--complete}$ problems where such existence was proven with our result:
+All the following consequences are assuming that we have a practical solution for the $\textit{NP--complete}$ problems where such existence was proven with our nonconstructive result:
 
@@
 
-The economy would become vastly more efficient.
 There would be disruption, including maybe displacing programmers \cite{IMP95}.

### 2019-11-24 doc/manuscript.tex
Update the content proof

@@
 That is, a $``no"$ instance of a problem in $coNP$ possesses a short proof of its being a $``no"$ instance \cite{Pap03}.
-
-\begin{lemma}
-\label{verifier}
-Given a language $L_{1} \in P$, a language $L_{2}$ is in $NP$ if there is a deterministic Turing machine $M$, where:
-\[L_{2} = \{w: M(w, c) = y \textit{ for some string } c \textit{ such that } y \in L_{1}\}\]
-and $M$ runs in polynomial time in the length of $w$.
-In this way, $NP$ is the complexity class of languages defined by polynomial time verifiers $M$ such that when the input is an element of the language with its certificate, then $M$ outputs a string which belongs to a single language in $P$.
-\end{lemma}
-
-\begin{proof}
-If $L_{1}$ can be decided by the Turing machine $M'$ in polynomial time, then the deterministic Turing machine $M''(w, c) = M'(M(w, c))$ will accept when $w \in L_{2}$.
-Consequently, $M''$ is a polynomial time verifier of $L_{2}$ and thus, $L_{2}$ is in $NP$.
-\end{proof}
 
@@
 
-INSTANCE: A collection of integers (positive or negative) $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we fill with zeroes to the left the elements with bit-length lesser than the cardinality of $C$ multiplied by $3$).
+INSTANCE: A collection of integers (positive or negative) $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we fill with zeroes to the left the elements in case of necessity).
 
@@
 \begin{proof}
-Given a collection of integers $C$, we can read its elements from left to right, verify that every element is not equal to $0$, check that every element in $C$ has the same bit-length and count the amount of elements in $C$ to finally compare it multiplied by $3$ with the single bit-length from the elements in $C$.
+Given a collection of integers $C$, we can read its elements from left to right, verify that every element is not equal to $0$, check that every element in $C$ has the same bit-length and count the amount of elements in $C$ to finally multiply it by $3$ and compare its bit-length with the single bit-length from the elements in $C$.
 In addition, we can nondeterministically pick two elements $a$ and $b$ from $C$ and accept in case of $a + b = 0$ otherwise we reject.
@@
 Certainly, the calculation and store of the bit-length of the elements in $C$ could be done in logarithmic space since this is a unique value.
-On the one hand, we can count and store the number of elements that we read from the input and compare this multiplied by $3$ with the stored bit-length, since the cardinality of $C$ could be stored in a binary number of bit-length that is logarithmic in relation to the encoded length of $C$.
+On the one hand, we can count and store the number of elements that we read from the input and multiply it by $3$ to finally compare its bit-length with the stored bit-length, since the cardinality of $C$ multiplied by $3$ could be stored in a binary number of bit-length that is logarithmic in relation to the encoded length of $C$.
 On the other hand, the two elements $a$ and $b$ that we pick from $C$ have a logarithmic space in relation to the encoded length of $C$, because of every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$.
@@
 Note, that every possible literal in $\phi$ could have a representation by an integer between $-3 \times m$ and $3 \times m$ with the exception of $0$, where $m$ is the cardinality of the collection $C$.
-In this way, we guarantee the output collection $C$ is an appropriated instance of $\textit{SUM--ZERO}$ just filling with zeroes to the left the elements with bit-length lesser than $3 \times m$.
+In this way, we guarantee the output collection $C$ is an appropriated instance of $\textit{SUM--ZERO}$ just filling with zeroes to the left the elements with bit-length lesser than $|3 \times m|$ where $|\ldots|$ is the bit-length function.
 
@@
 \Comment{Where $x$, $y$ and $z$ are literals with local indexes $\{j, k, r\} = \{1,2,3\}$ in $c_{i}$}
-\Comment{Output the integer of the $j^{th}$ literal filled with zeroes until $3 \times m$ bits}
+\Comment{Output the integer of the $j^{th}$ literal filled with zeroes until $|3 \times m|$ bits}
 \State \textbf{output} $``x_{j}"$

### 2019-11-25 doc/manuscript.tex
Updated finally the content proof

@@
 A principal $\textit{coNP--complete}$ problem is $UNSAT$ \cite{GJ79}.
-A formula without any satisfying truth assignment is an unsatisfiable formula.
+A Boolean formula without any satisfying truth assignment is unsatisfiable.
 The problem $UNSAT$ asks whether a given Boolean formula is unsatisfiable \cite{GJ79}.
@@
 
-INSTANCE: A collection of integers (positive or negative) $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we fill with zeroes to the left the elements in case of necessity).
+INSTANCE: A collection of integers $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we do not take into account the symbol minus in the bit-length of the negative integers).
 
-QUESTION: Are there two elements $a, b \in C$ such that $a + b = 0$?
+QUESTION: Are there two elements $a, b \in C$, such that $a + b = 0$?
 

### 2019-11-25 doc/manuscript.tex
Updated revision proof

@@
 \label{hypothesis1}
-Given a language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
+Given a nonempty language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
 \[L_{2} = \{w: M(w, u) = y \textit{ for some string } u \textit{ such that } y \in L_{1}\}\]
@@
 \label{hypothesis2}
-Given a language $L_{1} \in 1NL$, there is a language $L_{2}$ in $\textit{coNP--complete}$ with a deterministic Turing machine $M$, where:
+Given a nonempty language $L_{1} \in 1NL$, there is a language $L_{2}$ in $\textit{coNP--complete}$ with a deterministic Turing machine $M$, where:
 \[L_{2} = \{w: M(w, u) = y \textit{ for all the appropriated string } u \textit{ such that } y \in L_{1}\}\]
@@
 \begin{definition}
-$\textbf{MINIMUM EXCLUSIVE-OR 2-SATISFIABILITY}$
+$\textbf{MAXIMUM EXCLUSIVE-OR 2-SATISFIABILITY}$
 
@@
 
-QUESTION: Is there a truth assignment in $\phi$ such that at most $K$ clauses are unsatisfiable?
+QUESTION: Is there a truth assignment in $\phi$ such that at most $K$ clauses are unsatisfied?
 
-REMARKS: We denote this problem as $MIN\oplus2SAT$.
+REMARKS: We denote this problem as $MAX\oplus2SAT$.
 \end{definition}
@@
 \label{completeness}
-$MIN\oplus2SAT \in \textit{NP--complete}$.
+$MAX\oplus2SAT \in \textit{NP--complete}$.
 \end{theorem}
@@
 \begin{proof}
-It is trivial to see $MIN\oplus2SAT \in NP$ \cite{Pap03}.
+It is trivial to see $MAX\oplus2SAT \in NP$ \cite{Pap03}.
 Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we create three new variables $a_{c_{i}}$, $b_{c_{i}}$ and $d_{c_{i}}$ for each clause $c_{i} = (x \vee y \vee z)$ in $\phi$, where $x$, $y$ and $z$ are literals, in the following formula:
 \[P_{i} = (a_{c_{i}} \oplus b_{c_{i}}) \wedge (b_{c_{i}} \oplus d_{c_{i}}) \wedge (a_{c_{i}} \oplus d_{c_{i}}) \wedge (x \oplus a_{c_{i}}) \wedge (y \oplus b_{c_{i}}) \wedge (z \oplus d_{c_{i}}).\]
-We can see $P_{i}$ has at most one unsatisfiable clause for some truth assignment if and only if at least one member of $\{x,y,z\}$ is true and at least one member of $\{x,y,z\}$ is false for the same truth assignment.
+We can see $P_{i}$ has at most one unsatisfied clause for some truth assignment if and only if at least one member of $\{x,y,z\}$ is true and at least one member of $\{x,y,z\}$ is false for the same truth assignment.
 Hence, we can create the Boolean formula $\psi$ as the conjunction of the $P_{i}$ formulas for every clause $c_{i}$ in $\phi$, such that $\psi = P_{1} \wedge \ldots \wedge P_{m}$.
 Finally, we obtain that
-\[\phi \in \textit{NAE 3SAT} \textit{ if and only if } (\psi, m) \in MIN\oplus2SAT.\]
-Consequently, we prove $\textit{NAE 3SAT} \leq_{p} MIN\oplus2SAT$ where we already know the language $\textit{NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}.
-To sum up, we show $MIN\oplus2SAT \in \textit{NP--hard}$ and $MIN\oplus2SAT \in NP$ and thus, $MIN\oplus2SAT \in \textit{NP--complete}$.
+\[\phi \in \textit{NAE 3SAT} \textit{ if and only if } (\psi, m) \in MAX\oplus2SAT.\]
+Consequently, we prove $\textit{NAE 3SAT} \leq_{p} MAX\oplus2SAT$ where we already know the language $\textit{NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}.
+To sum up, we show $MAX\oplus2SAT \in \textit{NP--hard}$ and $MAX\oplus2SAT \in NP$ and thus, $MAX\oplus2SAT \in \textit{NP--complete}$.
 \end{proof}
@@
 There is a deterministic Turing machine $M$, where:
-\[MIN\oplus2SAT = \{w: M(w, u) = y \textit{ for some string } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
+\[MAX\oplus2SAT = \{w: M(w, u) = y \textit{ for some string } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
@@
 \begin{proof}
-Given a valid instance $(\psi, K)$ for $MIN\oplus2SAT$ when $\psi$ has $m$ clauses, we can create a certificate array $A$ which contains $K$ different natural numbers in ascending order which represents the indexes of the clauses in $\psi$ that we are going to remove from the instance.
+Given a valid instance $(\psi, K)$ for $MAX\oplus2SAT$ when $\psi$ has $m$ clauses, we can create a certificate array $A$ which contains $K$ different natural numbers in ascending order which represents the indexes of the clauses in $\psi$ that we are going to remove from the instance.
 We read at once the elements of the array $A$ and we reject whether this is not an appropriated certificate: That is when the numbers are not sorted in ascending order, or the array $A$ does not contain exactly $K$ elements, or the array $A$ contains a number that is not between $1$ and $m$.
-While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MIN\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$.
+While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MAX\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$.
 Therefore, we obtain the array $A$ should be valid according to the Theorem \ref{proof} when:
-\[(\psi, K) \in MIN\oplus2SAT \textit{ if and only if } \phi \in \textit{XOR 2SAT}.\]
+\[(\psi, K) \in MAX\oplus2SAT \textit{ if and only if } \phi \in \textit{XOR 2SAT}.\]
 Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right.
@@
 \begin{algorithmic}[1]
-\Comment{A valid instance for $MIN\oplus2SAT$ with its certificate}
+\Comment{A valid instance for $MAX\oplus2SAT$ with its certificate}
 \Procedure{$\textit{VERIFIER}$}{$(\psi, K), A$}
@@
 
-INSTANCE: A collection of integers $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we do not take into account the symbol minus in the bit-length of the negative integers).
+INSTANCE: A collection of integers $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we do not take into account the symbol minus in counting the bit-length of the negative integers).
 

### 2019-11-26 doc/manuscript.tex
Update style proof doc

@@
 While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MAX\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$.
-Therefore, we obtain the array $A$ should be valid according to the Theorem \ref{proof} when:
+Therefore, we obtain the array $A$ would be valid according to the Theorem \ref{proof} when:
 \[(\psi, K) \in MAX\oplus2SAT \textit{ if and only if } \phi \in \textit{XOR 2SAT}.\]
@@
 This logarithmic space verification will be the Algorithm \ref{algorithm1}.
-We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = undefined$.
+We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$.
 In addition, we reject immediately when the following comparisons
@@
 \Comment{There exists a $K+1$ element in the array}
-\If{$A[i] \neq undefined$}
+\If{$A[i] \neq \textit{undefined}$}
 \Comment{Reject the certificate}
@@
 \State $max \gets m + 1$
-\ElsIf{$A[i] = undefined \vee A[i] \leq max \vee A[i] < 1 \vee A[i] > m$}
+\ElsIf{$A[i] = \textit{undefined} \vee A[i] \leq max \vee A[i] < 1 \vee A[i] > m$}
 \Comment{Reject the certificate}
@@
 This logarithmic space verification will be the Algorithm \ref{algorithm2}.
-We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = undefined$.
+We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$.
 In addition, we reject immediately when the following comparisons
@@
 \Comment{There exists an $m+1$ element in the array}
-\If{$A[i] \neq undefined$}
+\If{$A[i] \neq \textit{undefined}$}
 \Comment{Reject the disqualification}
@@
 \State \textbf{break}
-\ElsIf{$A[i] = undefined \vee A[i] < 1 \vee A[i] > 3$}
+\ElsIf{$A[i] = \textit{undefined} \vee A[i] < 1 \vee A[i] > 3$}
 \Comment{Reject the disqualification}

### 2019-12-04 doc/manuscript.tex
The content proof was slighlty modified

@@
 Interactive proofs introduced by Goldwasser, Micali and Rackoff and Babi can be viewed as a model of the verification process \cite{LIP90}.
-Dwork and Stockmeyer and Condon have studied interactive proofs where the verifier is a space bounded computation instead of the original model where the verifer is a time bounded computation \cite{LIP90}.
+Dwork and Stockmeyer and Condon have studied interactive proofs where the verifier is a space bounded computation instead of the original model where the verifier is a time bounded computation \cite{LIP90}.
 In addition, Blum and Kannan has studied another model where the goal is to check a computation based solely on the final answer \cite{LIP90}.
@@
 \[x \in L_{1} \textit{ if and only if } f(x) \in L_{2}.\]
-The logarithmic space reduction is frequently used for $L$ and $NL$ \cite{Pap03}.
+The logarithmic space reduction is used in the definition of the complete languages for the classes $L$ and $NL$ \cite{Pap03}.
 A Boolean formula is in 2-conjunctive normal form, or $2CNF$, if it is in $CNF$ and each clause has exactly two distinct literals.
@@
 Given a nonempty language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
-\[L_{2} = \{w: M(w, u) = y \textit{ for some string } u \textit{ such that } y \in L_{1}\}\]
+\[L_{2} = \{w: M(w, u) = y, \exists \textit{ string } u \textit{ such that } y \in L_{1}\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
@@
 
-$coNL$ is the complexity class containing the languages when their complements belong to $NL$ \cite{Pap03}.
+$coNL$ is the complexity class containing the languages such that their complements belong to $NL$ \cite{Pap03}.
 We can give a disqualification-based definition for $coNL$ \cite{AB09}.
@@
 Given a nonempty language $L_{1} \in 1NL$, there is a language $L_{2}$ in $\textit{coNP--complete}$ with a deterministic Turing machine $M$, where:
-\[L_{2} = \{w: M(w, u) = y \textit{ for all the appropriated string } u \textit{ such that } y \in L_{1}\}\]
+\[L_{2} = \{w: M(w, u) = y, \forall \textit{ appropriated string } u \textit{ such that } y \in L_{1}\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
@@
 There is a deterministic Turing machine $M$, where:
-\[MAX\oplus2SAT = \{w: M(w, u) = y \textit{ for some string } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
+\[MAX\oplus2SAT = \{w: M(w, u) = y, \exists \textit{ string } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
@@
 In addition, we can nondeterministically pick two elements $a$ and $b$ from $C$ and accept in case of $a + b = 0$ otherwise we reject.
-We can make all this computation in a nondeterministically one-way using logarithmic space.
+We can make all this computation in a nondeterministic one-way using logarithmic space.
 Certainly, the calculation and store of the bit-length of the elements in $C$ could be done in logarithmic space since this is a unique value.
@@
 On the other hand, the two elements $a$ and $b$ that we pick from $C$ have a logarithmic space in relation to the encoded length of $C$, because of every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$.
-Indeed, we never need to read to the left on the input for the acceptance of the elements in $\textit{SUM--ZERO}$ in a nondeterministically logarithmic space.
+Indeed, we never need to read to the left on the input for the acceptance of the elements in $\textit{SUM--ZERO}$ in a nondeterministic logarithmic space.
 \end{proof}
@@
 There is a deterministic Turing machine $M$, where:
-\[3UNSAT = \{w: M(w, u) = y \textit{ for all the appropriated string } u \textit{ such that } y \in \textit{SUM--ZERO}\}\]
+\[3UNSAT = \{w: M(w, u) = y, \forall \textit{ appropriated string } u \textit{ such that } y \in \textit{SUM--ZERO}\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
@@
 \EndIf
-\Comment{Break the for loop}
+\Comment{Break the $\textbf{for}$ loop}
 \State \textbf{break}
@@
 \Comment{Where $x$, $y$ and $z$ are literals with local indexes $\{j, k, r\} = \{1,2,3\}$ in $c_{i}$}
-\Comment{Output the integer of the $j^{th}$ literal filled with zeroes until $|3 \times m|$ bits}
-\State \textbf{output} $``x_{j}"$
+\Comment{Output the integer representation of the $j^{th}$ literal}
+\Comment{Filled with zeroes to the left until a total of $|3 \times m|$ bits including the literal}
+\Comment{But, the bit-length of the symbol minus is ignored in filling the negated literals}
+\State \textbf{output} $``,x_{j}"$
 \EndFor
@@
 \begin{proof}
-Since we have is true either $L \neq NL$ or $L = NL$, then the complexity class $P$ is equal to $NP$.
+Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $P$ is equal to $NP$.
 \end{proof}
@@
 The consequences, both positive and negative, arise since various $\textit{NP--complete}$ problems are fundamental in many fields \cite{CS00}.
-All the following consequences are assuming that we have a practical solution for the $\textit{NP--complete}$ problems where such existence was proven with our nonconstructive result:
+The following consequences are assuming that we have a practical solution for the $\textit{NP--complete}$ problems where such existence was proven with our nonconstructive result:
 
-Cryptography, for example, relies on certain problems being difficult.
+\begin{enumerate}
+\item Cryptography, for example, relies on certain problems being difficult.
 A constructive and efficient solution to an $\textit{NP--complete}$ problem such as $3SAT$ will break most existing cryptosystems including: Public-key cryptography \cite{HW97}, symmetric ciphers \cite{MM00} and one-way functions used in cryptographic hashing \cite{DKV07}.
 These would need to be modified or replaced by information-theoretically secure solutions not inherently based on $\textit{P--NP}$ equivalence.
-
-There are enormous positive consequences that will follow from rendering tractable many currently mathematically intractable problems.
+\item There are enormous positive consequences that will follow from rendering tractable many currently mathematically intractable problems.
 For instance, many problems in operations research are $\textit{NP--complete}$, such as some types of integer programming and the traveling salesman problem \cite{GJ79}.
@@
 Many other important problems, such as some problems in protein structure prediction, are also $\textit{NP--complete}$, so this will spur considerable advances in biology \cite{BL98}.
-
-Since all the $\textit{NP--complete}$ optimization problems become easy, everything will be much more efficient \cite{LF09}.
+\item Since all the $\textit{NP--complete}$ optimization problems become easy, everything will be much more efficient \cite{LF09}.
 Transportation of all forms will be scheduled optimally to move people and goods around quicker and cheaper \cite{LF09}.
 Manufacturers can improve their production to increase speed and create less waste \cite{LF09}.
-
 Learning becomes easy by using the principle of Occam's razor: We simply find the smallest program consistent with the data \cite{LF09}.
@@
 We will also have much better predictions of weather and earthquakes and other natural phenomenon \cite{LF09}.
-
-There would be disruption, including maybe displacing programmers \cite{IMP95}.
+\item There would be disruption, including maybe displacing programmers \cite{IMP95}.
 The practice of programming itself would be more about gathering training data and less about writing code \cite{IMP95}.
 Google would have the resources to excel in such a world \cite{IMP95}.
-
-But such changes may pale in significance compared to the revolution an efficient method for solving $\textit{NP--complete}$ problems will cause in mathematics itself.
-Research mathematicians spend their careers trying to prove theorems, and some proofs have taken decades or even centuries to find after problems have been stated.
-For instance, Fermat's Last Theorem took over three centuries to prove.
+\item But such changes may pale in significance compared to the revolution an efficient method for solving $\textit{NP--complete}$ problems will cause in mathematics itself \cite{CS00}.
+Research mathematicians spend their careers trying to prove theorems, and some proofs have taken decades or even centuries to find after problems have been stated \cite{AS17}.
+For instance, Fermat's Last Theorem took over three centuries to prove \cite{AS17}.
 A method that is guaranteed to find proofs to theorems, should one exist of a $``$reasonable$"$ size, would essentially end this struggle \cite{CS00}.
+\end{enumerate}
 

### 2019-12-08 doc/manuscript.tex
The content was slightly modified

@@
 since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value.
-Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$.
+Furthermore, we can make this disqualification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$.
 Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated disqualification and pick the $m$ literals from the Boolean formula $\phi$ when we write the final integers that represent these literals to the output.
-This logarithmic space verification will be the Algorithm \ref{algorithm2}.
+This logarithmic space disqualification will be the Algorithm \ref{algorithm2}.
 We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$.

### 2019-12-12 doc/manuscript.tex
Changed a sentence.
Set real meaning of disqualification string

@@
 $NP$ is the complexity class of languages defined by polynomial time verifiers \cite{Pap03}.
-If $NP$ is the class of problems that have succinct certificates, then the complexity class $coNP$ must contain those problems that have succinct disqualifications \cite{Pap03}.
-That is, a $``no"$ instance of a problem in $coNP$ possesses a short proof of its being a $``no"$ instance \cite{Pap03}.
+If $NP$ is the class of problems that have succinct certificates, then the complexity class $coNP$ must contain those problems that have exhaustive disqualifications \cite{Pap03}.
+That is, a $``yes"$ instance of a problem in $coNP$ possesses a large proof of its being a $``yes"$ instance \cite{Pap03}.
 
@@
 A satisfying truth assignment is a truth assignment that causes $\phi$ to be evaluated as true.
-A formula with a satisfying truth assignment is a satisfiable formula.
+A Boolean formula with a satisfying truth assignment is satisfiable.
 The problem $SAT$ asks whether a given Boolean formula is satisfiable \cite{GJ79}.

### 2019-12-14 doc/manuscript.tex
Extended the definition of succinct disqualification

--- 2019-12-08 doc/manuscript.tex
@@
 That is, a $``no"$ instance of a problem in $coNP$ possesses a short proof of its being a $``no"$ instance \cite{Pap03}.
+We will extend the definition of succinct disqualification for an element $w \in L_{2}$ when $L_{2} \in coNP$ as the polynomially bounded string $c$ such that $M(w, c) = ``no"$ and $M$ is the polynomial time verifier of the complement of $L_{2}$ in $NP$.
 

### 2019-12-16 doc/manuscript.tex
Extended to NL = NP proof

@@
 In this way, we prove the complexity class P is equal to NP.
+Furthermore, we demonstrate the complexity class NL is equal to NP.
 \end{abstract}
@@
 
+\begin{theorem}
+$NL = NP$.
+\end{theorem}
+
+\begin{proof}
+Since the polynomial time reduction in Theorem \ref{completeness} could be easily transformed in a logarithmic space reduction, then the $\textit{NP--complete}$ problem in Theorem \ref{neg-implication}, that would be $MAX\oplus2SAT$, is necessarily in $NL$ and thus all the problems in $NP$ when $L \neq NL$, because of the Cook's Theorem can also be transformed in a logarithmic space reduction \cite{GJ79}.
+For the same reason, the $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$.
+Since we have that $NL = coNL$ and either $L \neq NL$ or $L = NL$ is true, then the complexity class $NL$ is equal to $NP$ \cite{Pap03}.
+\end{proof}
+
 \section{Conclusions}

### 2019-12-24 doc/manuscript.tex
Uploaded details

@@
 \Comment{Where $x$, $y$ and $z$ are literals with local indexes $\{j, k, r\} = \{1,2,3\}$ in $c_{i}$}
-\Comment{Output the integer representation of the $j^{th}$ literal}
+\Comment{Output the integer representation of the $j^{th}$ literal, that is $n(x_{j})$}
 \Comment{Filled with zeroes to the left until a total of $|3 \times m|$ bits including the literal}
 \Comment{But, the bit-length of the symbol minus is ignored in filling the negated literals}
-\State \textbf{output} $``,x_{j}"$
+\State \textbf{output} $``\ , \ n(x_{j})"$
 \EndFor
@@
 For the same reason, the $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$.
-Since we have that $NL = coNL$ and either $L \neq NL$ or $L = NL$ is true, then the complexity class $NL$ is equal to $NP$ \cite{Pap03}.
+Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $NL$ is equal to $NP$ \cite{Pap03}.
 \end{proof}

### 2019-12-26 doc/manuscript.tex
Showing NL=NP outcomes

@@
 That is, a $``no"$ instance of a problem in $coNP$ possesses a short proof of its being a $``no"$ instance \cite{Pap03}.
+
+\begin{definition}
 We will extend the definition of succinct disqualification for an element $w \in L_{2}$ when $L_{2} \in coNP$ as the polynomially bounded string $c$ such that $M(w, c) = ``no"$ and $M$ is the polynomial time verifier of the complement of $L_{2}$ in $NP$.
+\end{definition}
 
@@
 We call $f$ a logarithmic space computable function \cite{MS06}.
-We say that a language $L_{1} \subseteq \{0, 1\}^{*}$ is logarithmic space reducible to a language $L_{2} \subseteq \{0, 1\}^{*}$, written $L_{1} \leq_{l} L_{2}$, if there exists a logarithmic space computable function $f : \{0, 1\}^{*} \rightarrow \{0, 1\}^{*}$ such that for all $x \in \{0, 1\}^{*}$,
+We say that a language $L_{1} \subseteq \{0, 1\}^{*}$ is logarithmic space reducible to a language $L_{2} \subseteq \{0, 1\}^{*}$, written $L_{1} \leq_{l} L_{2}$, if there exists a logarithmic space computable function $f : \{0, 1\}^{*} \rightarrow \{0, 1\}^{*}$ such that for all $x \in \{0, 1\}^{*}$:
 \[x \in L_{1} \textit{ if and only if } f(x) \in L_{2}.\]
@@
 \begin{definition}
-A language $L_{1}$ is in $NL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$,
+A language $L_{1}$ is in $NL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$:
 \[x \in L_{1} \Leftrightarrow \exists u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = ``yes" \]
@@
 \label{neg-implication}
-If the Hypothesis \ref{hypothesis1} is true, therefore if $L \neq NL$, then $P = NP$.
+If the Hypothesis \ref{hypothesis1} is true, therefore when $L \neq NL$, then $P = NP$.
 \end{theorem}
@@
 \begin{definition}
-A language $L_{1}$ is in $coNL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$,
+A language $L_{1}$ is in $coNL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$:
 \[x \in L_{1} \Leftrightarrow \forall \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ then } M(x, u) = ``yes" \]
@@
 \label{pos-implication}
-If the Hypothesis \ref{hypothesis2} is true, therefore if $L = NL$, then $P = NP$.
+If the Hypothesis \ref{hypothesis2} is true, therefore when $L = NL$, then $P = NP$.
 \end{theorem}
@@
 Hence, we can create the Boolean formula $\psi$ as the conjunction of the $P_{i}$ formulas for every clause $c_{i}$ in $\phi$, such that $\psi = P_{1} \wedge \ldots \wedge P_{m}$.
-Finally, we obtain that
+Finally, we obtain that:
 \[\phi \in \textit{NAE 3SAT} \textit{ if and only if } (\psi, m) \in MAX\oplus2SAT.\]
@@
 We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$.
-In addition, we reject immediately when the following comparisons
+In addition, we reject immediately when the following comparisons:
 \[A[i] \leq max \vee A[i] < 1 \vee A[i] > m\]
@@
 We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$.
-In addition, we reject immediately when the following comparisons
+In addition, we reject immediately when the following comparisons:
 \[A[i] < 1 \vee A[i] > 3\]
@@
 For the same reason, the $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$.
-Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $NL$ is equal to $NP$ \cite{Pap03}.
+Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $NL$ is equal to $NP$.
 \end{proof}
@@
 
+We also prove that $NL = NP$.
+There are several important consequences from this result, but we will only mention one of the principal outcomes, that is the Theorem Buhrman-Fortnow-van Melkebeek-Torenvliet \cite{BU00}.
+A set $A$ is auto-reducible if there exists an oracle polynomial time Turing machine $M$ such that $L(M^{A}) = A$ with the restriction that for all $x$, $M^{A}(x)$ does not query whether $x$ is in $A$ \cite{BU00}.
+When $NL = NP$, Buhrman, Fortnow, van Melkebeek and Torenvliet created a series of constructions to get an $A$ such that: $A$ is in $EXPSPACE$, $A$ is Turing-hard for $EXPSPACE$ and $A$ $``$diagonalizes$"$ against all possible auto-reductions \cite{BU00}.
+
 \bibliography{manuscript}

### 2019-12-26 doc/manuscript.tex
Fixed style doc

@@
 A set $A$ is auto-reducible if there exists an oracle polynomial time Turing machine $M$ such that $L(M^{A}) = A$ with the restriction that for all $x$, $M^{A}(x)$ does not query whether $x$ is in $A$ \cite{BU00}.
-When $NL = NP$, Buhrman, Fortnow, van Melkebeek and Torenvliet created a series of constructions to get an $A$ such that: $A$ is in $EXPSPACE$, $A$ is Turing-hard for $EXPSPACE$ and $A$ $``$diagonalizes$"$ against all possible auto-reductions \cite{BU00}.
+When $NL = NP$, Buhrman, Fortnow, van Melkebeek and Torenvliet created a series of constructions to get an $A$ such that $A$ is in $EXPSPACE$, $A$ is Turing-hard for $EXPSPACE$ and $A$ $``$diagonalizes$"$ against all possible auto-reductions \cite{BU00}.
 

### 2019-12-26 doc/manuscript.tex
Added some technical content

@@
 Certainly, the calculation and store of the bit-length of the elements in $C$ could be done in logarithmic space since this is a unique value.
-On the one hand, we can count and store the number of elements that we read from the input and multiply it by $3$ to finally compare its bit-length with the stored bit-length, since the cardinality of $C$ multiplied by $3$ could be stored in a binary number of bit-length that is logarithmic in relation to the encoded length of $C$.
+On the one hand, we can count and store the number of elements that we read from the input and multiply it by $3$ to finally compare its bit-length with the stored unique bit-length from the elements of the collection, since the cardinality of $C$ multiplied by $3$ could be stored in a binary number of bit-length that is logarithmic in relation to the encoded length of $C$.
 On the other hand, the two elements $a$ and $b$ that we pick from $C$ have a logarithmic space in relation to the encoded length of $C$, because of every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$.

### 2019-12-26 doc/manuscript.tex
Improving the doc

@@
 Since the polynomial time reduction in Theorem \ref{completeness} could be easily transformed in a logarithmic space reduction, then the $\textit{NP--complete}$ problem in Theorem \ref{neg-implication}, that would be $MAX\oplus2SAT$, is necessarily in $NL$ and thus all the problems in $NP$ when $L \neq NL$, because of the Cook's Theorem can also be transformed in a logarithmic space reduction \cite{GJ79}.
-For the same reason, the $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$.
+Certainly, every $NP$ problem could be logarithmic space reduced to $SAT$ by the Cook's Theorem algorithm and $SAT$ can be indeed logarithmic space reduced to $\textit{NAE 3SAT}$ \cite{GJ79}.
+For the same reason, the $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$, since the problem $UNSAT$ can be actually logarithmic space reduced to $3UNSAT$ \cite{GJ79}.
 Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $NL$ is equal to $NP$.
@@
 We also prove that $NL = NP$.
-There are several important consequences from this result, but we will only mention one of the principal outcomes, that is the Theorem Buhrman-Fortnow-van Melkebeek-Torenvliet \cite{BU00}.
-A set $A$ is auto-reducible if there exists an oracle polynomial time Turing machine $M$ such that $L(M^{A}) = A$ with the restriction that for all $x$, $M^{A}(x)$ does not query whether $x$ is in $A$ \cite{BU00}.
-When $NL = NP$, Buhrman, Fortnow, van Melkebeek and Torenvliet created a series of constructions to get an $A$ such that $A$ is in $EXPSPACE$, $A$ is Turing-hard for $EXPSPACE$ and $A$ $``$diagonalizes$"$ against all possible auto-reductions \cite{BU00}.
+There are several important consequences from this result, but we will only mention one of the principal outcomes, that would be the application of Theorem Buhrman-Fortnow-van Melkebeek-Torenvliet when $NL = NP$ \cite{BU00}.
 

### 2019-12-27 doc/manuscript.tex
Added a comma
Fixed some details

@@
 The certificate-based definition of $NL$ assumes that a logarithmic space Turing machine has another separated read-only tape \cite{AB09}.
-On each step of the machine the machine's head on that tape can either stay in place or move to the right \cite{AB09}.
+On each step of the machine, the machine's head on that tape can either stay in place or move to the right \cite{AB09}.
 In particular, it cannot reread any bit to the left of where the head currently is \cite{AB09}.
@@
 \begin{proof}
-We can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis1} by a nondeterministic logarithmic space Turing machine $N$, such that $N(w) = y$ since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$ \cite{Pap03}.
+We can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis1} by a nondeterministic logarithmic space Turing machine $N$ such that $N(w) = y$, since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$ \cite{Pap03}.
 Certainly, we can simulate the reading of one symbol from the string $u$ into the read-once tape just nondeterministically generating the same symbol in the work tapes using a logarithmic space \cite{Pap03}.
@@
 Certainly, every $NP$ problem could be logarithmic space reduced to $SAT$ by the Cook's Theorem algorithm and $SAT$ can be indeed logarithmic space reduced to $\textit{NAE 3SAT}$ \cite{GJ79}.
-For the same reason, the $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$, since the problem $UNSAT$ can be actually logarithmic space reduced to $3UNSAT$ \cite{GJ79}.
+For the same reason, the $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$, because of the problem $UNSAT$ can be actually logarithmic space reduced to $3UNSAT$ \cite{GJ79}.
 Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $NL$ is equal to $NP$.

### 2019-12-30 doc/manuscript.tex
Modified a single sentence

@@
 We can accept the elements of the language $L_{1} \in 1NL$ by a nondeterministic one-way logarithmic space Turing machine $M'$.
-In this way, there is a nondeterministic logarithmic space Turing machine $M''(w, u) = M'(M(w, u))$ which will accept when $w \in L_{2}$ for all the appropriated disqualification $u$.
+In this way, there is a nondeterministic logarithmic space Turing machine $M''(w, u) = M'(M(w, u))$ which will accept when $w \in L_{2}$ for all the appropriated disqualification $u$, where $u$ is placed on the special read-once tape of $M''$.
 The reason is because we can simulate the output string of $M(w, u)$ within a read-once tape and thus, we can compute in a nondeterministic logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}.

### 2019-12-31 doc/manuscript.tex
Finalized the doc proof

@@
 This consists in knowing the answer of the following question: Is P equal to NP?
-A precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin.
+It was essentially mentioned in 1955 from a letter written by John Nash to the United States National Security Agency.
+However, a precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin.
 Since that date, all efforts to find a proof for this problem have failed.
 Another major complexity classes are L and NL.
+Whether L = NL is another fundamental question that it is as important as it is unresolved.
 We demonstrate if L is not equal to NL, then P = NP.
@@
 It is one of the seven Millennium Prize Problems selected by the Clay Mathematics Institute to carry a US\$1,000,000 prize for the first correct solution \cite{CS00}.
-It was essentially mentioned in 1955 from a letter written by John Nash to the United States National Security Agency \cite{AS17}.
-However, the precise statement of the $P=NP$ problem was introduced in 1971 by Stephen Cook in a seminal paper \cite{CS00}.
+The precise statement of the $P=NP$ problem was introduced in 1971 by Stephen Cook in a seminal paper \cite{CS00}.
 In 2012, a poll of 151 researchers showed that 126 (83\%) believed the answer to be no, 12 (9\%) believed the answer is yes, 5 (3\%) believed the question may be independent of the currently accepted axioms and therefore impossible to prove or disprove, 8 (5\%) said either do not know or do not care or don't want the answer to be yes nor the problem to be resolved \cite{GA12}.
+
+The $P = NP$ question is also singular in the number of approaches that researchers have brought to bear upon it over the years \cite{DEO10}.
+From the initial question in logic, the focus moved to complexity theory where early work used diagonalization and relativization techniques \cite{DEO10}.
+It was showed that these methods were perhaps inadequate to resolve $P$ versus $NP$ by demonstrating relativized worlds in which $P = NP$ and others in which $P \neq NP$ \cite{BA75}.
+This shifted the focus to methods using circuit complexity and for a while this approach was deemed the one most likely to resolve the question \cite{DEO10}.
+Once again, a negative result showed that a class of techniques known as $``$Natural Proofs$"$ that subsumed the above could not separate the classes $NP$ and $P$, provided one-way functions exist \cite{RAZ97}.
+There has been speculation that resolving the $P = NP$ question might be outside the domain of mathematical techniques \cite{DEO10}.
+More precisely, the question might be independent of standard axioms of set theory.
+Some results have showed that some relativized versions of the $P = NP$ question are independent of reasonable formalizations of set theory \cite{HOP76}.
+
 It is fully expected that $P \neq NP$ \cite{Pap03}.
@@
 
-\begin{enumerate}
-\item Cryptography, for example, relies on certain problems being difficult.
+Cryptography, for example, relies on certain problems being difficult.
 A constructive and efficient solution to an $\textit{NP--complete}$ problem such as $3SAT$ will break most existing cryptosystems including: Public-key cryptography \cite{HW97}, symmetric ciphers \cite{MM00} and one-way functions used in cryptographic hashing \cite{DKV07}.
 These would need to be modified or replaced by information-theoretically secure solutions not inherently based on $\textit{P--NP}$ equivalence.
-\item There are enormous positive consequences that will follow from rendering tractable many currently mathematically intractable problems.
+
+There are enormous positive consequences that will follow from rendering tractable many currently mathematically intractable problems.
 For instance, many problems in operations research are $\textit{NP--complete}$, such as some types of integer programming and the traveling salesman problem \cite{GJ79}.
@@
 Many other important problems, such as some problems in protein structure prediction, are also $\textit{NP--complete}$, so this will spur considerable advances in biology \cite{BL98}.
-\item Since all the $\textit{NP--complete}$ optimization problems become easy, everything will be much more efficient \cite{LF09}.
+
+Since all the $\textit{NP--complete}$ optimization problems become easy, everything will be much more efficient \cite{LF09}.
 Transportation of all forms will be scheduled optimally to move people and goods around quicker and cheaper \cite{LF09}.
@@
 We will also have much better predictions of weather and earthquakes and other natural phenomenon \cite{LF09}.
-\item There would be disruption, including maybe displacing programmers \cite{IMP95}.
+
+There would be disruption, including maybe displacing programmers \cite{IMP95}.
 The practice of programming itself would be more about gathering training data and less about writing code \cite{IMP95}.
 Google would have the resources to excel in such a world \cite{IMP95}.
-\item But such changes may pale in significance compared to the revolution an efficient method for solving $\textit{NP--complete}$ problems will cause in mathematics itself \cite{CS00}.
+
+But such changes may pale in significance compared to the revolution an efficient method for solving $\textit{NP--complete}$ problems will cause in mathematics itself \cite{CS00}.
 Research mathematicians spend their careers trying to prove theorems, and some proofs have taken decades or even centuries to find after problems have been stated \cite{AS17}.
@@
 A method that is guaranteed to find proofs to theorems, should one exist of a $``$reasonable$"$ size, would essentially end this struggle \cite{CS00}.
-\end{enumerate}
 

### 2020-01-05 doc/manuscript.tex
Example of disqualification

@@
 There has been speculation that resolving the $P = NP$ question might be outside the domain of mathematical techniques \cite{DEO10}.
-More precisely, the question might be independent of standard axioms of set theory.
+More precisely, the question might be independent of standard axioms of set theory \cite{DEO10}.
 Some results have showed that some relativized versions of the $P = NP$ question are independent of reasonable formalizations of set theory \cite{HOP76}.
@@
 \end{definition}
+
+For example, there is a well-known $coNL$ problem that states: Given a directed graph $G = (V, E)$ and two nodes $s, t \in V$, is there no possible path from $s$ to $t$?
+In that problem, an appropriated disqualification $u$ is a sequence of nodes contained in $V$ when $s$ is the first node and $t$ is the last one such that this sequence of nodes is not a path: There is at least two consecutive pair of nodes in the sequence where they are not connected by an edge.
 

### 2020-01-07 doc/manuscript.tex
Updated doc.

@@
 For example, there is a well-known $coNL$ problem that states: Given a directed graph $G = (V, E)$ and two nodes $s, t \in V$, is there no possible path from $s$ to $t$?
-In that problem, an appropriated disqualification $u$ is a sequence of nodes contained in $V$ when $s$ is the first node and $t$ is the last one such that this sequence of nodes is not a path: There is at least two consecutive pair of nodes in the sequence where they are not connected by an edge.
+In that problem, an appropriated disqualification $u$ is a sequence of nodes contained in $V$ when $s$ is the first node and $t$ is the last one such that this sequence of nodes is not a path: There is at least a consecutive pair of nodes in the sequence where they are not connected by an edge.
 
@@
 \begin{definition}
-$\textbf{MAXIMUM EXCLUSIVE-OR 2-SATISFIABILITY}$
+$\textbf{MAXIMUM EXCLUSIVE-OR 2SAT}$
 

### 2020-01-09 doc/manuscript.tex
Fixed detail
Fixed technical detail

@@
 Hartmanis and Mahaney have also shown with their result that if $1NL \subseteq L$ or even $1NL \subset L$, then $L=NL$, because they proved there is a complete problem for both $1NL$ and $NL$ at the same time \cite{HM81}.
-If this way, if $L \neq NL$, then $L \subset 1NL$ by contraposition \cite{Pap03}.
+In this way, if $L \neq NL$, then $L \subset 1NL$ by contraposition \cite{Pap03}.
 Since we already obtained that $P = NP$ under the assumption that $L \subset 1NL$, therefore if $L \neq NL$, then $P = NP$.
@@
 Therefore, we obtain the array $A$ would be valid according to the Theorem \ref{proof} when:
-\[(\psi, K) \in MAX\oplus2SAT \textit{ if and only if } \phi \in \textit{XOR 2SAT}.\]
+\[(\psi, K) \in MAX\oplus2SAT \textit{ if and only if } (\exists \textit{ array } A \textit{ such that } \phi \in \textit{XOR 2SAT}).\]
 Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right.
@@
 Therefore, we obtain that all the appropriated array $A$ would be valid according to the Theorem \ref{demonstration} when:
-\[\phi \in 3UNSAT \textit{ if and only if } C \in \textit{SUM--ZERO}\]
+\[\phi \in 3UNSAT \textit{ if and only if } (\forall \textit{ appropriated array } A \textit{ such that } C \in \textit{SUM--ZERO})\]
 since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value.

### 2020-01-10 doc/manuscript.tex
Fixed details

@@
 \[L(M) = \{w \in \Sigma^{*}: M(w)=``yes" \}.\]
-We denote by $t_{M}(w)$ the number of steps in the computation of $M$ on input $w$ \cite{AB09}. For $n \in \mathbb{N}$ we denote by $T_{M}(n)$ the worst case run time of $M$; that is:
+Moreover, $L(M)$ is decided by $M$, when $w \notin L(M)$ if and only if $M(w)=``no"$ \cite{CLRS01}.
+We denote by $t_{M}(w)$ the number of steps in the computation of $M$ on input $w$ \cite{AB09}.
+For $n \in \mathbb{N}$ we denote by $T_{M}(n)$ the worst case run time of $M$; that is:
 \[T_{M}(n) = max\{t_{M}(w): w \in \Sigma^{n} \}\]
@@
 \begin{definition}
-We will extend the definition of succinct disqualification for an element $w \in L_{2}$ when $L_{2} \in coNP$ as the polynomially bounded string $c$ such that $M(w, c) = ``no"$ and $M$ is the polynomial time verifier of the complement of $L_{2}$ in $NP$.
+We will extend the definition of succinct disqualification for an element $w \in L_{2}$ when $L_{2} \in coNP$ as the polynomially bounded string $c$ by $w$ such that $M(w, c) = ``no"$ and $M$ is the polynomial time verifier of the complement of $L_{2}$ in $NP$.
 \end{definition}

### 2020-01-10 doc/manuscript.tex
Fixed another detail

@@
 \[\phi \in 3UNSAT \textit{ if and only if } (\forall \textit{ appropriated array } A \textit{ such that } C \in \textit{SUM--ZERO})\]
-since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value.
+since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value, respectively.
 Furthermore, we can make this disqualification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$.

### 2020-01-10 doc/manuscript.tex
Fixed other details

--- 2020-01-10 doc/manuscript.tex
@@
 Therefore, we obtain the array $A$ would be valid according to the Theorem \ref{proof} when:
-\[(\psi, K) \in MAX\oplus2SAT \textit{ if and only if } (\exists \textit{ array } A \textit{ such that } \phi \in \textit{XOR 2SAT}).\]
+\[(\psi, K) \in MAX\oplus2SAT \Leftrightarrow (\exists \textit{ appropriated array } A \textit{ such that } \phi \in \textit{XOR 2SAT}).\]
 Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right.
@@
 Therefore, we obtain that all the appropriated array $A$ would be valid according to the Theorem \ref{demonstration} when:
-\[\phi \in 3UNSAT \textit{ if and only if } (\forall \textit{ appropriated array } A \textit{ such that } C \in \textit{SUM--ZERO})\]
-since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value.
+\[\phi \in 3UNSAT \Leftrightarrow (\forall \textit{ appropriated array } A \textit{ such that } C \in \textit{SUM--ZERO})\]
+since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value, respectively.
 Furthermore, we can make this disqualification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$.

### 2020-01-10 doc/presentation.tex
Final presentation

--- 2019-11-17 doc/presentation.tex
@@
 \setbeamertemplate{theorems}[numbered]
+\newtheorem{hypothesis}[theorem]{Hypothesis}
 
@@
 
-\subtitle{The proof on \url{https://www.preprints.org/manuscript/201908.0037/v1} \cite{PFV19}}
+%\subtitle{}
 
@@
 
-%\address{Copsonic, 1471 Route de St-Nauphary, 82000 Montauban, France}
+%\address{}
 
 %\email{vega.frank@gmail.com}
-
-%\subjclass[2000]{Primary 68Q15}
-
-\keywords{complexity classes, completeness, verifier, reduction, polynomial time, logarithmic space}
 
@@
 
-\begin{frame}{Another definition of $NP$}
+\begin{frame}{$L$ versus $NL$}
 
-We can define an $NP$ problem as
-
-\[L2 = \{w: M(w, c) = y \textit{ where } y \in L1\} (\textit{y is the output in the halting state})\]
-
-when $L1$ is a language in $P$, $M$ is a deterministic Turing machine that runs in polynomial time in the length of $w$ and $c$ (the certificate) is polynomially bounded by $w$.
+A logarithmic space Turing machine has a read-only input tape, a write-only output tape, and read/write work tapes.
+The work tapes may contain at most $O(\log n)$ symbols.
+In computational complexity theory, $L$ is the complexity class containing those decision problems that can be decided by a deterministic logarithmic space Turing machine.
+$NL$ is the complexity class containing the decision problems that can be decided by a nondeterministic logarithmic space Turing machine.
+Whether $L = NL$ is another fundamental question that it is as important as it is unresolved.
 
@@
 
-\begin{frame}{Equivalent definition}
+\begin{frame}{The problem $\textit{XOR 2SAT}$}
 
-This is easy to prove since the polynomial time composition reduction can be done in polynomial time.
-Therefore, the previous definition complies with the existence of a polynomial time verifier $M’$ such that the $NP$ problem $L2$ is defined as
-
-\[L2 = \{w: M'(w, c) = ``yes"\} (\textit{``yes" is the acceptance state})\]
-
-where the computation of $M'(w, c)$ is equal to $N(M(w, c))$ when $N$ is the Turing machine which accepts $L1$ in polynomial time.
+We denote the $XOR$ function as $\oplus$.
+The $\textit{XOR 2SAT}$ problem will be equivalent to $\textit{XOR SAT}$, but the clauses in the formula have exactly two distinct literals.
+$\textit{XOR 2SAT}$ is in $L$.
 
@@
 
-\begin{frame}{The logarithmic space verifier}
+\begin{frame}{A certificate-based definition for $NL$}
 
-On the other hand, the verifier for a language in $NL$ (nondeterministic logarithmic space class) has as premise that the certificate c is placed in a special tape that is read only and read at once (that means we cannot read to the left).
+We can give a certificate-based definition for $NL$.
+The certificate-based definition of $NL$ assumes that a logarithmic space Turing machine has another separated read-only tape.
+On each step of the machine, the machine's head on that tape can either stay in place or move to the right.
+In particular, it cannot reread any bit to the left of where the head currently is.
+For that reason this kind of special tape is called $``$read-once$"$.
 
@@
 
-\begin{frame}{Our result}
+\begin{frame}{Definition of an $NL$ problem}
+
+\begin{definition}
+A language $L_{1}$ is in $NL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$:
+\[x \in L_{1} \Leftrightarrow \exists u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = ``yes" \]
+where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the certificate $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function.
+$M$ is called a logarithmic space verifier.
+\end{definition}
+
+\end{frame}
+
+\begin{frame}{Hypothesis \ref{hypothesis1}}
+
+\begin{hypothesis}
+\label{hypothesis1}
+Given a nonempty language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
+\[L_{2} = \{w: M(w, u) = y, \ \exists \textit{ string } u \textit{ such that } y \in L_{1}\}\]
+when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
+In this way, there is an $\textit{NP--complete}$ language defined by a logarithmic space verifier $M$ such that when the input is an element of the language with its certificate, then $M$ outputs a string which belongs to a single language in $L$.
+\end{hypothesis}
+
+\end{frame}
+
+\begin{frame}{Two-way and one-way Turing machines}
+
+From the early days of automata and complexity  theory,  two  different  models  of  Turing  machines  are  considered, the offline and online machines.
+Each model has a read-only input tape and some work tapes.
+The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left.
+In the terminology of the (generalized) Turing machine models are called two-way and one-way Turing machines, respectively.
+
+\end{frame}
+
+\begin{frame}{One-way logarithmic space Turing machine}
+
+Hartmanis and Mahaney have investigated the classes $1L$ and $1NL$ of languages recognizable by deterministic one-way logarithmic space Turing machine and nondeterministic one-way logarithmic space Turing machine, respectively.
+They have shown that $1L \neq 1NL$ (by looking at a uniform variant of the string non-equality problem from communication complexity theory) and have defined a natural complete problem for $1NL$ under deterministic one-way logarithmic space reductions.
+Furthermore, they have proven that $1NL \subseteq L$ if and only if $L=NL$.
+
+\end{frame}
+
+\begin{frame}{When the Hypothesis \ref{hypothesis1} is true}
 
 \begin{theorem}
-\label{result}
-In our work was proved that we can define an $\textit{NP--complete}$ problem as
-
-\[L2 = \{w: M(w, c) = y \textit{ where } y \in L1\} (\textit{y is the output in the halting state})\]
-
-when $L1$ is a language in $L$ (deterministic logarithmic space class), $M$ is a deterministic Turing machine that runs in logarithmic space in the length of $w$ and $c$ (the certificate) is polynomially bounded by $w$ such that $c$ is placed in the special tape in $M$ that is read only and read at once.
+\label{neg-implication}
+If the Hypothesis \ref{hypothesis1} is true, therefore when $L \neq NL$, then $P = NP$.
 \end{theorem}
@@
 
-\begin{frame}{Converting the verifier}
+\begin{frame}{Proof}
 
-We can simulate the computation $M(w, c) = y$ by a nondeterministic logarithmic space Turing machine $N$, such that $N(w) = y$ since we can read the certificate string $c$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $c$.
-Certainly, we can simulate the reading of one symbol from the string $c$ into the read-once tape just nondeterministically generating the same symbol in the work tapes using a logarithmic space.
+We can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis1} by a nondeterministic logarithmic space Turing machine $N$ such that $N(w) = y$, since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$.
+Certainly, we can simulate the reading of one symbol from the string $u$ into the read-once tape just nondeterministically generating the same symbol in the work tapes using a logarithmic space.
 
@@
 
-\begin{frame}{The classes $1L$ and $1NL$}
+\begin{frame}{Proof}
 
-\begin{definition}
-Hartmanis and Mahaney have investigated the classes 1L and 1NL of languages recognizable by deterministic one-way logarithmic space Turing machine and nondeterministic one-way logarithmic space Turing machine, respectively.
-The one-way machines are not allowed to move the input head to the left.
-\end{definition}
+If we suppose that $L \subset 1NL$, then we can accept the elements of the language $L_{1} \in L$ by a nondeterministic one-way logarithmic space Turing machine $M'$.
+In this way, there is a nondeterministic logarithmic space Turing machine $M''(w) = M'(N(w))$ which will accept when $w \in L_{2}$.
+Consequently, $M''$ is a nondeterministic logarithmic space Turing machine which decides the language $L_{2}$.
 
@@
 
-\begin{frame}{Supposition}
-
-If we suppose that $L \subset 1NL$, then we can accept the elements of the language $L1 \in L$ by a nondeterministic one-way logarithmic space Turing machine $M'$.
-In this way, there is a nondeterministic logarithmic space Turing machine $M''(w) = M'(N(w))$ which will halt in the acceptance state when $w \in L2$.
-Consequently, $M''$ is a nondeterministic logarithmic space Turing machine which decides the language $L2$.
-
-\end{frame}
-
-\begin{frame}{The arguments}
+\begin{frame}{Proof}
 
@@
 
-\begin{frame}{Consequences}
+\begin{frame}{Proof}
 
-Therefore, $L2 \in NL$ and thus, $L2 \in P$ due to $NL \subseteq P$.
+Therefore, $L_{2}$ is in $NL$ and thus, $L_{2} \in P$ due to $NL \subseteq P$.
 If any single $\textit{NP--complete}$ problem can be solved in polynomial time, then $P = NP$.
-Since $L2 \in P$ and $L2 \in \textit{NP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that $L \subset 1NL$.
-Hartmanis and Mahaney have also shown with their result that if $1NL$ is a subset of $L$, then $L=NL$, because they proved there is a complete problem for both $1NL$ and $NL$ at the same time.
-If this way, if $L \neq NL$, then $L \subset 1NL$ by contraposition.
-Since we already obtained that $P = NP$ under the assumption that $L \subset 1NL$, therefore if $L \neq NL$, then $P = NP$.
+Since $L_{2} \in P$ and $L_{2} \in \textit{NP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that $L \subset 1NL$.
 
@@
 
-\begin{frame}{The complexity class $LNL$}
+\begin{frame}{Proof}
+
+Hartmanis and Mahaney have also shown with their result that if $1NL \subseteq L$ or even $1NL \subset L$, then $L=NL$, because they proved there is a complete problem for both $1NL$ and $NL$ at the same time.
+In this way, if $L \neq NL$, then $L \subset 1NL$ by contraposition.
+Since we already obtained that $P = NP$ under the assumption that $L \subset 1NL$, therefore if $L \neq NL$, then $P = NP$.
+\qed
+
+\end{frame}
+
+\begin{frame}{Definition of a $coNL$ problem}
 
 \begin{definition}
-\label{definition}
-The class $LNL$ contains those languages that are decided by a nondeterministic logarithmic space Turing machine $N$ such that for every element $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves strictly deterministically on $y$ and strictly nondeterministically on $z$ when strictly deterministically means there is no a possible nondeterministic step and strictly nondeterministically means there is at least one nondeterministic step on the computation.
+A language $L_{1}$ is in $coNL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$:
+\[x \in L_{1} \Leftrightarrow \forall \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ then } M(x, u) = ``yes" \]
+where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the disqualification $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function.
+$M$ is called a logarithmic space disqualifier.
 \end{definition}
@@
 
-\begin{frame}{The class $BNL$}
+\begin{frame}{Example}
 
-Sauerhoff has shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input ($``$nondeterminism at the beginning$"$).
+For example, there is a well-known $coNL$ problem that states: Given a directed graph $G = (V, E)$ and two nodes $s, t \in V$, is there no possible path from $s$ to $t$?
+In that problem, an appropriated disqualification $u$ is a sequence of nodes contained in $V$ when $s$ is the first node and $t$ is the last one such that this sequence of nodes is not a path: There is at least a consecutive pair of nodes in the sequence where they are not connected by an edge.
 
@@
 
-\begin{frame}{Proof of $LNL = NL$}
+\begin{frame}{Hypothesis \ref{hypothesis2}}
 
-We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string.
-Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the elements $x = yz$).
-Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines.
-Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$.
-\end{frame}
-
-\begin{frame}{Proof of $L \neq NL$}
-
-However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ in some languages in $BNL$ when the prefix $y$ is the empty string, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$.
-Hence, we obtain that $BNL \neq NL$ by transitivity.
-Nevertheless, Sauerhoff has also shown that $L \subseteq BNL \subseteq NL$.
-Consequently, we prove the complexity class $L$ is not equal to $NL$.
+\begin{hypothesis}
+\label{hypothesis2}
+Given a nonempty language $L_{1} \in 1NL$, there is a language $L_{2}$ in $\textit{coNP--complete}$ with a deterministic Turing machine $M$, where:
+\[L_{2} = \{w: M(w, u) = y, \ \forall \textit{ appropriated string } u \textit{ such that } y \in L_{1}\}\]
+when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
+In this way, there is a $\textit{coNP--complete}$ language defined by a logarithmic space disqualifier $M$ such that when the input is an element of the language with any of its appropriated disqualification, then $M$ always outputs a string which belongs to a single language in $1NL$.
+\end{hypothesis}
 
@@
 
-\begin{frame}{Conclusion: $P = NP$}
+\begin{frame}{When the Hypothesis \ref{hypothesis2} is true}
 
-Since we show that $L \neq NL$, then we prove the complexity class $P$ is equal to $NP$.
+\begin{theorem}
+\label{pos-implication}
+If the Hypothesis \ref{hypothesis2} is true, therefore when $L = NL$, then $P = NP$.
+\end{theorem}
 
@@
 
-\begin{frame}{Code}
+\begin{frame}{Proof}
 
-In this Scala Project \cite{GFV19}, we use the Assertion on the properties of the instances of each problem and the Unit Test for checking the correctness of the Theorem \ref{result}.
-We need to install JDK 8 in order to test the Scala Project.
-In addition, we need to install SBT to run the unit test (we could run the unit test with the $\textbf{sbt test}$ command).
+We can accept the elements of the language $L_{1} \in 1NL$ by a nondeterministic one-way logarithmic space Turing machine $M'$.
+In this way, there is a nondeterministic logarithmic space Turing machine $M''(w, u) = M'(M(w, u))$ which will accept when $w \in L_{2}$ for all the appropriated disqualification $u$, where $u$ is placed on the special read-once tape of $M''$.
 
@@
 
-\begin{frame}{References}
+\begin{frame}{Proof}
 
-\begin{thebibliography}{1}
+The reason is because we can simulate the output string of $M(w, u)$ within a read-once tape and thus, we can compute in a nondeterministic logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation.
+Certainly, we do not need to reset the computation of $M(w, u)$ for the reading at once of a symbol in the output string of $M(w, u)$ by the nondeterministic one-way logarithmic space Turing machine $M'$.
 
-\bibitem{PFV19}
-Frank Vega.
-\newblock Logarithmic Space Verifiers on NP-complete.
-\newblock In {\em Preprints}, 2019, 2019080037.
-\newblock \href {https://doi.org/10.20944/preprints201908.0037.v1}
-  {\path{doi:10.20944/preprints201908.0037.v1}}.
+\end{frame}
 
-\bibitem{GFV19}
-Frank Vega.
-\newblock Verify{R}eduction, August 2019.
-\newblock In a GitHub repository at
-  \url{https://github.com/frankvegadelgado/VerifyReduction}.
+\begin{frame}{Proof}
 
-\end{thebibliography}
+Consequently, $M''$ can be converted into a logarithmic space disqualifier for the language $L_{2}$ just assuming that $L = NL$, because of the nondeterministic logarithmic space Turing machine $M''$ could be simulated by a deterministic logarithmic space Turing machine.
+Therefore, $L_{2}$ is in $coNL$ and thus, $L_{2} \in P$ due to $coNL \subseteq P$.
+If any single $\textit{coNP--complete}$ problem can be solved in polynomial time, then $P = NP$.
+Since $L_{2} \in P$ and $L_{2} \in \textit{coNP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that $L = NL$.
+\qed
+
+\end{frame}
+
+\begin{frame}{$\textbf{NAE 3SAT}$}
+
+\begin{definition}
+INSTANCE: A Boolean formula $\phi$ in $3CNF$.
+
+QUESTION: Is there a truth assignment for $\phi$ such that each clause has at least one true literal and at least one false literal?
+
+REMARKS: $\textit{NAE 3SAT} \in \textit{NP--complete}$.
+\end{definition}
+
+\end{frame}
+
+\begin{frame}{$\textbf{MAXIMUM EXCLUSIVE-OR 2SAT}$}
+
+\begin{definition}
+INSTANCE: A positive integer $K$ and a Boolean formula $\phi$ that is an instance of $\textit{XOR 2SAT}$.
+
+QUESTION: Is there a truth assignment in $\phi$ such that at most $K$ clauses are unsatisfied?
+
+REMARKS: We denote this problem as $MAX\oplus2SAT$.
+\end{definition}
+
+\end{frame}
+
+\begin{frame}{$\textit{NP--completeness}$}
+
+\begin{theorem}
+\label{completeness}
+$MAX\oplus2SAT \in \textit{NP--complete}$.
+\end{theorem}
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+It is trivial to see $MAX\oplus2SAT \in NP$.
+Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we create three new variables $a_{c_{i}}$, $b_{c_{i}}$ and $d_{c_{i}}$ for each clause $c_{i} = (x \vee y \vee z)$ in $\phi$, where $x$, $y$ and $z$ are literals, in the following formula:
+\[P_{i} = (a_{c_{i}} \oplus b_{c_{i}}) \wedge (b_{c_{i}} \oplus d_{c_{i}}) \wedge (a_{c_{i}} \oplus d_{c_{i}}) \wedge (x \oplus a_{c_{i}}) \wedge (y \oplus b_{c_{i}}) \wedge (z \oplus d_{c_{i}}).\]
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+We can see $P_{i}$ has at most one unsatisfied clause for some truth assignment if and only if at least one member of $\{x,y,z\}$ is true and at least one member of $\{x,y,z\}$ is false for the same truth assignment.
+Hence, we can create the Boolean formula $\psi$ as the conjunction of the $P_{i}$ formulas for every clause $c_{i}$ in $\phi$, such that $\psi = P_{1} \wedge \ldots \wedge P_{m}$.
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+Finally, we obtain that:
+\[\phi \in \textit{NAE 3SAT} \textit{ if and only if } (\psi, m) \in MAX\oplus2SAT.\]
+Consequently, we prove $\textit{NAE 3SAT} \leq_{p} MAX\oplus2SAT$ where we already know the language $\textit{NAE 3SAT} \in \textit{NP--complete}$.
+To sum up, we show $MAX\oplus2SAT \in \textit{NP--hard}$ and $MAX\oplus2SAT \in NP$ and thus, $MAX\oplus2SAT \in \textit{NP--complete}$.
+\qed
+
+\end{frame}
+
+\begin{frame}{Hypothesis \ref{hypothesis1} proof}
+
+\begin{theorem}
+\label{proof}
+There is a deterministic Turing machine $M$, where:
+\[MAX\oplus2SAT = \{w: M(w, u) = y, \exists \textit{ string } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
+when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
+\end{theorem}
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+Given a valid instance $(\psi, K)$ for $MAX\oplus2SAT$ when $\psi$ has $m$ clauses, we can create a certificate array $A$ which contains $K$ different natural numbers in ascending order which represents the indexes of the clauses in $\psi$ that we are going to remove from the instance.
+We read at once the elements of the array $A$ and we reject whether this is not an appropriated certificate: That is when the numbers are not sorted in ascending order, or the array $A$ does not contain exactly $K$ elements, or the array $A$ contains a number that is not between $1$ and $m$.
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MAX\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$.
+Therefore, we obtain the array $A$ would be valid according to the Theorem \ref{proof} when:
+\[(\psi, K) \in MAX\oplus2SAT \Leftrightarrow (\exists \textit{ appropriated array } A \textit{ such that } \phi \in \textit{XOR 2SAT}).\]
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right.
+Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated certificate and also remove the $K$ different clauses from the Boolean formula $\psi$ when we write the final clauses to the output.
+\qed
+
+\end{frame}
+
+\begin{frame}{$\textbf{3UNSAT}$}
+
+\begin{definition}
+INSTANCE: A Boolean formula $\phi$ in $3CNF$.
+
+QUESTION: Is $\phi$ unsatisfiable?
+
+REMARKS: $3UNSAT \in \textit{coNP--complete}$.
+\end{definition}
+
+\end{frame}
+
+\begin{frame}{$\textbf{SUM ZERO}$}
+
+\begin{definition}
+INSTANCE: A collection of integers $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we do not take into account the symbol minus in counting the bit-length of the negative integers).
+
+QUESTION: Are there two elements $a, b \in C$, such that $a + b = 0$?
+
+REMARKS: We denote this problem as $0SUM$.
+\end{definition}
+
+\end{frame}
+
+\begin{frame}{Contained in $1NL$}
+
+\begin{theorem}
+\label{1nl}
+$0SUM \in 1NL$.
+\end{theorem}
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+Given a collection of integers $C$, we can read its elements from left to right, verify that every element is not equal to $0$, check that every element in $C$ has the same bit-length and count the amount of elements in $C$ to finally multiply it by $3$ and compare its bit-length with the single bit-length from the elements in $C$.
+In addition, we can nondeterministically pick two elements $a$ and $b$ from $C$ and accept in case of $a + b = 0$ otherwise we reject.
+We can make all this computation in a nondeterministic one-way using logarithmic space.
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+Certainly, the calculation and store of the bit-length of the elements in $C$ could be done in logarithmic space since this is a unique value.
+On the one hand, we can count and store the number of elements that we read from the input and multiply it by $3$ to finally compare its bit-length with the stored unique bit-length from the elements of the collection, since the cardinality of $C$ multiplied by $3$ could be stored in a binary number of bit-length that is logarithmic in relation to the encoded length of $C$.
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+On the other hand, the two elements $a$ and $b$ that we pick from $C$ have a logarithmic space in relation to the encoded length of $C$, because of every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$.
+Indeed, we never need to read to the left on the input for the acceptance of the elements in $0SUM$ in a nondeterministic logarithmic space.
+\qed
+
+\end{frame}
+
+\begin{frame}{Hypothesis \ref{hypothesis2} proof}
+
+\begin{theorem}
+\label{demonstration}
+There is a deterministic Turing machine $M$, where:
+\[3UNSAT = \{w: M(w, u) = y, \forall \textit{ appropriated string } u \textit{ such that } y \in 0SUM\}\]
+when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
+\end{theorem}
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we can create a disqualification array $A$ which contains $m$ positive integers between $1$ and $3$ which represents the literals of the clauses in $\phi$ which appear from left to right.
+We read at once the elements of the array $A$ and we reject whether this is not an appropriated disqualification: That is when the array $A$ does not contain exactly $m$ elements, or the array $A$ contains a number that is not between $1$ and $3$.
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+While we read the elements of the array $A$, we select from the clauses $\phi$ the literals such that these ones occupy the position that represents the number between $1$ and $3$, that is the first, second or third place within the clause from left to right.
+In this way, we output the selected literals that are represented by a positive or negative (in case of a negated variable) integer just creating another instance $C$ for $0SUM$ where the collection $C$ contains those integers which are the selected literals for each clause in $\phi$.
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+Therefore, we obtain that all the appropriated array $A$ would be valid according to the Theorem \ref{demonstration} when:
+\[\phi \in 3UNSAT \Leftrightarrow (\forall \textit{ appropriated array } A \textit{ such that } C \in 0SUM)\]
+since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value, respectively.
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+Furthermore, we can make this disqualification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$.
+Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated disqualification and pick the $m$ literals from the Boolean formula $\phi$ when we write the final integers that represent these literals to the output.
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+Note, that every possible literal in $\phi$ could have a representation by an integer between $-3 \times m$ and $3 \times m$ with the exception of $0$, where $m$ is the cardinality of the collection $C$.
+In this way, we guarantee the output collection $C$ is an appropriated instance of $0SUM$ just filling with zeroes to the left the elements with bit-length lesser than $|3 \times m|$ where $|\ldots|$ is the bit-length function.
+\qed
+
+\end{frame}
+
+\begin{frame}{Final Result}
+
+\begin{theorem}
+$P = NP$.
+\end{theorem}
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+If $L \neq NL$, then $P = NP$ as a consequence of the Hypothesis \ref{hypothesis1}.
+If $L = NL$, then $P = NP$ as a consequence of the Hypothesis \ref{hypothesis2}.
+Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $P$ is equal to $NP$.
+\qed
+
+\end{frame}
+
+\begin{frame}{THE END}
+
+\begin{center}
+$\textbf{QUESTIONS?}$
+\end{center}
 

### 2020-01-12 doc/manuscript.tex
Finalizing the presentation

@@
 For that reason this kind of special tape is called $``$read-once$"$ \cite{AB09}.
+Besides, in the certificate-based definition of $NL$, we assume the certificate string is appropriated for the instance \cite{Pap03}.
+For example, a truth assignment for a Boolean formula $\phi$ is appropriated for the instance when every possible variable in $\phi$ could be evaluated in that truth assignment string, but we cannot affirm the same for every possible binary string.
 
@@
 A language $L_{1}$ is in $NL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$:
-\[x \in L_{1} \Leftrightarrow \exists u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = ``yes" \]
+\[x \in L_{1} \Leftrightarrow \exists \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = ``yes" \]
 where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the certificate $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function \cite{AB09}.
@@
 Given a nonempty language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
-\[L_{2} = \{w: M(w, u) = y, \exists \textit{ string } u \textit{ such that } y \in L_{1}\}\]
+\[L_{2} = \{w: M(w, u) = y, \exists \textit{ appropriated } u \textit{ such that } y \in L_{1}\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
@@
 Besides, in the disqualification-based definition of $coNL$, we assume the disqualification string is appropriated for the instance \cite{Pap03}.
-For example, a truth assignment for a Boolean formula $\phi$ in $3CNF$ is appropriated for the instance when every possible variable in $\phi$ could be evaluated in that truth assignment string, but we cannot affirm the same for every possible binary string.
 
@@
 \[x \in L_{1} \Leftrightarrow \forall \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ then } M(x, u) = ``yes" \]
-where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the disqualification $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function \cite{AB09}.
+where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the disqualification $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function.
 $M$ is called a logarithmic space disqualifier.
@@
 Given a nonempty language $L_{1} \in 1NL$, there is a language $L_{2}$ in $\textit{coNP--complete}$ with a deterministic Turing machine $M$, where:
-\[L_{2} = \{w: M(w, u) = y, \forall \textit{ appropriated string } u \textit{ such that } y \in L_{1}\}\]
+\[L_{2} = \{w: M(w, u) = y, \forall \textit{ appropriated } u \textit{ such that } y \in L_{1}\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
@@
 There is a deterministic Turing machine $M$, where:
-\[MAX\oplus2SAT = \{w: M(w, u) = y, \exists \textit{ string } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
+\[MAX\oplus2SAT = \{w: M(w, u) = y, \exists \textit{ appropriated } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
@@
 There is a deterministic Turing machine $M$, where:
-\[3UNSAT = \{w: M(w, u) = y, \forall \textit{ appropriated string } u \textit{ such that } y \in \textit{SUM--ZERO}\}\]
+\[3UNSAT = \{w: M(w, u) = y, \forall \textit{ appropriated } u \textit{ such that } y \in \textit{SUM--ZERO}\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.

### 2020-01-12 doc/presentation.tex
Finalizing the presentation

@@
 
-%\subtitle{}
+\subtitle{The $15^{th}$ International Computer Science Symposium in Russia\\
+ $\textbf{(CSR 2020)}$}
 
@@
 
+\begin{frame}{A certificate-based definition for $NL$}
+
+Besides, in the certificate-based definition of $NL$, we assume the certificate string is appropriated for the instance.
+For example, a truth assignment for a Boolean formula $\phi$ is appropriated for the instance when every possible variable in $\phi$ could be evaluated in that truth assignment string, but we cannot affirm the same for every possible binary string.
+
+\end{frame}
+
 \begin{frame}{Definition of an $NL$ problem}
@@
 A language $L_{1}$ is in $NL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$:
-\[x \in L_{1} \Leftrightarrow \exists u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = ``yes" \]
+\[x \in L_{1} \Leftrightarrow \exists \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = ``yes" \]
 where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the certificate $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function.
@@
 Given a nonempty language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
-\[L_{2} = \{w: M(w, u) = y, \ \exists \textit{ string } u \textit{ such that } y \in L_{1}\}\]
+\[L_{2} = \{w: M(w, u) = y, \ \exists \textit{ appropriated } u \textit{ such that } y \in L_{1}\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
@@
 Given a nonempty language $L_{1} \in 1NL$, there is a language $L_{2}$ in $\textit{coNP--complete}$ with a deterministic Turing machine $M$, where:
-\[L_{2} = \{w: M(w, u) = y, \ \forall \textit{ appropriated string } u \textit{ such that } y \in L_{1}\}\]
+\[L_{2} = \{w: M(w, u) = y, \ \forall \textit{ appropriated } u \textit{ such that } y \in L_{1}\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
@@
 There is a deterministic Turing machine $M$, where:
-\[3UNSAT = \{w: M(w, u) = y, \forall \textit{ appropriated string } u \textit{ such that } y \in 0SUM\}\]
+\[3UNSAT = \{w: M(w, u) = y, \forall \textit{ appropriated } u \textit{ such that } y \in 0SUM\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
@@
 
-\begin{frame}{THE END}
+\begin{frame}{$NL$ versus $NP$}
 
-\begin{center}
-$\textbf{QUESTIONS?}$
-\end{center}
+\begin{theorem}
+$NL = NP$.
+\end{theorem}
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+Since the polynomial time reduction in Theorem \ref{completeness} could be easily transformed in a logarithmic space reduction, then the $\textit{NP--complete}$ problem in Theorem \ref{neg-implication}, that would be $MAX\oplus2SAT$, is necessarily in $NL$ and thus all the problems in $NP$ when $L \neq NL$, because of the Cook's Theorem can also be transformed in a logarithmic space reduction.
+Certainly, every $NP$ problem could be logarithmic space reduced to $SAT$ by the Cook's Theorem algorithm and $SAT$ can be indeed logarithmic space reduced to $\textit{NAE 3SAT}$.
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+For the same reason, the $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$, because of the problem $UNSAT$ can be actually logarithmic space reduced to $3UNSAT$.
+Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $NL$ is equal to $NP$.
+\qed
 

### 2020-01-12 doc/presentation.tex
Finalized the presentation

@@
 There is a deterministic Turing machine $M$, where:
-\[MAX\oplus2SAT = \{w: M(w, u) = y, \exists \textit{ appropriated } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
+\[MAX\oplus2SAT = \{w: M(w, u) = y, \exists \textit{ appropriated } u\]
+\[\textit{such that } y \in \textit{XOR 2SAT}\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
@@
 Therefore, we obtain the array $A$ would be valid according to the Theorem \ref{proof} when:
-\[(\psi, K) \in MAX\oplus2SAT \Leftrightarrow (\exists \textit{ appropriated array } A \textit{ such that } \phi \in \textit{XOR 2SAT}).\]
+\[(\psi, K) \in MAX\oplus2SAT \Leftrightarrow (\exists \textit{ appropriated array } A\]
+\[\textit{such that } \phi \in \textit{XOR 2SAT}).\]
 
@@
 
-\begin{frame}{Final Result}
+\begin{frame}{Result}
 

### 2020-02-10 doc/manuscript.tex
Finalized the whole proof

@@
 In this way, we prove the complexity class P is equal to NP.
-Furthermore, we demonstrate the complexity class NL is equal to NP.
+Furthermore, we demonstrate the complexity class L is equal to NP.
 \end{abstract}
@@
 \begin{theorem}
+\label{nl}
 $NL = NP$.
@@
 Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $NL$ is equal to $NP$.
+\end{proof}
+
+\begin{theorem}
+$L = NP$.
+\end{theorem}
+
+\begin{proof}
+Under the assumption of $L \subseteq 1NL$, then we would obtain that $1NL = NL$.
+Certainly, the logarithmic space verifier of Theorem \ref{proof} works into one-way when $L \subseteq 1NL$.
+Indeed, the logarithmic space verifier through the certificate generates the output into one-way according to the arguments provided by the proof in Theorem \ref{proof}.
+Moreover, we know that $\textit{XOR 2SAT} \in 1NL$ under the assumption of $L \subseteq 1NL$, since $\textit{XOR 2SAT}$ is in $L$ \cite{AR00}, \cite{RM08}.
+In this way, we obtain that $MAX\oplus2SAT \in 1NL$.
+Since $MAX\oplus2SAT$ is $\textit{NP--complete}$ under logarithmic space reductions and $NL = NP$ due to Theorem \ref{nl}, then we would deduce that $1NL = NL$, because of every problem in $NP$ could be reduced to $MAX\oplus2SAT$ under $1NL$-reductions.
+However, it is a known result that $1NL \neq NL$ \cite{MI92}.
+Consequently, we obtain that $1NL \subset L$ as a consequence of this contradiction.
+Since $1NL \subset L$ implies $L=NL$ \cite{HM81}, then we have the complexity class $L$ is equal to $NP$.
 \end{proof}
@@
 
-We also prove that $NL = NP$.
-There are several important consequences from this result, but we will only mention one of the principal outcomes, that would be the application of Theorem Buhrman-Fortnow-van Melkebeek-Torenvliet when $NL = NP$ \cite{BU00}.
-
 \bibliography{manuscript}

### 2020-02-10 doc/presentation.tex
Finalized the whole proof

@@
 
-\begin{frame}{$NL$ versus $NP$}
+\begin{frame}{Extended version: $NL$ versus $NP$}
 
 \begin{theorem}
+\label{nl}
 $NL = NP$.
@@
 
+\begin{frame}{Extended version: $L$ versus $NP$}
+
+\begin{theorem}
+$L = NP$.
+\end{theorem}
+
+\end{frame}
+
+\begin{frame}{Proof}
+
+Under the assumption of $L \subseteq 1NL$, then we would obtain that $1NL = NL$.
+Certainly, the logarithmic space verifier of Theorem \ref{proof} works into one-way when $L \subseteq 1NL$.
+Indeed, the logarithmic space verifier through the certificate generates the output into one-way according to the arguments provided by the proof in Theorem \ref{proof}.
+Moreover, we know that $\textit{XOR 2SAT} \in 1NL$ under the assumption of $L \subseteq 1NL$, since $\textit{XOR 2SAT}$ is in $L$.
+In this way, we obtain that $MAX\oplus2SAT \in 1NL$.
+\end{frame}
+
+\begin{frame}{Proof}
+
+Since $MAX\oplus2SAT$ is $\textit{NP--complete}$ under logarithmic space reductions and $NL = NP$ due to Theorem \ref{nl}, then we would deduce that $1NL = NL$, because of every problem in $NP$ could be reduced to $MAX\oplus2SAT$ under $1NL$-reductions.
+However, it is a known result that $1NL \neq NL$.
+Consequently, we obtain that $1NL \subset L$ as a consequence of this contradiction.
+Since $1NL \subset L$ implies $L=NL$, then we have the complexity class $L$ is equal to $NP$.
+\qed
+
+\end{frame}
+
 \end{document}

### 2020-02-25 doc/manuscript.tex
Changed the content.

--- 2020-01-12 doc/manuscript.tex
@@
 
-\keywords{complexity classes, completeness, polynomial time, reduction, logarithmic space, one-way}%TODO mandatory; please add comma-separated list of keywords
+\keywords{complexity classes, completeness, polynomial time, reduction, logarithmic space}%TODO mandatory; please add comma-separated list of keywords
 
@@
 For each string $w$ in $\Sigma^{*}$ there is a computation associated with $M$ on input $w$ \cite{AB09}.
-We say that $M$ accepts $w$ if this computation terminates in the accepting state, that is $M(w)=``yes"$ \cite{AB09}.
-Note that $M$ fails to accept $w$ either if this computation ends in the rejecting state, that is $M(w)=``no"$, or if the computation fails to terminate, or the computation ends in the halting state with some output, that is $M(w)=y$ (when $M$ outputs the string $y$ on the input $w$) \cite{AB09}.
+We say that $M$ accepts $w$ if this computation terminates in the accepting state, that is $M(w)=1$ \cite{AB09}.
+Note that $M$ fails to accept $w$ either if this computation ends in the rejecting state, that is $M(w)=0$, or if the computation fails to terminate, or the computation ends in the halting state with some output, that is $M(w)=y$ (when $M$ outputs the string $y$ on the input $w$) \cite{AB09}.
 
@@
 The language accepted by a Turing machine $M$, denoted $L(M)$, has an associated alphabet $\Sigma$ and is defined by:
-\[L(M) = \{w \in \Sigma^{*}: M(w)=``yes" \}.\]
-Moreover, $L(M)$ is decided by $M$, when $w \notin L(M)$ if and only if $M(w)=``no"$ \cite{CLRS01}.
+\[L(M) = \{w \in \Sigma^{*}: M(w)=1 \}.\]
+Moreover, $L(M)$ is decided by $M$, when $w \notin L(M)$ if and only if $M(w)=0$ \cite{CLRS01}.
 We denote by $t_{M}(w)$ the number of steps in the computation of $M$ on input $w$ \cite{AB09}.
@@
 A verifier for a language $L_{1}$ is a deterministic Turing machine $M$, where:
-\[L_{1} = \{w: M(w, c) = ``yes" \textit{ for some string } c\}.\]
+\[L_{1} = \{w: M(w, c) = 1 \textit{ for some string } c\}.\]
 We measure the time of a verifier only in terms of the length of $w$, so a polynomial time verifier runs in polynomial time in the length of $w$ \cite{AB09}.
@@
 If $NP$ is the class of problems that have succinct certificates, then the complexity class $coNP$ must contain those problems that have succinct disqualifications \cite{Pap03}.
-That is, a $``no"$ instance of a problem in $coNP$ possesses a short proof of its being a $``no"$ instance \cite{Pap03}.
+That is, a rejection instance of a problem in $coNP$ possesses a short proof of its being a rejection instance \cite{Pap03}.
 
 \begin{definition}
-We will extend the definition of succinct disqualification for an element $w \in L_{2}$ when $L_{2} \in coNP$ as the polynomially bounded string $c$ by $w$ such that $M(w, c) = ``no"$ and $M$ is the polynomial time verifier of the complement of $L_{2}$ in $NP$.
+We will extend the definition of succinct disqualification for an element $w \in L_{2}$ when $L_{2} \in coNP$ as the polynomially bounded string $c$ by $w$ such that $M(w, c) = 0$ and $M$ is the polynomial time verifier of the complement of $L_{2}$ in $NP$.
 \end{definition}
 
-\subsection{First Hypothesis}
+\subsection{Hypothesis}
 
@@
 A language $L_{1}$ is in $NL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$:
-\[x \in L_{1} \Leftrightarrow \exists \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = ``yes" \]
+\[x \in L_{1} \Leftrightarrow \exists \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = 1 \]
 where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the certificate $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function \cite{AB09}.
@@
 
-From the early days of automata and complexity theory,  two  different  models  of  Turing  machines  are  considered, the offline and online machines \cite{KU15}.
-Each model has a read-only input tape and some work tapes \cite{KU15}.
-The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left \cite{KU15}.
-In the terminology of the (generalized) Turing machine models are called two-way and one-way Turing machines, respectively \cite{KU15}.
-
-Hartmanis and Mahaney have investigated the classes $1L$ and $1NL$ of languages recognizable by deterministic one-way logarithmic space Turing machine and nondeterministic one-way logarithmic space Turing machine, respectively \cite{HM81}.
-They have shown that $1L \neq 1NL$ (by looking at a uniform variant of the string non-equality problem from communication complexity theory) and have defined a natural complete problem for $1NL$ under deterministic one-way logarithmic space reductions \cite{HM81}.
-Furthermore, they have proven that $1NL \subseteq L$ if and only if $L=NL$ \cite{HM81}.
-
 \begin{theorem}
-\label{neg-implication}
-If the Hypothesis \ref{hypothesis1} is true, therefore when $L \neq NL$, then $P = NP$.
+\label{implication}
+When the Hypothesis \ref{hypothesis1} is true, therefore if $L_{2}$ is $\textit{NP--complete}$ under logarithmic space reduction, then $NL = NP$.
 \end{theorem}
@@
 \begin{proof}
-We can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis1} by a nondeterministic logarithmic space Turing machine $N$ such that $N(w) = y$, since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$ \cite{Pap03}.
-Certainly, we can simulate the reading of one symbol from the string $u$ into the read-once tape just nondeterministically generating the same symbol in the work tapes using a logarithmic space \cite{Pap03}.
-
-If we suppose that $L \subset 1NL$, then we can accept the elements of the language $L_{1} \in L$ by a nondeterministic one-way logarithmic space Turing machine $M'$.
-In this way, there is a nondeterministic logarithmic space Turing machine $M''(w) = M'(N(w))$ which will accept when $w \in L_{2}$.
-Consequently, $M''$ is a nondeterministic logarithmic space Turing machine which decides the language $L_{2}$.
-The reason is because we can simulate the output string of $N(w)$ within a read-once tape and thus, we can compute in a nondeterministic logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}.
-Certainly, we do not need to reset the computation of $N(w)$ for the reading at once of a symbol in the output string of $N(w)$ by the nondeterministic one-way logarithmic space Turing machine $M'$.
-Therefore, $L_{2}$ is in $NL$ and thus, $L_{2} \in P$ due to $NL \subseteq P$ \cite{Pap03}.
-If any single $\textit{NP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{CLRS01}.
-Since $L_{2} \in P$ and $L_{2} \in \textit{NP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that $L \subset 1NL$.
-
-Hartmanis and Mahaney have also shown with their result that if $1NL \subseteq L$ or even $1NL \subset L$, then $L=NL$, because they proved there is a complete problem for both $1NL$ and $NL$ at the same time \cite{HM81}.
-In this way, if $L \neq NL$, then $L \subset 1NL$ by contraposition \cite{Pap03}.
-Since we already obtained that $P = NP$ under the assumption that $L \subset 1NL$, therefore if $L \neq NL$, then $P = NP$.
-\end{proof}
-
-\subsection{Second Hypothesis}
-
-An important complexity class is $\textit{coNP--complete}$ \cite{GJ79}. A language $L_{1} \subseteq \{0, 1\}^{*}$ is $\textit{coNP--complete}$ if:
-
-\begin{itemize}
-\item $L_{1} \in coNP$, and
-\item $L' \leq_{p} L_{1}$ for every $L' \in coNP$.
-\end{itemize}
-
-If $L_{1}$ is a language such that $L' \leq_{p} L_{1}$ for some $L' \in \textit{coNP--complete}$, then $L_{1}$ is $\textit{coNP--hard}$ \cite{CLRS01}.
-Moreover, if $L_{1} \in coNP$, then $L_{1} \in \textit{coNP--complete}$ \cite{CLRS01}.
-A principal $\textit{coNP--complete}$ problem is $UNSAT$ \cite{GJ79}.
-A Boolean formula without any satisfying truth assignment is unsatisfiable.
-The problem $UNSAT$ asks whether a given Boolean formula is unsatisfiable \cite{GJ79}.
-
-$coNL$ is the complexity class containing the languages such that their complements belong to $NL$ \cite{Pap03}.
-We can give a disqualification-based definition for $coNL$ \cite{AB09}.
-The disqualification-based definition of $coNL$ assumes that a logarithmic space Turing machine has another separated read-only tape, that is the same kind of special tape called $``$read-once$"$ that we use in the certificate-based definition for $NL$ \cite{AB09}.
-Besides, in the disqualification-based definition of $coNL$, we assume the disqualification string is appropriated for the instance \cite{Pap03}.
-
-\begin{definition}
-A language $L_{1}$ is in $coNL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$:
-\[x \in L_{1} \Leftrightarrow \forall \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ then } M(x, u) = ``yes" \]
-where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the disqualification $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function.
-$M$ is called a logarithmic space disqualifier.
-\end{definition}
-
-For example, there is a well-known $coNL$ problem that states: Given a directed graph $G = (V, E)$ and two nodes $s, t \in V$, is there no possible path from $s$ to $t$?
-In that problem, an appropriated disqualification $u$ is a sequence of nodes contained in $V$ when $s$ is the first node and $t$ is the last one such that this sequence of nodes is not a path: There is at least a consecutive pair of nodes in the sequence where they are not connected by an edge.
-
-We state the following Hypothesis:
-
-\begin{hypothesis}
-\label{hypothesis2}
-Given a nonempty language $L_{1} \in 1NL$, there is a language $L_{2}$ in $\textit{coNP--complete}$ with a deterministic Turing machine $M$, where:
-\[L_{2} = \{w: M(w, u) = y, \forall \textit{ appropriated } u \textit{ such that } y \in L_{1}\}\]
-when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
-In this way, there is a $\textit{coNP--complete}$ language defined by a logarithmic space disqualifier $M$ such that when the input is an element of the language with any of its appropriated disqualification, then $M$ always outputs a string which belongs to a single language in $1NL$.
-\end{hypothesis}
-
-\begin{theorem}
-\label{pos-implication}
-If the Hypothesis \ref{hypothesis2} is true, therefore when $L = NL$, then $P = NP$.
-\end{theorem}
-
-\begin{proof}
-We can accept the elements of the language $L_{1} \in 1NL$ by a nondeterministic one-way logarithmic space Turing machine $M'$.
-In this way, there is a nondeterministic logarithmic space Turing machine $M''(w, u) = M'(M(w, u))$ which will accept when $w \in L_{2}$ for all the appropriated disqualification $u$, where $u$ is placed on the special read-once tape of $M''$.
-The reason is because we can simulate the output string of $M(w, u)$ within a read-once tape and thus, we can compute in a nondeterministic logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}.
-Certainly, we do not need to reset the computation of $M(w, u)$ for the reading at once of a symbol in the output string of $M(w, u)$ by the nondeterministic one-way logarithmic space Turing machine $M'$.
-Consequently, $M''$ can be converted into a logarithmic space disqualifier for the language $L_{2}$ just assuming that $L = NL$, because of the nondeterministic logarithmic space Turing machine $M''$ could be simulated by a deterministic logarithmic space Turing machine.
-Therefore, $L_{2}$ is in $coNL$ and thus, $L_{2} \in P$ due to $coNL \subseteq P$ \cite{Pap03}.
-If any single $\textit{coNP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{Pap03}.
-Since $L_{2} \in P$ and $L_{2} \in \textit{coNP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that $L = NL$.
+Since every problem in $L$ is $\textit{L--complete}$ under logarithmic space reduction, then we can interpret the quantification of the above statement as $``$For any language $L_{1}$ in $L$, there is an $\textit{NP--complete}$ language $L_{2}$ $\ldots$ (rest is the same)$"$.
+However, if we can choose an arbitrary language $L_{1}$ in $L$, then choosing $L_{1}$ the trivial language $\{1\}$ will result in the right hand side of the expression defining $L_{2}$ contained in $NL$.
+Moreover, if that problem in $NL$ is $\textit{NP--complete}$ under logarithmic space reduction, then we obtain that certainly $NL = NP$.
 \end{proof}
@@
 \section{Results}
-
-\subsection{First Hypothesis}
 
@@
 \Comment{Reject the certificate}
-\State \textbf{return} $``no"$
+\State \textbf{return} $0$
 \EndIf
@@
 \Comment{Reject the certificate}
-\State \textbf{return} $``no"$
+\State \textbf{return} $0$
 \Else
@@
 
-\subsection{Second Hypothesis}
-
-We show a previous known $\textit{coNP--complete}$ problem:
-
-\begin{definition}
-$\textbf{3UNSAT}$
-
-INSTANCE: A Boolean formula $\phi$ in $3CNF$.
-
-QUESTION: Is $\phi$ unsatisfiable?
-
-REMARKS: $3UNSAT \in \textit{coNP--complete}$ \cite{GJ79}.
-\end{definition}
-
-We define a new problem:
-
-\begin{definition}
-$\textbf{SUM ZERO}$
-
-INSTANCE: A collection of integers $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we do not take into account the symbol minus in counting the bit-length of the negative integers).
-
-QUESTION: Are there two elements $a, b \in C$, such that $a + b = 0$?
-
-REMARKS: We denote this problem as $\textit{SUM--ZERO}$.
-\end{definition}
-
 \begin{theorem}
-\label{1nl}
-$\textit{SUM--ZERO} \in 1NL$.
+\label{nl}
+$NL = NP$ and thus, $P = NP$.
 \end{theorem}
@@
 \begin{proof}
-Given a collection of integers $C$, we can read its elements from left to right, verify that every element is not equal to $0$, check that every element in $C$ has the same bit-length and count the amount of elements in $C$ to finally multiply it by $3$ and compare its bit-length with the single bit-length from the elements in $C$.
-In addition, we can nondeterministically pick two elements $a$ and $b$ from $C$ and accept in case of $a + b = 0$ otherwise we reject.
-We can make all this computation in a nondeterministic one-way using logarithmic space.
-Certainly, the calculation and store of the bit-length of the elements in $C$ could be done in logarithmic space since this is a unique value.
-On the one hand, we can count and store the number of elements that we read from the input and multiply it by $3$ to finally compare its bit-length with the stored unique bit-length from the elements of the collection, since the cardinality of $C$ multiplied by $3$ could be stored in a binary number of bit-length that is logarithmic in relation to the encoded length of $C$.
-On the other hand, the two elements $a$ and $b$ that we pick from $C$ have a logarithmic space in relation to the encoded length of $C$, because of every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$.
-Indeed, we never need to read to the left on the input for the acceptance of the elements in $\textit{SUM--ZERO}$ in a nondeterministic logarithmic space.
-\end{proof}
-
-\begin{theorem}
-\label{demonstration}
-There is a deterministic Turing machine $M$, where:
-\[3UNSAT = \{w: M(w, u) = y, \forall \textit{ appropriated } u \textit{ such that } y \in \textit{SUM--ZERO}\}\]
-when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
-\end{theorem}
-
-\begin{proof}
-Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we can create a disqualification array $A$ which contains $m$ positive integers between $1$ and $3$ which represents the literals of the clauses in $\phi$ which appear from left to right.
-We read at once the elements of the array $A$ and we reject whether this is not an appropriated disqualification: That is when the array $A$ does not contain exactly $m$ elements, or the array $A$ contains a number that is not between $1$ and $3$.
-While we read the elements of the array $A$, we select from the clauses $\phi$ the literals such that these ones occupy the position that represents the number between $1$ and $3$, that is the first, second or third place within the clause from left to right.
-In this way, we output the selected literals that are represented by a positive or negative (in case of a negated variable) integer just creating another instance $C$ for $\textit{SUM--ZERO}$ where the collection $C$ contains those integers which are the selected literals for each clause in $\phi$.
-Therefore, we obtain that all the appropriated array $A$ would be valid according to the Theorem \ref{demonstration} when:
-\[\phi \in 3UNSAT \Leftrightarrow (\forall \textit{ appropriated array } A \textit{ such that } C \in \textit{SUM--ZERO})\]
-since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value, respectively.
-Furthermore, we can make this disqualification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$.
-Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated disqualification and pick the $m$ literals from the Boolean formula $\phi$ when we write the final integers that represent these literals to the output.
-This logarithmic space disqualification will be the Algorithm \ref{algorithm2}.
-We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$.
-In addition, we reject immediately when the following comparisons:
-\[A[i] < 1 \vee A[i] > 3\]
-hold at least into one single binary digit.
-Note, that every possible literal in $\phi$ could have a representation by an integer between $-3 \times m$ and $3 \times m$ with the exception of $0$, where $m$ is the cardinality of the collection $C$.
-In this way, we guarantee the output collection $C$ is an appropriated instance of $\textit{SUM--ZERO}$ just filling with zeroes to the left the elements with bit-length lesser than $|3 \times m|$ where $|\ldots|$ is the bit-length function.
-
-\begin{algorithm}
-\caption{Logarithmic space disqualifier}\label{algorithm2}
-\begin{algorithmic}[1]
-\Comment{A valid instance for $3UNSAT$ with its disqualification}
-\Procedure{$\textit{DISQUALIFIER}$}{$\phi, A$}
-\Comment{Initialize an index}
-\State $j \gets 0$
-\Comment{$m$ is the number of clauses in $\phi$}
-\Comment{Iterate for the elements of the disqualification array $A$}
-\For{$i$}{$1$}{$m + 1$}
-\If{$i = m+1$}
-\Comment{There exists an $m+1$ element in the array}
-\If{$A[i] \neq \textit{undefined}$}
-\Comment{Reject the disqualification}
-\State \textbf{return} $``no"$
-\EndIf
-\Comment{Break the $\textbf{for}$ loop}
-\State \textbf{break}
-\ElsIf{$A[i] = \textit{undefined} \vee A[i] < 1 \vee A[i] > 3$}
-\Comment{Reject the disqualification}
-\State \textbf{return} $``no"$
-\Else
-\State $j \gets A[i]$
-\EndIf
-\Comment{From the indexed $i^{th}$ clause $c_{i} = (x_{j} \vee y_{k} \vee z_{r})$ in $\phi$}
-\Comment{Where $x$, $y$ and $z$ are literals with local indexes $\{j, k, r\} = \{1,2,3\}$ in $c_{i}$}
-\Comment{Output the integer representation of the $j^{th}$ literal, that is $n(x_{j})$}
-\Comment{Filled with zeroes to the left until a total of $|3 \times m|$ bits including the literal}
-\Comment{But, the bit-length of the symbol minus is ignored in filling the negated literals}
-\State \textbf{output} $``\ , \ n(x_{j})"$
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\end{proof}
-
-\begin{theorem}
-\label{result2}
-The Hypothesis \ref{hypothesis2} is true.
-\end{theorem}
-
-\begin{proof}
-This is a consequence of Theorems \ref{1nl} and \ref{demonstration}.
-\end{proof}
-
-\subsection{Consequences}
-
-\begin{theorem}
-If $L \neq NL$ then $P = NP$.
-\end{theorem}
-
-\begin{proof}
-This is a direct consequence of Theorems \ref{neg-implication} and \ref{result1}.
-\end{proof}
-
-\begin{theorem}
-If $L = NL$ then $P = NP$.
-\end{theorem}
-
-\begin{proof}
-This is a direct consequence of Theorems \ref{pos-implication} and \ref{result2}.
-\end{proof}
-
-\begin{theorem}
-$P = NP$.
-\end{theorem}
-
-\begin{proof}
-Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $P$ is equal to $NP$.
-\end{proof}
-
-\begin{theorem}
-$NL = NP$.
-\end{theorem}
-
-\begin{proof}
-Since the polynomial time reduction in Theorem \ref{completeness} could be easily transformed in a logarithmic space reduction, then the $\textit{NP--complete}$ problem in Theorem \ref{neg-implication}, that would be $MAX\oplus2SAT$, is necessarily in $NL$ and thus all the problems in $NP$ when $L \neq NL$, because of the Cook's Theorem can also be transformed in a logarithmic space reduction \cite{GJ79}.
+The Hypothesis \ref{hypothesis1} is true according to Theorem \ref{proof}.
+Since the polynomial time reduction in Theorem \ref{completeness} could be easily transformed in a logarithmic space reduction, then the $\textit{NP--complete}$ problem in Hypothesis \ref{hypothesis1}, that would be $MAX\oplus2SAT$, is necessarily in $NL$ and thus all the problems in $NP$, because of the Cook's Theorem can also be transformed in a logarithmic space reduction \cite{GJ79}.
 Certainly, every $NP$ problem could be logarithmic space reduced to $SAT$ by the Cook's Theorem algorithm and $SAT$ can be indeed logarithmic space reduced to $\textit{NAE 3SAT}$ \cite{GJ79}.
-For the same reason, the $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$, because of the problem $UNSAT$ can be actually logarithmic space reduced to $3UNSAT$ \cite{GJ79}.
-Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $NL$ is equal to $NP$.
+In addition, as a consequence of Theorem \ref{completeness}, the problem $\textit{NAE 3SAT}$ could be logarithmic space reduced to $MAX\oplus2SAT$.
+In this way, we obtain that $NL = NP$ as result of Theorem \ref{implication}.
+Since $NL \subseteq P$, then $P = NP$ \cite{Pap03}.
 \end{proof}

### 2020-02-25 doc/manuscript.tex
Fixed bug

@@
 \begin{proof}
-Since every problem in $L$ is $\textit{L--complete}$ under logarithmic space reduction, then we can interpret the quantification of the above statement as $``$For any language $L_{1}$ in $L$, there is an $\textit{NP--complete}$ language $L_{2}$ $\ldots$ (rest is the same)$"$.
+Since every problem in $L$ is $\textit{L--complete}$ under logarithmic space reduction, then we can interpret the quantification of the above statement as $``$For any nonempty language $L_{1}$ in $L$, there is an $\textit{NP--complete}$ language $L_{2}$ $\ldots$ (rest is the same)$"$.
 However, if we can choose an arbitrary language $L_{1}$ in $L$, then choosing $L_{1}$ the trivial language $\{1\}$ will result in the right hand side of the expression defining $L_{2}$ contained in $NL$.

### 2020-02-25 doc/manuscript.tex
Removed unused part.

@@
 $NP$ is the complexity class of languages defined by polynomial time verifiers \cite{Pap03}.
-If $NP$ is the class of problems that have succinct certificates, then the complexity class $coNP$ must contain those problems that have succinct disqualifications \cite{Pap03}.
-That is, a rejection instance of a problem in $coNP$ possesses a short proof of its being a rejection instance \cite{Pap03}.
-
-\begin{definition}
-We will extend the definition of succinct disqualification for an element $w \in L_{2}$ when $L_{2} \in coNP$ as the polynomially bounded string $c$ by $w$ such that $M(w, c) = 0$ and $M$ is the polynomial time verifier of the complement of $L_{2}$ in $NP$.
-\end{definition}
 

### 2020-02-25 doc/manuscript.tex
Changed the title
We update the content proof.

@@
 
-%\titlerunning{P vs NP}%optional, please use if title is longer than one line
+\titlerunning{P vs NP}%optional, please use if title is longer than one line
 
@@
 
-\keywords{complexity classes, completeness, polynomial time, reduction, logarithmic space}%TODO mandatory; please add comma-separated list of keywords
+\keywords{complexity classes, completeness, polynomial time, reduction, logarithmic space, one-way}%TODO mandatory; please add comma-separated list of keywords
 
@@
 Whether L = NL is another fundamental question that it is as important as it is unresolved.
-We demonstrate if L is not equal to NL, then P = NP.
-In addition, we show if L is equal to NL, then P = NP.
+We show if L is equal to NL, then P = NP.
+In addition, we demonstrate that L is equal to NL.
 In this way, we prove the complexity class P is equal to NP.
-Furthermore, we demonstrate the complexity class NL is equal to NP.
 \end{abstract}
@@
 For each string $w$ in $\Sigma^{*}$ there is a computation associated with $M$ on input $w$ \cite{AB09}.
-We say that $M$ accepts $w$ if this computation terminates in the accepting state, that is $M(w)=1$ \cite{AB09}.
-Note that $M$ fails to accept $w$ either if this computation ends in the rejecting state, that is $M(w)=0$, or if the computation fails to terminate, or the computation ends in the halting state with some output, that is $M(w)=y$ (when $M$ outputs the string $y$ on the input $w$) \cite{AB09}.
+We say that $M$ accepts $w$ if this computation terminates in the accepting state, that is $M(w)=``yes"$ \cite{AB09}.
+Note that $M$ fails to accept $w$ either if this computation ends in the rejecting state, that is $M(w)=``no"$, or if the computation fails to terminate, or the computation ends in the halting state with some output, that is $M(w)=y$ (when $M$ outputs the string $y$ on the input $w$) \cite{AB09}.
 
@@
 The language accepted by a Turing machine $M$, denoted $L(M)$, has an associated alphabet $\Sigma$ and is defined by:
-\[L(M) = \{w \in \Sigma^{*}: M(w)=1 \}.\]
-Moreover, $L(M)$ is decided by $M$, when $w \notin L(M)$ if and only if $M(w)=0$ \cite{CLRS01}.
+\[L(M) = \{w \in \Sigma^{*}: M(w)=``yes" \}.\]
+Moreover, $L(M)$ is decided by $M$, when $w \notin L(M)$ if and only if $M(w)=``no"$ \cite{CLRS01}.
 We denote by $t_{M}(w)$ the number of steps in the computation of $M$ on input $w$ \cite{AB09}.
@@
 $NP$ is the complexity class of languages defined by polynomial time verifiers \cite{Pap03}.
+If $NP$ is the class of problems that have succinct certificates, then the complexity class $coNP$ must contain those problems that have succinct disqualifications \cite{Pap03}.
+That is, a $``no"$ instance of a problem in $coNP$ possesses a short proof of its being a $``no"$ instance \cite{Pap03}.
+
+\begin{definition}
+We will extend the definition of succinct disqualification for an element $w \in L_{2}$ when $L_{2} \in coNP$ as the polynomially bounded string $c$ by $w$ such that $M(w, c) = ``no"$ and $M$ is the polynomial time verifier of the complement of $L_{2}$ in $NP$.
+\end{definition}
 
@@
 We denote the $XOR$ function as $\oplus$.
-The $\textit{XOR 2SAT}$ problem will be equivalent to $\textit{XOR SAT}$, but the clauses in the formula have exactly two distinct literals.
+The $\textit{XOR 2SAT}$ problem will be equivalent to $\textit{XOR SAT}$, but the clauses in the formula have at most two distinct literals \cite{AR00}.
 $\textit{XOR 2SAT}$ is in $L$ \cite{AR00}, \cite{RM08}.
@@
 A language $L_{1}$ is in $NL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$:
-\[x \in L_{1} \Leftrightarrow \exists \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = 1 \]
+\[x \in L_{1} \Leftrightarrow \exists \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = ``yes" \]
 where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the certificate $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function \cite{AB09}.
@@
 
+An important complexity class is $\textit{coNP--complete}$ \cite{GJ79}. A language $L_{1} \subseteq \{0, 1\}^{*}$ is $\textit{coNP--complete}$ if:
+
+\begin{itemize}
+\item $L_{1} \in coNP$, and
+\item $L' \leq_{p} L_{1}$ for every $L' \in coNP$.
+\end{itemize}
+
+If $L_{1}$ is a language such that $L' \leq_{p} L_{1}$ for some $L' \in \textit{coNP--complete}$, then $L_{1}$ is $\textit{coNP--hard}$ \cite{CLRS01}.
+Moreover, if $L_{1} \in coNP$, then $L_{1} \in \textit{coNP--complete}$ \cite{CLRS01}.
+A principal $\textit{coNP--complete}$ problem is $UNSAT$ \cite{GJ79}.
+A Boolean formula without any satisfying truth assignment is unsatisfiable.
+The problem $UNSAT$ asks whether a given Boolean formula is unsatisfiable \cite{GJ79}.
+
+$coNL$ is the complexity class containing the languages such that their complements belong to $NL$ \cite{Pap03}.
+We can give a disqualification-based definition for $coNL$ \cite{AB09}.
+The disqualification-based definition of $coNL$ assumes that a logarithmic space Turing machine has another separated read-only tape, that is the same kind of special tape called $``$read-once$"$ that we use in the certificate-based definition for $NL$ \cite{AB09}.
+Besides, in the disqualification-based definition of $coNL$, we assume the disqualification string is appropriated for the instance \cite{Pap03}.
+
+\begin{definition}
+A language $L_{1}$ is in $coNL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$:
+\[x \in L_{1} \Leftrightarrow \forall \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ then } M(x, u) = ``yes" \]
+where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the disqualification $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function.
+$M$ is called a logarithmic space disqualifier.
+\end{definition}
+
+For example, there is a well-known $coNL$ problem that states: Given a directed graph $G = (V, E)$ and two nodes $s, t \in V$, is there no possible path from $s$ to $t$?
+In that problem, an appropriated disqualification $u$ is a sequence of nodes contained in $V$ when $s$ is the first node and $t$ is the last one such that this sequence of nodes is not a path: There is at least a consecutive pair of nodes in the sequence where they are not connected by an edge.
+
+From the early days of automata and complexity theory,  two  different  models  of  Turing  machines  are  considered, the offline and online machines \cite{KU15}.
+Each model has a read-only input tape and some work tapes \cite{KU15}.
+The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left \cite{KU15}.
+In the terminology of the (generalized) Turing machine models are called two-way and one-way Turing machines, respectively \cite{KU15}.
+
+Hartmanis and Mahaney have investigated the classes $1L$ and $1NL$ of languages recognizable by deterministic one-way logarithmic space Turing machine and nondeterministic one-way logarithmic space Turing machine, respectively \cite{HM81}.
+They have shown that $1L \neq 1NL$ (by looking at a uniform variant of the string non-equality problem from communication complexity theory) and have defined a natural complete problem for $1NL$ under deterministic one-way logarithmic space reductions \cite{HM81}.
+Furthermore, they have proven that $1NL \subseteq L$ if and only if $L=NL$ \cite{HM81}.
+
 We state the following Hypothesis:
@@
 \begin{hypothesis}
-\label{hypothesis1}
-Given a nonempty language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
-\[L_{2} = \{w: M(w, u) = y, \exists \textit{ appropriated } u \textit{ such that } y \in L_{1}\}\]
+\label{hypothesis2}
+Given a nonempty language $L_{1} \in 1NL$, there is a language $L_{2}$ in $\textit{coNP--complete}$ with a deterministic Turing machine $M$, where:
+\[L_{2} = \{w: M(w, u) = y, \forall \textit{ appropriated } u \textit{ such that } y \in L_{1}\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
-In this way, there is an $\textit{NP--complete}$ language defined by a logarithmic space verifier $M$ such that when the input is an element of the language with its certificate, then $M$ outputs a string which belongs to a single language in $L$.
+In this way, there is a $\textit{coNP--complete}$ language defined by a logarithmic space disqualifier $M$ such that when the input is an element of the language with any of its appropriated disqualification, then $M$ always outputs a string which belongs to a single language in $1NL$.
 \end{hypothesis}
@@
 \begin{theorem}
-\label{implication}
-When the Hypothesis \ref{hypothesis1} is true, therefore if $L_{2}$ is $\textit{NP--complete}$ under logarithmic space reduction, then $NL = NP$.
+\label{pos-implication}
+If the Hypothesis \ref{hypothesis2} is true, therefore when $L = NL$, then $P = NP$.
 \end{theorem}
@@
 \begin{proof}
-Since every problem in $L$ is $\textit{L--complete}$ under logarithmic space reduction, then we can interpret the quantification of the above statement as $``$For any nonempty language $L_{1}$ in $L$, there is an $\textit{NP--complete}$ language $L_{2}$ $\ldots$ (rest is the same)$"$.
-However, if we can choose an arbitrary language $L_{1}$ in $L$, then choosing $L_{1}$ the trivial language $\{1\}$ will result in the right hand side of the expression defining $L_{2}$ contained in $NL$.
-Moreover, if that problem in $NL$ is $\textit{NP--complete}$ under logarithmic space reduction, then we obtain that certainly $NL = NP$.
+We can accept the elements of the language $L_{1} \in 1NL$ by a nondeterministic one-way logarithmic space Turing machine $M'$.
+In this way, there is a nondeterministic logarithmic space Turing machine $M''(w, u) = M'(M(w, u))$ which will accept when $w \in L_{2}$ for all the appropriated disqualification $u$, where $u$ is placed on the special read-once tape of $M''$.
+The reason is because we can simulate the output string of $M(w, u)$ within a read-once tape and thus, we can compute in a nondeterministic logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}.
+Certainly, we do not need to reset the computation of $M(w, u)$ for the reading at once of a symbol in the output string of $M(w, u)$ by the nondeterministic one-way logarithmic space Turing machine $M'$.
+Consequently, $M''$ can be converted into a logarithmic space disqualifier for the language $L_{2}$ just assuming that $L = NL$, because of the nondeterministic logarithmic space Turing machine $M''$ could be simulated by a deterministic logarithmic space Turing machine.
+Therefore, $L_{2}$ is in $coNL$ and thus, $L_{2} \in P$ due to $coNL \subseteq P$ \cite{Pap03}.
+If any single $\textit{coNP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{Pap03}.
+Since $L_{2} \in P$ and $L_{2} \in \textit{coNP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that $L = NL$.
 \end{proof}
@@
 
-We show a previous known $\textit{NP--complete}$ problem:
+\subsection{Hypothesis}
+
+We show a previous known $\textit{coNP--complete}$ problem:
 
 \begin{definition}
-$\textbf{NAE 3SAT}$
+$\textbf{3UNSAT}$
 
@@
 
-QUESTION: Is there a truth assignment for $\phi$ such that each clause has at least one true literal and at least one false literal?
+QUESTION: Is $\phi$ unsatisfiable?
 
-REMARKS: $\textit{NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}.
+REMARKS: $3UNSAT \in \textit{coNP--complete}$ \cite{GJ79}.
 \end{definition}
@@
 \begin{definition}
-$\textbf{MAXIMUM EXCLUSIVE-OR 2SAT}$
+$\textbf{SUM ZERO}$
 
-INSTANCE: A positive integer $K$ and a Boolean formula $\phi$ that is an instance of $\textit{XOR 2SAT}$.
+INSTANCE: A collection of integers $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we do not take into account the symbol minus in counting the bit-length of the negative integers).
 
-QUESTION: Is there a truth assignment in $\phi$ such that at most $K$ clauses are unsatisfied?
+QUESTION: Are there two elements $a, b \in C$, such that $a + b = 0$?
 
-REMARKS: We denote this problem as $MAX\oplus2SAT$.
+REMARKS: We denote this problem as $\textit{SUM--ZERO}$.
 \end{definition}
@@
 \begin{theorem}
-\label{completeness}
-$MAX\oplus2SAT \in \textit{NP--complete}$.
+\label{1nl}
+$\textit{SUM--ZERO} \in 1NL$.
 \end{theorem}
@@
 \begin{proof}
-It is trivial to see $MAX\oplus2SAT \in NP$ \cite{Pap03}.
-Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we create three new variables $a_{c_{i}}$, $b_{c_{i}}$ and $d_{c_{i}}$ for each clause $c_{i} = (x \vee y \vee z)$ in $\phi$, where $x$, $y$ and $z$ are literals, in the following formula:
-\[P_{i} = (a_{c_{i}} \oplus b_{c_{i}}) \wedge (b_{c_{i}} \oplus d_{c_{i}}) \wedge (a_{c_{i}} \oplus d_{c_{i}}) \wedge (x \oplus a_{c_{i}}) \wedge (y \oplus b_{c_{i}}) \wedge (z \oplus d_{c_{i}}).\]
-We can see $P_{i}$ has at most one unsatisfied clause for some truth assignment if and only if at least one member of $\{x,y,z\}$ is true and at least one member of $\{x,y,z\}$ is false for the same truth assignment.
-Hence, we can create the Boolean formula $\psi$ as the conjunction of the $P_{i}$ formulas for every clause $c_{i}$ in $\phi$, such that $\psi = P_{1} \wedge \ldots \wedge P_{m}$.
-Finally, we obtain that:
-\[\phi \in \textit{NAE 3SAT} \textit{ if and only if } (\psi, m) \in MAX\oplus2SAT.\]
-Consequently, we prove $\textit{NAE 3SAT} \leq_{p} MAX\oplus2SAT$ where we already know the language $\textit{NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}.
-To sum up, we show $MAX\oplus2SAT \in \textit{NP--hard}$ and $MAX\oplus2SAT \in NP$ and thus, $MAX\oplus2SAT \in \textit{NP--complete}$.
+Given a collection of integers $C$, we can read its elements from left to right, verify that every element is not equal to $0$, check that every element in $C$ has the same bit-length and count the amount of elements in $C$ to finally multiply it by $3$ and compare its bit-length with the single bit-length from the elements in $C$.
+In addition, we can nondeterministically pick two elements $a$ and $b$ from $C$ and accept in case of $a + b = 0$ otherwise we reject.
+We can make all this computation in a nondeterministic one-way using logarithmic space.
+Certainly, the calculation and store of the bit-length of the elements in $C$ could be done in logarithmic space since this is a unique value.
+On the one hand, we can count and store the number of elements that we read from the input and multiply it by $3$ to finally compare its bit-length with the stored unique bit-length from the elements of the collection, since the cardinality of $C$ multiplied by $3$ could be stored in a binary number of bit-length that is logarithmic in relation to the encoded length of $C$.
+On the other hand, the two elements $a$ and $b$ that we pick from $C$ have a logarithmic space in relation to the encoded length of $C$, because of every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$.
+Indeed, we never need to read to the left on the input for the acceptance of the elements in $\textit{SUM--ZERO}$ in a nondeterministic logarithmic space.
 \end{proof}
@@
 \begin{theorem}
-\label{proof}
+\label{demonstration}
 There is a deterministic Turing machine $M$, where:
-\[MAX\oplus2SAT = \{w: M(w, u) = y, \exists \textit{ appropriated } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
+\[3UNSAT = \{w: M(w, u) = y, \forall \textit{ appropriated } u \textit{ such that } y \in \textit{SUM--ZERO}\}\]
 when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
@@
 \begin{proof}
-Given a valid instance $(\psi, K)$ for $MAX\oplus2SAT$ when $\psi$ has $m$ clauses, we can create a certificate array $A$ which contains $K$ different natural numbers in ascending order which represents the indexes of the clauses in $\psi$ that we are going to remove from the instance.
-We read at once the elements of the array $A$ and we reject whether this is not an appropriated certificate: That is when the numbers are not sorted in ascending order, or the array $A$ does not contain exactly $K$ elements, or the array $A$ contains a number that is not between $1$ and $m$.
-While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MAX\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$.
-Therefore, we obtain the array $A$ would be valid according to the Theorem \ref{proof} when:
-\[(\psi, K) \in MAX\oplus2SAT \Leftrightarrow (\exists \textit{ appropriated array } A \textit{ such that } \phi \in \textit{XOR 2SAT}).\]
-Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right.
-Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated certificate and also remove the $K$ different clauses from the Boolean formula $\psi$ when we write the final clauses to the output.
-This logarithmic space verification will be the Algorithm \ref{algorithm1}.
+Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we can create a disqualification array $A$ which contains $m$ positive integers between $1$ and $3$ which represents the literals of the clauses in $\phi$ which appear from left to right.
+We read at once the elements of the array $A$ and we reject whether this is not an appropriated disqualification: That is when the array $A$ does not contain exactly $m$ elements, or the array $A$ contains a number that is not between $1$ and $3$.
+While we read the elements of the array $A$, we select from the clauses $\phi$ the literals such that these ones occupy the position that represents the number between $1$ and $3$, that is the first, second or third place within the clause from left to right.
+In this way, we output the selected literals that are represented by a positive or negative (in case of a negated variable) integer just creating another instance $C$ for $\textit{SUM--ZERO}$ where the collection $C$ contains those integers which are the selected literals for each clause in $\phi$.
+Therefore, we obtain that all the appropriated array $A$ would be valid according to the Theorem \ref{demonstration} when:
+\[\phi \in 3UNSAT \Leftrightarrow (\forall \textit{ appropriated array } A \textit{ such that } C \in \textit{SUM--ZERO})\]
+since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value, respectively.
+Furthermore, we can make this disqualification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$.
+Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated disqualification and pick the $m$ literals from the Boolean formula $\phi$ when we write the final integers that represent these literals to the output.
+This logarithmic space disqualification will be the Algorithm \ref{algorithm2}.
 We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$.
 In addition, we reject immediately when the following comparisons:
-\[A[i] \leq max \vee A[i] < 1 \vee A[i] > m\]
-hold at least into one single binary digit. Note, in the loop $j$ from $min$ to $max - 1$, we do not output any clause when $max - 1 < min$.
+\[A[i] < 1 \vee A[i] > 3\]
+hold at least into one single binary digit.
+Note, that every possible literal in $\phi$ could have a representation by an integer between $-3 \times m$ and $3 \times m$ with the exception of $0$, where $m$ is the cardinality of the collection $C$.
+In this way, we guarantee the output collection $C$ is an appropriated instance of $\textit{SUM--ZERO}$ just filling with zeroes to the left the elements with bit-length lesser than $|3 \times m|$ where $|\ldots|$ is the bit-length function.
 
 \begin{algorithm}
-\caption{Logarithmic space verifier}\label{algorithm1}
+\caption{Logarithmic space disqualifier}\label{algorithm2}
 \begin{algorithmic}[1]
-\Comment{A valid instance for $MAX\oplus2SAT$ with its certificate}
-\Procedure{$\textit{VERIFIER}$}{$(\psi, K), A$}
-\Comment{Initialize minimum and maximum values}
-\State $min \gets 1$
-\State $max \gets 0$
-\Comment{Iterate for the elements of the certificate array $A$}
-\For{$i$}{$1$}{$K + 1$}
-\If{$i = K+1$}
-\Comment{There exists a $K+1$ element in the array}
+\Comment{A valid instance for $3UNSAT$ with its disqualification}
+\Procedure{$\textit{DISQUALIFIER}$}{$\phi, A$}
+\Comment{Initialize an index}
+\State $j \gets 0$
+\Comment{$m$ is the number of clauses in $\phi$}
+\Comment{Iterate for the elements of the disqualification array $A$}
+\For{$i$}{$1$}{$m + 1$}
+\If{$i = m+1$}
+\Comment{There exists an $m+1$ element in the array}
 \If{$A[i] \neq \textit{undefined}$}
-\Comment{Reject the certificate}
-\State \textbf{return} $0$
+\Comment{Reject the disqualification}
+\State \textbf{return} $``no"$
 \EndIf
-\Comment{$m$ is the number of clauses in $\psi$}
-\State $max \gets m + 1$
-\ElsIf{$A[i] = \textit{undefined} \vee A[i] \leq max \vee A[i] < 1 \vee A[i] > m$}
-\Comment{Reject the certificate}
-\State \textbf{return} $0$
+\Comment{Break the $\textbf{for}$ loop}
+\State \textbf{break}
+\ElsIf{$A[i] = \textit{undefined} \vee A[i] < 1 \vee A[i] > 3$}
+\Comment{Reject the disqualification}
+\State \textbf{return} $``no"$
 \Else
-\State $max \gets A[i]$
+\State $j \gets A[i]$
 \EndIf
-\Comment{Iterate for the clauses of the Boolean formula $\psi$}
-\For{$j$}{$min$}{$max - 1$}
-\Comment{Output the indexed $j^{th}$ clause in $\psi$}
-\State \textbf{output} $``\wedge c_{j}"$
-\EndFor
-\State $min \gets max + 1$
+\Comment{From the indexed $i^{th}$ clause $c_{i} = (x_{j} \vee y_{k} \vee z_{r})$ in $\phi$}
+\Comment{Where $x$, $y$ and $z$ are literals with local indexes $\{j, k, r\} = \{1,2,3\}$ in $c_{i}$}
+\Comment{Output the integer representation of the $j^{th}$ literal, that is $n(x_{j})$}
+\Comment{Filled with zeroes to the left until a total of $|3 \times m|$ bits including the literal}
+\Comment{But, the bit-length of the symbol minus is ignored in filling the negated literals}
+\State \textbf{output} $``\ , \ n(x_{j})"$
 \EndFor
@@
 \begin{theorem}
-\label{result1}
-The Hypothesis \ref{hypothesis1} is true.
+\label{result2}
+The Hypothesis \ref{hypothesis2} is true.
 \end{theorem}
@@
 \begin{proof}
-This is a consequence of Theorems \ref{completeness} and \ref{proof}.
+This is a consequence of Theorems \ref{1nl} and \ref{demonstration}.
 \end{proof}
@@
 \begin{theorem}
-\label{nl}
-$NL = NP$ and thus, $P = NP$.
+\label{equal-NP}
+If $L = NL$ then $P = NP$.
 \end{theorem}
@@
 \begin{proof}
-The Hypothesis \ref{hypothesis1} is true according to Theorem \ref{proof}.
-Since the polynomial time reduction in Theorem \ref{completeness} could be easily transformed in a logarithmic space reduction, then the $\textit{NP--complete}$ problem in Hypothesis \ref{hypothesis1}, that would be $MAX\oplus2SAT$, is necessarily in $NL$ and thus all the problems in $NP$, because of the Cook's Theorem can also be transformed in a logarithmic space reduction \cite{GJ79}.
-Certainly, every $NP$ problem could be logarithmic space reduced to $SAT$ by the Cook's Theorem algorithm and $SAT$ can be indeed logarithmic space reduced to $\textit{NAE 3SAT}$ \cite{GJ79}.
-In addition, as a consequence of Theorem \ref{completeness}, the problem $\textit{NAE 3SAT}$ could be logarithmic space reduced to $MAX\oplus2SAT$.
-In this way, we obtain that $NL = NP$ as result of Theorem \ref{implication}.
-Since $NL \subseteq P$, then $P = NP$ \cite{Pap03}.
+This is a direct consequence of Theorems \ref{pos-implication} and \ref{result2}.
+\end{proof}
+
+\subsection{L versus NL}
+
+A directed acyclic graph $G = (V, E)$ is topologically sorted when for any pair of edges $(a, b)$ and $(b, c)$ in $G$, then the edge $(a, b)$ is listed before $(b, c)$ \cite{HM81}.
+
+We show a previous known $\textit{NL--complete}$ problem:
+
+\begin{definition}
+$\textbf{TAGAP}$
+
+INSTANCE: Given a directed acyclic graph $G = (V, E)$ that is topologically sorted and two nodes $s, t \in V$.
+
+QUESTION: Is there a path from $s$ to $t$?
+
+REMARKS: $TAGAP \in \textit{NL--complete}$ \cite{HM81}.
+\end{definition}
+
+\begin{definition}
+An instance $\phi$ of $\textit{XOR 2SAT}$ is topologically sorted when for any pair of clauses $(a, b)$ and $(b, c)$ in $\phi$, then the clause $(a, b)$ is listed before $(b, c)$.
+\end{definition}
+
+\begin{definition}
+$\textbf{TAGAP 2SAT}$
+
+INSTANCE: Given an instance $\phi$ of $\textit{XOR 2SAT}$ that is topologically sorted.
+
+QUESTION: Is there a truth assignment, such that each clause of one literal is satisfied and each clause of two literals has not a true and false evaluated literals at the same time?
+\end{definition}
+
+\begin{theorem}
+$\textit{TAGAP 2SAT} \in L$.
+\end{theorem}
+
+\begin{proof}
+We can check whether an instance $\phi$ of $\textit{XOR 2SAT}$ is topologically sorted in logarithmic space.
+Certainly, for each clause $(a, b)$ we can verify in logarithmic space whether there is not another clause $(b, c)$ that is listed before of $(a, b)$.
+In addition, given an instance $\phi$ of $\textit{XOR 2SAT}$ with $m$ clauses, for each clause of two literals $c_{i} = (x \oplus y)$ in the input tape, we create a new clause $d_{i} = (x \oplus \rightharpoondown y)$ into the output tape, where $x$ and $y$ are literals.
+Moreover, for each clause of one literal $c_{i} = (x)$ in the input tape, we create the same clause $d_{i} = (x)$ into the output tape, where $x$ is a literal.
+Hence, we can create a new instance $\psi$ of $\textit{XOR 2SAT}$ as the conjunction of the $d_{i}$ clauses for every clause $c_{i}$ in $\phi$, such that $\psi = d_{1} \wedge \ldots \wedge d_{m}$.
+Finally, we obtain that:
+\[\phi \in \textit{TAGAP 2SAT} \textit{ if and only if } \psi \in \textit{XOR 2SAT}.\]
+Consequently, we prove $\textit{TAGAP 2SAT} \leq_{l} \textit{XOR 2SAT}$ where we already know the language $\textit{XOR 2SAT} \in L$ \cite{AR00}, \cite{RM08}.
+Since $L$ is closed under logarithmic space reductions, then we obtain that $\textit{TAGAP 2SAT} \in L$ \cite{Pap03}.
+\end{proof}
+
+\begin{lemma}
+\label{nl-complete}
+We have the complement of $TAGAP$ complies with $coTAGAP \in \textit{NL--complete}$.
+\end{lemma}
+
+\begin{proof}
+This is trivially true since $NL$ is closed under complement \cite{Pap03}.
+\end{proof}
+
+\begin{theorem}
+\label{reduction}
+$coTAGAP \leq_{l} \textit{TAGAP 2SAT}$.
+\end{theorem}
+
+\begin{proof}
+Given a directed acyclic graph $G = (V, E)$ that is topologically sorted and two nodes $s, t \in V$, for each edge $(x, y)$ in the input tape from left to right, we create a new clause $(x \oplus y)$ for an instance $\phi$ of $\textit{XOR 2SAT}$ into the output tape, where $x$ and $y$ are positive literals represented by the positive integers $x$ and $y$ which are two nodes in $G$.
+In addition, before we generate the first clause from the edges, then we create the clause $(\rightharpoondown s)$ into the output tape, and after we generate all the clauses, then we create the clause $(t)$ into the output tape from the IN and OUT nodes of the possible path $s, t \in V$: This is possible because an instance of $\textit{XOR 2SAT}$ have clauses of at most two literals \cite{AR00}.
+We can see the final instance $\phi$ of $\textit{XOR 2SAT}$ into the output tape will be topologically sorted, since we create the clauses through the edges from left to right with the exception of $(\rightharpoondown s)$ that is the first clause and $(t)$ that is the last one in $\phi$.
+Hence, if $\phi$ is an acceptance instance of $\textit{TAGAP 2SAT}$, then there is no a possible path from $s$ to $t$ in $G$, because it is necessary that $s$ and $t$ must be false and true on the clauses $(\rightharpoondown s)$ and $(t)$, respectively.
+Certainly, if there is path from $s$ to $t$, then $s$ and $t$ should be both true or both false in order the instance $\phi$ of $\textit{TAGAP 2SAT}$ could be possible accepted.
+Finally, we obtain that:
+\[G \in coTAGAP \textit{ if and only if } \phi \in \textit{TAGAP 2SAT}.\]
+Consequently, we prove $coTAGAP \leq_{l} \textit{TAGAP 2SAT}$ \cite{Pap03}.
+\end{proof}
+
+\begin{theorem}
+\label{equal-L}
+$L = NL$.
+\end{theorem}
+
+\begin{proof}
+A single language in $\textit{NL--complete}$ that is logarithmic space reduced to another language $L$, it is sufficiently to prove $L = NL$, since $L$ and $NL$ are closed under logarithmic space reduction \cite{Pap03}.
+Therefore, this is direct result from Lemma \ref{nl-complete} and Theorem \ref{reduction}.
+\end{proof}
+
+\begin{theorem}
+$P = NP$.
+\end{theorem}
+
+\begin{proof}
+This is a direct consequence of Theorems \ref{equal-NP} and \ref{equal-L}. 
 \end{proof}

### 2020-02-26 doc/manuscript.tex
Fixed bug

@@
 In this way, we prove the complexity class P is equal to NP.
+Furthermore, we demonstrate the complexity class L is equal to NP.
 \end{abstract}
@@
 
-A directed acyclic graph $G = (V, E)$ is topologically sorted when for any pair of edges $(a, b)$ and $(b, c)$ in $G$, then the edge $(a, b)$ is listed before $(b, c)$ \cite{HM81}.
+A directed graph $G = (V, E)$ is topologically sorted when for any pair of edges $(a, b)$ and $(b, c)$ in $G$, then the edge $(a, b)$ is listed before $(b, c)$ \cite{HM81}.
 
@@
 
-INSTANCE: Given a directed acyclic graph $G = (V, E)$ that is topologically sorted and two nodes $s, t \in V$.
+INSTANCE: Given a directed graph $G = (V, E)$ that is topologically sorted and two nodes $s, t \in V$.
 
@@
 
-REMARKS: $TAGAP \in \textit{NL--complete}$ \cite{HM81}.
+REMARKS: $TAGAP \in \textit{NL--complete}$ \cite{HM81}. Certainly, this problem remains in $\textit{NL--complete}$ even if the graph is not acyclic \cite{HM81}. 
 \end{definition}
@@
 \begin{proof}
-Given a directed acyclic graph $G = (V, E)$ that is topologically sorted and two nodes $s, t \in V$, for each edge $(x, y)$ in the input tape from left to right, we create a new clause $(x \oplus y)$ for an instance $\phi$ of $\textit{XOR 2SAT}$ into the output tape, where $x$ and $y$ are positive literals represented by the positive integers $x$ and $y$ which are two nodes in $G$.
+Given a directed graph $G = (V, E)$ that is topologically sorted and two nodes $s, t \in V$, for each edge $(x, y)$ in the input tape from left to right, we create a new clause $(x \oplus y)$ for an instance $\phi$ of $\textit{XOR 2SAT}$ into the output tape, where $x$ and $y$ are positive literals represented by the positive integers $x$ and $y$ which are two nodes in $G$.
 In addition, before we generate the first clause from the edges, then we create the clause $(\rightharpoondown s)$ into the output tape, and after we generate all the clauses, then we create the clause $(t)$ into the output tape from the IN and OUT nodes of the possible path $s, t \in V$: This is possible because an instance of $\textit{XOR 2SAT}$ have clauses of at most two literals \cite{AR00}.
@@
 This is a direct consequence of Theorems \ref{equal-NP} and \ref{equal-L}.
+\end{proof}
+
+\begin{theorem}
+$L = NP$.
+\end{theorem}
+
+\begin{proof}
+The $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$, because of every problem in $coNP$ can be actually logarithmic space reduced to $3UNSAT$ \cite{GJ79}.
+Certainly, every $coNP$ problem could be logarithmic space reduced to $UNSAT$ by the Cook's Theorem algorithm and $UNSAT$ can be indeed logarithmic space reduced to $3UNSAT$ \cite{GJ79}.
+Since we have that $L = NL = coNL$ is true, then the complexity class $L$ is equal to $NP$.
 \end{proof}

### 2020-02-26 doc/manuscript.tex
Fixed clause style

@@
 \begin{definition}
-An instance $\phi$ of $\textit{XOR 2SAT}$ is topologically sorted when for any pair of clauses $(a, b)$ and $(b, c)$ in $\phi$, then the clause $(a, b)$ is listed before $(b, c)$.
+An instance $\phi$ of $\textit{XOR 2SAT}$ is topologically sorted when for any pair of clauses $(a \oplus b)$ and $(b \oplus c)$ in $\phi$, then the clause $(a \oplus b)$ is listed before $(b \oplus c)$.
 \end{definition}
@@
 We can check whether an instance $\phi$ of $\textit{XOR 2SAT}$ is topologically sorted in logarithmic space.
-Certainly, for each clause $(a, b)$ we can verify in logarithmic space whether there is not another clause $(b, c)$ that is listed before of $(a, b)$.
+Certainly, for each clause $(a \oplus b)$ we can verify in logarithmic space whether there is not another clause $(b \oplus c)$ that is listed before of $(a \oplus b)$.
 In addition, given an instance $\phi$ of $\textit{XOR 2SAT}$ with $m$ clauses, for each clause of two literals $c_{i} = (x \oplus y)$ in the input tape, we create a new clause $d_{i} = (x \oplus \rightharpoondown y)$ into the output tape, where $x$ and $y$ are literals.

### 2020-02-29 doc/manuscript.tex
Finished the proof....

--- 2020-02-25 doc/manuscript.tex
@@
 
-\titlerunning{P vs NP}%optional, please use if title is longer than one line
+%\titlerunning{P vs NP}%optional, please use if title is longer than one line
 
@@
 Whether L = NL is another fundamental question that it is as important as it is unresolved.
-We show if L is equal to NL, then P = NP.
-In addition, we demonstrate that L is equal to NL.
+We demonstrate if L is not equal to NL, then P = NP.
+In addition, we show if L is equal to NL, then P = NP.
 In this way, we prove the complexity class P is equal to NP.
+Furthermore, we demonstrate the complexity class L is equal to NP.
 \end{abstract}
@@
 Dwork and Stockmeyer and Condon have studied interactive proofs where the verifier is a space bounded computation instead of the original model where the verifier is a time bounded computation \cite{LIP90}.
-In addition, Blum and Kannan has studied another model where the goal is to check a computation based solely on the final answer \cite{LIP90}.
+In addition, Blum and Kannan have studied another model where the goal is to check a computation based solely on the final answer \cite{LIP90}.
 More about probabilistic logarithmic space verifiers and the complexity class $NP$ has been investigated on a technique of Lipton \cite{LIP90}.
@@
 We denote the $XOR$ function as $\oplus$.
-The $\textit{XOR 2SAT}$ problem will be equivalent to $\textit{XOR SAT}$, but the clauses in the formula have at most two distinct literals \cite{AR00}.
+The $\textit{XOR 2SAT}$ problem will be equivalent to $\textit{XOR SAT}$, but the clauses in the formula have exactly two distinct literals.
 $\textit{XOR 2SAT}$ is in $L$ \cite{AR00}, \cite{RM08}.
@@
 \end{definition}
+
+We state the following Hypothesis:
+
+\begin{hypothesis}
+\label{hypothesis1}
+Given a nonempty language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
+\[L_{2} = \{w: M(w, u) = y, \exists \textit{ appropriated } u \textit{ such that } y \in L_{1}\}\]
+when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
+In this way, there is an $\textit{NP--complete}$ language defined by a logarithmic space verifier $M$ such that when the input is an element of the language with its certificate, then $M$ outputs a string which belongs to a single language in $L$.
+\end{hypothesis}
+
+From the early days of automata and complexity theory,  two  different  models  of  Turing  machines  are  considered, the offline and online machines \cite{KU15}.
+Each model has a read-only input tape and some work tapes \cite{KU15}.
+The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left \cite{KU15}.
+In the terminology of the (generalized) Turing machine models are called two-way and one-way Turing machines, respectively \cite{KU15}.
+
+Hartmanis and Mahaney have investigated the classes $1L$ and $1NL$ of languages recognizable by deterministic one-way logarithmic space Turing machine and nondeterministic one-way logarithmic space Turing machine, respectively \cite{HM81}.
+They have shown that $1L \neq 1NL$ (by looking at a uniform variant of the string non-equality problem from communication complexity theory) and have defined a natural complete problem for $1NL$ under deterministic one-way logarithmic space reductions \cite{HM81}.
+Furthermore, they have proven that $1NL \subseteq L$ if and only if $L=NL$ \cite{HM81}.
+
+\begin{theorem}
+\label{neg-implication}
+If the Hypothesis \ref{hypothesis1} is true, therefore when $L \neq NL$, then $P = NP$.
+\end{theorem}
+
+\begin{proof}
+We can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis1} by a nondeterministic logarithmic space Turing machine $N$ such that $N(w) = y$, since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$ \cite{Pap03}.
+Certainly, we can simulate the reading of one symbol from the string $u$ into the read-once tape just nondeterministically generating the same symbol in the work tapes using a logarithmic space \cite{Pap03}.
+
+If we suppose that $L \subset 1NL$, then we can accept the elements of the language $L_{1} \in L$ by a nondeterministic one-way logarithmic space Turing machine $M'$.
+In this way, there is a nondeterministic logarithmic space Turing machine $M''(w) = M'(N(w))$ which will accept when $w \in L_{2}$.
+Consequently, $M''$ is a nondeterministic logarithmic space Turing machine which decides the language $L_{2}$.
+The reason is because we can simulate the output string of $N(w)$ within a read-once tape and thus, we can compute in a nondeterministic logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}.
+Certainly, we do not need to reset the computation of $N(w)$ for the reading at once of a symbol in the output string of $N(w)$ by the nondeterministic one-way logarithmic space Turing machine $M'$.
+Therefore, $L_{2}$ is in $NL$ and thus, $L_{2} \in P$ due to $NL \subseteq P$ \cite{Pap03}.
+If any single $\textit{NP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{CLRS01}.
+Since $L_{2} \in P$ and $L_{2} \in \textit{NP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that $L \subset 1NL$.
+
+Hartmanis and Mahaney have also shown with their result that if $1NL \subseteq L$ or even $1NL \subset L$, then $L=NL$, because they proved there is a complete problem for both $1NL$ and $NL$ at the same time \cite{HM81}.
+In this way, if $L \neq NL$, then $L \subset 1NL$ by contraposition \cite{Pap03}.
+Since we already obtained that $P = NP$ under the assumption that $L \subset 1NL$, therefore if $L \neq NL$, then $P = NP$.
+\end{proof}
+
+\subsection{Second Hypothesis}
 
@@
 
-From the early days of automata and complexity theory,  two  different  models  of  Turing  machines  are  considered, the offline and online machines \cite{KU15}.
-Each model has a read-only input tape and some work tapes \cite{KU15}.
-The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left \cite{KU15}.
-In the terminology of the (generalized) Turing machine models are called two-way and one-way Turing machines, respectively \cite{KU15}.
-
-Hartmanis and Mahaney have investigated the classes $1L$ and $1NL$ of languages recognizable by deterministic one-way logarithmic space Turing machine and nondeterministic one-way logarithmic space Turing machine, respectively \cite{HM81}.
-They have shown that $1L \neq 1NL$ (by looking at a uniform variant of the string non-equality problem from communication complexity theory) and have defined a natural complete problem for $1NL$ under deterministic one-way logarithmic space reductions \cite{HM81}.
-Furthermore, they have proven that $1NL \subseteq L$ if and only if $L=NL$ \cite{HM81}.
-
 We state the following Hypothesis:
@@
 
-\subsection{Hypothesis}
+\subsection{First Hypothesis}
+
+We show a previous known $\textit{NP--complete}$ problem:
+
+\begin{definition}
+$\textbf{NAE 3SAT}$
+
+INSTANCE: A Boolean formula $\phi$ in $3CNF$.
+
+QUESTION: Is there a truth assignment for $\phi$ such that each clause has at least one true literal and at least one false literal?
+
+REMARKS: $\textit{NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}.
+\end{definition}
+
+We define a new problem:
+
+\begin{definition}
+$\textbf{MAXIMUM EXCLUSIVE-OR 2SAT}$
+
+INSTANCE: A positive integer $K$ and a Boolean formula $\phi$ that is an instance of $\textit{XOR 2SAT}$.
+
+QUESTION: Is there a truth assignment in $\phi$ such that at most $K$ clauses are unsatisfied?
+
+REMARKS: We denote this problem as $MAX\oplus2SAT$.
+\end{definition}
+
+\begin{theorem}
+\label{completeness}
+$MAX\oplus2SAT \in \textit{NP--complete}$.
+\end{theorem}
+
+\begin{proof}
+It is trivial to see $MAX\oplus2SAT \in NP$ \cite{Pap03}.
+Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we create three new variables $a_{c_{i}}$, $b_{c_{i}}$ and $d_{c_{i}}$ for each clause $c_{i} = (x \vee y \vee z)$ in $\phi$, where $x$, $y$ and $z$ are literals, in the following formula:
+\[P_{i} = (a_{c_{i}} \oplus b_{c_{i}}) \wedge (b_{c_{i}} \oplus d_{c_{i}}) \wedge (a_{c_{i}} \oplus d_{c_{i}}) \wedge (x \oplus a_{c_{i}}) \wedge (y \oplus b_{c_{i}}) \wedge (z \oplus d_{c_{i}}).\]
+We can see $P_{i}$ has at most one unsatisfied clause for some truth assignment if and only if at least one member of $\{x,y,z\}$ is true and at least one member of $\{x,y,z\}$ is false for the same truth assignment.
+Hence, we can create the Boolean formula $\psi$ as the conjunction of the $P_{i}$ formulas for every clause $c_{i}$ in $\phi$, such that $\psi = P_{1} \wedge \ldots \wedge P_{m}$.
+Finally, we obtain that:
+\[\phi \in \textit{NAE 3SAT} \textit{ if and only if } (\psi, m) \in MAX\oplus2SAT.\]
+Consequently, we prove $\textit{NAE 3SAT} \leq_{p} MAX\oplus2SAT$ where we already know the language $\textit{NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}.
+To sum up, we show $MAX\oplus2SAT \in \textit{NP--hard}$ and $MAX\oplus2SAT \in NP$ and thus, $MAX\oplus2SAT \in \textit{NP--complete}$.
+\end{proof}
+
+\begin{theorem}
+\label{proof}
+There is a deterministic Turing machine $M$, where:
+\[MAX\oplus2SAT = \{w: M(w, u) = y, \exists \textit{ appropriated } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
+when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
+\end{theorem}
+
+\begin{proof}
+Given a valid instance $(\psi, K)$ for $MAX\oplus2SAT$ when $\psi$ has $m$ clauses, we can create a certificate array $A$ which contains $K$ different natural numbers in ascending order which represents the indexes of the clauses in $\psi$ that we are going to remove from the instance.
+We read at once the elements of the array $A$ and we reject whether this is not an appropriated certificate: That is when the numbers are not sorted in ascending order, or the array $A$ does not contain exactly $K$ elements, or the array $A$ contains a number that is not between $1$ and $m$.
+While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MAX\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$.
+Therefore, we obtain the array $A$ would be valid according to the Theorem \ref{proof} when:
+\[(\psi, K) \in MAX\oplus2SAT \Leftrightarrow (\exists \textit{ appropriated array } A \textit{ such that } \phi \in \textit{XOR 2SAT}).\]
+Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right.
+Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated certificate and also remove the $K$ different clauses from the Boolean formula $\psi$ when we write the final clauses to the output.
+This logarithmic space verification will be the Algorithm \ref{algorithm1}.
+We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$.
+In addition, we reject immediately when the following comparisons:
+\[A[i] \leq max \vee A[i] < 1 \vee A[i] > m\]
+hold at least into one single binary digit. Note, in the loop $j$ from $min$ to $max - 1$, we do not output any clause when $max - 1 < min$.
+
+\begin{algorithm}
+\caption{Logarithmic space verifier}\label{algorithm1}
+\begin{algorithmic}[1]
+\Comment{A valid instance for $MAX\oplus2SAT$ with its certificate}
+\Procedure{$\textit{VERIFIER}$}{$(\psi, K), A$}
+\Comment{Initialize minimum and maximum values}
+\State $min \gets 1$
+\State $max \gets 0$
+\Comment{Iterate for the elements of the certificate array $A$}
+\For{$i$}{$1$}{$K + 1$}
+\If{$i = K+1$}
+\Comment{There exists a $K+1$ element in the array}
+\If{$A[i] \neq \textit{undefined}$}
+\Comment{Reject the certificate}
+\State \textbf{return} $``no"$
+\EndIf
+\Comment{$m$ is the number of clauses in $\psi$}
+\State $max \gets m + 1$
+\ElsIf{$A[i] = \textit{undefined} \vee A[i] \leq max \vee A[i] < 1 \vee A[i] > m$}
+\Comment{Reject the certificate}
+\State \textbf{return} $``no"$
+\Else
+\State $max \gets A[i]$
+\EndIf
+\Comment{Iterate for the clauses of the Boolean formula $\psi$}
+\For{$j$}{$min$}{$max - 1$}
+\Comment{Output the indexed $j^{th}$ clause in $\psi$}
+\State \textbf{output} $``\wedge c_{j}"$
+\EndFor
+\State $min \gets max + 1$
+\EndFor
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+\end{proof}
+
+\begin{theorem}
+\label{result1}
+The Hypothesis \ref{hypothesis1} is true.
+\end{theorem}
+
+\begin{proof}
+This is a consequence of Theorems \ref{completeness} and \ref{proof}.
+\end{proof}
+
+\subsection{Second Hypothesis}
 
@@
 
+\subsection{Consequences}
+
 \begin{theorem}
-\label{equal-NP}
+If $L \neq NL$ then $P = NP$.
+\end{theorem}
+
+\begin{proof}
+This is a direct consequence of Theorems \ref{neg-implication} and \ref{result1}.
+\end{proof}
+
+\begin{theorem}
 If $L = NL$ then $P = NP$.
@@
 
-\subsection{L versus NL}
-
-A directed acyclic graph $G = (V, E)$ is topologically sorted when for any pair of edges $(a, b)$ and $(b, c)$ in $G$, then the edge $(a, b)$ is listed before $(b, c)$ \cite{HM81}.
-
-We show a previous known $\textit{NL--complete}$ problem:
-
-\begin{definition}
-$\textbf{TAGAP}$
-
-INSTANCE: Given a directed acyclic graph $G = (V, E)$ that is topologically sorted and two nodes $s, t \in V$.
-
-QUESTION: Is there a path from $s$ to $t$?
-
-REMARKS: $TAGAP \in \textit{NL--complete}$ \cite{HM81}.
-\end{definition}
-
-\begin{definition}
-An instance $\phi$ of $\textit{XOR 2SAT}$ is topologically sorted when for any pair of clauses $(a, b)$ and $(b, c)$ in $\phi$, then the clause $(a, b)$ is listed before $(b, c)$.
-\end{definition}
-
-\begin{definition}
-$\textbf{TAGAP 2SAT}$
-
-INSTANCE: Given an instance $\phi$ of $\textit{XOR 2SAT}$ that is topologically sorted.
-
-QUESTION: Is there a truth assignment, such that each clause of one literal is satisfied and each clause of two literals has not a true and false evaluated literals at the same time?
-\end{definition}
-
-\begin{theorem}
-$\textit{TAGAP 2SAT} \in L$.
-\end{theorem}
-
-\begin{proof}
-We can check whether an instance $\phi$ of $\textit{XOR 2SAT}$ is topologically sorted in logarithmic space.
-Certainly, for each clause $(a, b)$ we can verify in logarithmic space whether there is not another clause $(b, c)$ that is listed before of $(a, b)$.
-In addition, given an instance $\phi$ of $\textit{XOR 2SAT}$ with $m$ clauses, for each clause of two literals $c_{i} = (x \oplus y)$ in the input tape, we create a new clause $d_{i} = (x \oplus \rightharpoondown y)$ into the output tape, where $x$ and $y$ are literals.
-Moreover, for each clause of one literal $c_{i} = (x)$ in the input tape, we create the same clause $d_{i} = (x)$ into the output tape, where $x$ is a literal.
-Hence, we can create a new instance $\psi$ of $\textit{XOR 2SAT}$ as the conjunction of the $d_{i}$ clauses for every clause $c_{i}$ in $\phi$, such that $\psi = d_{1} \wedge \ldots \wedge d_{m}$.
-Finally, we obtain that:
-\[\phi \in \textit{TAGAP 2SAT} \textit{ if and only if } \psi \in \textit{XOR 2SAT}.\]
-Consequently, we prove $\textit{TAGAP 2SAT} \leq_{l} \textit{XOR 2SAT}$ where we already know the language $\textit{XOR 2SAT} \in L$ \cite{AR00}, \cite{RM08}.
-Since $L$ is closed under logarithmic space reductions, then we obtain that $\textit{TAGAP 2SAT} \in L$ \cite{Pap03}.
-\end{proof}
-
-\begin{lemma}
-\label{nl-complete}
-We have the complement of $TAGAP$ complies with $coTAGAP \in \textit{NL--complete}$.
-\end{lemma}
-
-\begin{proof}
-This is trivially true since $NL$ is closed under complement \cite{Pap03}.
-\end{proof}
-
-\begin{theorem}
-\label{reduction}
-$coTAGAP \leq_{l} \textit{TAGAP 2SAT}$.
-\end{theorem}
-
-\begin{proof}
-Given a directed acyclic graph $G = (V, E)$ that is topologically sorted and two nodes $s, t \in V$, for each edge $(x, y)$ in the input tape from left to right, we create a new clause $(x \oplus y)$ for an instance $\phi$ of $\textit{XOR 2SAT}$ into the output tape, where $x$ and $y$ are positive literals represented by the positive integers $x$ and $y$ which are two nodes in $G$.
-In addition, before we generate the first clause from the edges, then we create the clause $(\rightharpoondown s)$ into the output tape, and after we generate all the clauses, then we create the clause $(t)$ into the output tape from the IN and OUT nodes of the possible path $s, t \in V$: This is possible because an instance of $\textit{XOR 2SAT}$ have clauses of at most two literals \cite{AR00}.
-We can see the final instance $\phi$ of $\textit{XOR 2SAT}$ into the output tape will be topologically sorted, since we create the clauses through the edges from left to right with the exception of $(\rightharpoondown s)$ that is the first clause and $(t)$ that is the last one in $\phi$.
-Hence, if $\phi$ is an acceptance instance of $\textit{TAGAP 2SAT}$, then there is no a possible path from $s$ to $t$ in $G$, because it is necessary that $s$ and $t$ must be false and true on the clauses $(\rightharpoondown s)$ and $(t)$, respectively.
-Certainly, if there is path from $s$ to $t$, then $s$ and $t$ should be both true or both false in order the instance $\phi$ of $\textit{TAGAP 2SAT}$ could be possible accepted.
-Finally, we obtain that:
-\[G \in coTAGAP \textit{ if and only if } \phi \in \textit{TAGAP 2SAT}.\]
-Consequently, we prove $coTAGAP \leq_{l} \textit{TAGAP 2SAT}$ \cite{Pap03}.
-\end{proof}
-
-\begin{theorem}
-\label{equal-L}
-$L = NL$.
-\end{theorem}
-
-\begin{proof}
-A single language in $\textit{NL--complete}$ that is logarithmic space reduced to another language $L$, it is sufficiently to prove $L = NL$, since $L$ and $NL$ are closed under logarithmic space reduction \cite{Pap03}.
-Therefore, this is direct result from Lemma \ref{nl-complete} and Theorem \ref{reduction}.
-\end{proof}
-
 \begin{theorem}
@@
 \begin{proof}
-This is a direct consequence of Theorems \ref{equal-NP} and \ref{equal-L}. 
+Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $P$ is equal to $NP$.
+\end{proof}
+
+\begin{theorem}
+\label{nl}
+$NL = NP$.
+\end{theorem}
+
+\begin{proof}
+Since the polynomial time reduction in Theorem \ref{completeness} could be easily transformed in a logarithmic space reduction, then the $\textit{NP--complete}$ problem in Theorem \ref{neg-implication}, that would be $MAX\oplus2SAT$, is necessarily in $NL$ and thus all the problems in $NP$ when $L \neq NL$, because of the Cook's Theorem can also be transformed in a logarithmic space reduction \cite{GJ79}.
+Certainly, every $NP$ problem could be logarithmic space reduced to $SAT$ by the Cook's Theorem algorithm and $SAT$ can be indeed logarithmic space reduced to $\textit{NAE 3SAT}$ \cite{GJ79}.
+For the same reason, the $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$, because of the problem $UNSAT$ can be actually logarithmic space reduced to $3UNSAT$ \cite{GJ79}.
+Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $NL$ is equal to $NP$.
+\end{proof}
+
+\begin{theorem}
+$L = NP$.
+\end{theorem}
+
+\begin{proof}
+Under the assumption of $L \subseteq 1NL$, then we would obtain that $1NL = NL$.
+Certainly, the logarithmic space verifier of Theorem \ref{proof} works into one-way when $L \subseteq 1NL$.
+Indeed, the logarithmic space verifier through the certificate generates the output into one-way according to the arguments provided by the proof in Theorem \ref{proof}.
+Moreover, we know that $\textit{XOR 2SAT} \in 1NL$ under the assumption of $L \subseteq 1NL$, since $\textit{XOR 2SAT}$ is in $L$ \cite{AR00}, \cite{RM08}.
+In this way, we obtain that $MAX\oplus2SAT \in 1NL$.
+Since $MAX\oplus2SAT$ is $\textit{NP--complete}$ under logarithmic space reductions and $NL = NP$ due to Theorem \ref{nl}, then we would deduce that $1NL = NL$, because of every problem in $NP$ could be reduced to $MAX\oplus2SAT$ under $1NL$-reductions.
+However, it is a known result that $1NL \neq NL$ \cite{MI92}.
+Consequently, we obtain that $1NL \subset L$ as a consequence of this contradiction.
+Since $1NL \subset L$ implies $L=NL$ \cite{HM81}, then we have the complexity class $L$ is equal to $NP$.
 \end{proof}

### 2020-03-10 doc/manuscript.tex
Possibly, the last commit

--- 2020-02-26 doc/manuscript.tex
@@
 Since that date, all efforts to find a proof for this problem have failed.
-Another major complexity classes are L and NL.
-Whether L = NL is another fundamental question that it is as important as it is unresolved.
-We show if L is equal to NL, then P = NP.
-In addition, we demonstrate that L is equal to NL.
-In this way, we prove the complexity class P is equal to NP.
-Furthermore, we demonstrate the complexity class L is equal to NP.
+The answer P = NP is considered as a very unlikely event.
+However, we prove the complexity class P is equal to NP.
 \end{abstract}
@@
 Indeed, if $P = NP$ then there are stunning practical consequences \cite{Pap03}.
-For that reason, $P = NP$ is considered as a very unlikely event \cite{Pap03}.
 Certainly, $P$ versus $NP$ is one of the greatest open problems in science and a correct solution for this incognita will have a great impact not only in computer science, but for many other fields as well \cite{AS17}.
@@
 \section{Theory and Methods}
-
-\subsection{Preliminaries}
 
@@
 \end{definition}
-
-\subsection{Hypothesis}
 
@@
 
-From the early days of automata and complexity theory,  two  different  models  of  Turing  machines  are  considered, the offline and online machines \cite{KU15}.
-Each model has a read-only input tape and some work tapes \cite{KU15}.
-The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left \cite{KU15}.
-In the terminology of the (generalized) Turing machine models are called two-way and one-way Turing machines, respectively \cite{KU15}.
+\section{Hypothesis}
 
+The two-way Turing machines may move their head on the input tape into two-way (left and right directions) while the one-way Turing machines are not allowed to move the input head on the input tape to the left \cite{KU15}.
 Hartmanis and Mahaney have investigated the classes $1L$ and $1NL$ of languages recognizable by deterministic one-way logarithmic space Turing machine and nondeterministic one-way logarithmic space Turing machine, respectively \cite{HM81}.
@@
 \begin{theorem}
-\label{pos-implication}
-If the Hypothesis \ref{hypothesis2} is true, therefore when $L = NL$, then $P = NP$.
+\label{coNL}
+A language $L_{1}$ is in $coNL$ if and only if $L_{1}$ complies with there is a nondeterministic logarithmic space Turing machine $M_{1}$, such that for every appropriate instance $x$, then all the paths on $M_{1}(x)$ accept when $x \in L_{1}$ or at least one of the paths on $M_{1}(x)$ rejects when $x \notin L_{1}$.
 \end{theorem}
@@
 \begin{proof}
-We can accept the elements of the language $L_{1} \in 1NL$ by a nondeterministic one-way logarithmic space Turing machine $M'$.
-In this way, there is a nondeterministic logarithmic space Turing machine $M''(w, u) = M'(M(w, u))$ which will accept when $w \in L_{2}$ for all the appropriated disqualification $u$, where $u$ is placed on the special read-once tape of $M''$.
-The reason is because we can simulate the output string of $M(w, u)$ within a read-once tape and thus, we can compute in a nondeterministic logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}.
-Certainly, we do not need to reset the computation of $M(w, u)$ for the reading at once of a symbol in the output string of $M(w, u)$ by the nondeterministic one-way logarithmic space Turing machine $M'$.
-Consequently, $M''$ can be converted into a logarithmic space disqualifier for the language $L_{2}$ just assuming that $L = NL$, because of the nondeterministic logarithmic space Turing machine $M''$ could be simulated by a deterministic logarithmic space Turing machine.
-Therefore, $L_{2}$ is in $coNL$ and thus, $L_{2} \in P$ due to $coNL \subseteq P$ \cite{Pap03}.
+The proof is simple, since we can interchange the acceptance and rejection states of $M_{1}$ into a new Turing machine $M_{1}'$, such that $M_{1}'(x) = ``yes"$ when $M_{1}(x) = ``no"$ and $M_{1}'(x) = ``no"$ when $M_{1}(x) = ``yes"$.
+Certainly, the language $L(M_{1}')$ is the complement of $L_{1}$ and it is in $NL$ according to the definition of $NL$ and because of the string $x$ is an appropriate instance \cite{Pap03}.
+\end{proof}
+
+\begin{theorem}
+\label{pos-implication}
+When the Hypothesis \ref{hypothesis2} is true, then $P = NP$.
+\end{theorem}
+
+\begin{proof}
+We can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis2} by a nondeterministic logarithmic space Turing machine $N$ such that $N(w) = y$, since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$ \cite{Pap03}.
+Certainly, we can simulate the reading of one symbol from the string $u$ into the read-once tape just nondeterministically generating the same symbol in the work tapes using a logarithmic space \cite{Pap03}.
+We remove each symbol generated in the work tapes, when we try to generate the next symbol contiguous to the right on the string $u$.
+In this way, the generation will always be in logarithmic space.
+In addition, we can guarantee that the generation of symbols in the work tapes always produces an appropriated string $u$, since we can check this by symbol per symbol from the generated string $u$.
+
+Since we have that $L_{1} \in 1NL$, then we can accept the elements of the language $L_{1}$ by a nondeterministic one-way logarithmic space Turing machine $M'$.
+In this way, there is a nondeterministic logarithmic space Turing machine $M''(w) = M'(N(w))$ which will accept when $w \in L_{2}$ for all the possible paths and will reject when $w \notin L_{2}$ for at least one of the paths.
+
+The reason is because we can simulate the output string of $N(w)$ within a read-once tape and thus, we can compute in a nondeterministic logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}.
+Certainly, we do not need to reset the computation of $N(w)$ for the reading at once of a symbol in the output string of $N(w)$ by the nondeterministic one-way logarithmic space Turing machine $M'$.
+Actually, the logarithmic space reduction is possible, because of $M'$ is in one way.
+Indeed, it is not necessary to reset the computation of $N$ in the composition $M'(N(w))$ on the input $w$, because $M'$ never moves to the left the head on the input tape (that would be the output tape of $N$).
+
+As a consequence of Theorem \ref{coNL}, then $L_{2}$ would be in $coNL$ and thus, $L_{2} \in P$ due to $coNL \subseteq P$ \cite{Pap03}.
 If any single $\textit{coNP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{Pap03}.
-Since $L_{2} \in P$ and $L_{2} \in \textit{coNP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that $L = NL$.
+Since $L_{2} \in P$ and $L_{2} \in \textit{coNP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that the Hypothesis \ref{hypothesis2} is true.
 \end{proof}
@@
 \section{Results}
-
-\subsection{Hypothesis}
 
@@
 In this way, we guarantee the output collection $C$ is an appropriated instance of $\textit{SUM--ZERO}$ just filling with zeroes to the left the elements with bit-length lesser than $|3 \times m|$ where $|\ldots|$ is the bit-length function.
+\end{proof}
 
@@
 \end{algorithm}
-\end{proof}
 
@@
 \begin{proof}
-This is a consequence of Theorems \ref{1nl} and \ref{demonstration}.
-\end{proof}
-
-\begin{theorem}
-\label{equal-NP}
-If $L = NL$ then $P = NP$.
-\end{theorem}
-
-\begin{proof}
-This is a direct consequence of Theorems \ref{pos-implication} and \ref{result2}.
-\end{proof}
-
-\subsection{L versus NL}
-
-A directed graph $G = (V, E)$ is topologically sorted when for any pair of edges $(a, b)$ and $(b, c)$ in $G$, then the edge $(a, b)$ is listed before $(b, c)$ \cite{HM81}.
-
-We show a previous known $\textit{NL--complete}$ problem:
-
-\begin{definition}
-$\textbf{TAGAP}$
-
-INSTANCE: Given a directed graph $G = (V, E)$ that is topologically sorted and two nodes $s, t \in V$.
-
-QUESTION: Is there a path from $s$ to $t$?
-
-REMARKS: $TAGAP \in \textit{NL--complete}$ \cite{HM81}. Certainly, this problem remains in $\textit{NL--complete}$ even if the graph is not acyclic \cite{HM81}. 
-\end{definition}
-
-\begin{definition}
-An instance $\phi$ of $\textit{XOR 2SAT}$ is topologically sorted when for any pair of clauses $(a, b)$ and $(b, c)$ in $\phi$, then the clause $(a, b)$ is listed before $(b, c)$.
-\end{definition}
-
-\begin{definition}
-$\textbf{TAGAP 2SAT}$
-
-INSTANCE: Given an instance $\phi$ of $\textit{XOR 2SAT}$ that is topologically sorted.
-
-QUESTION: Is there a truth assignment, such that each clause of one literal is satisfied and each clause of two literals has not a true and false evaluated literals at the same time?
-\end{definition}
-
-\begin{theorem}
-$\textit{TAGAP 2SAT} \in L$.
-\end{theorem}
-
-\begin{proof}
-We can check whether an instance $\phi$ of $\textit{XOR 2SAT}$ is topologically sorted in logarithmic space.
-Certainly, for each clause $(a, b)$ we can verify in logarithmic space whether there is not another clause $(b, c)$ that is listed before of $(a, b)$.
-In addition, given an instance $\phi$ of $\textit{XOR 2SAT}$ with $m$ clauses, for each clause of two literals $c_{i} = (x \oplus y)$ in the input tape, we create a new clause $d_{i} = (x \oplus \rightharpoondown y)$ into the output tape, where $x$ and $y$ are literals.
-Moreover, for each clause of one literal $c_{i} = (x)$ in the input tape, we create the same clause $d_{i} = (x)$ into the output tape, where $x$ is a literal.
-Hence, we can create a new instance $\psi$ of $\textit{XOR 2SAT}$ as the conjunction of the $d_{i}$ clauses for every clause $c_{i}$ in $\phi$, such that $\psi = d_{1} \wedge \ldots \wedge d_{m}$.
-Finally, we obtain that:
-\[\phi \in \textit{TAGAP 2SAT} \textit{ if and only if } \psi \in \textit{XOR 2SAT}.\]
-Consequently, we prove $\textit{TAGAP 2SAT} \leq_{l} \textit{XOR 2SAT}$ where we already know the language $\textit{XOR 2SAT} \in L$ \cite{AR00}, \cite{RM08}.
-Since $L$ is closed under logarithmic space reductions, then we obtain that $\textit{TAGAP 2SAT} \in L$ \cite{Pap03}.
-\end{proof}
-
-\begin{lemma}
-\label{nl-complete}
-We have the complement of $TAGAP$ complies with $coTAGAP \in \textit{NL--complete}$.
-\end{lemma}
-
-\begin{proof}
-This is trivially true since $NL$ is closed under complement \cite{Pap03}.
-\end{proof}
-
-\begin{theorem}
-\label{reduction}
-$coTAGAP \leq_{l} \textit{TAGAP 2SAT}$.
-\end{theorem}
-
-\begin{proof}
-Given a directed graph $G = (V, E)$ that is topologically sorted and two nodes $s, t \in V$, for each edge $(x, y)$ in the input tape from left to right, we create a new clause $(x \oplus y)$ for an instance $\phi$ of $\textit{XOR 2SAT}$ into the output tape, where $x$ and $y$ are positive literals represented by the positive integers $x$ and $y$ which are two nodes in $G$.
-In addition, before we generate the first clause from the edges, then we create the clause $(\rightharpoondown s)$ into the output tape, and after we generate all the clauses, then we create the clause $(t)$ into the output tape from the IN and OUT nodes of the possible path $s, t \in V$: This is possible because an instance of $\textit{XOR 2SAT}$ have clauses of at most two literals \cite{AR00}.
-We can see the final instance $\phi$ of $\textit{XOR 2SAT}$ into the output tape will be topologically sorted, since we create the clauses through the edges from left to right with the exception of $(\rightharpoondown s)$ that is the first clause and $(t)$ that is the last one in $\phi$.
-Hence, if $\phi$ is an acceptance instance of $\textit{TAGAP 2SAT}$, then there is no a possible path from $s$ to $t$ in $G$, because it is necessary that $s$ and $t$ must be false and true on the clauses $(\rightharpoondown s)$ and $(t)$, respectively.
-Certainly, if there is path from $s$ to $t$, then $s$ and $t$ should be both true or both false in order the instance $\phi$ of $\textit{TAGAP 2SAT}$ could be possible accepted.
-Finally, we obtain that:
-\[G \in coTAGAP \textit{ if and only if } \phi \in \textit{TAGAP 2SAT}.\]
-Consequently, we prove $coTAGAP \leq_{l} \textit{TAGAP 2SAT}$ \cite{Pap03}.
-\end{proof}
-
-\begin{theorem}
-\label{equal-L}
-$L = NL$.
-\end{theorem}
-
-\begin{proof}
-A single language in $\textit{NL--complete}$ that is logarithmic space reduced to another language $L$, it is sufficiently to prove $L = NL$, since $L$ and $NL$ are closed under logarithmic space reduction \cite{Pap03}.
-Therefore, this is direct result from Lemma \ref{nl-complete} and Theorem \ref{reduction}.
+This is a direct consequence of Theorems \ref{1nl} and \ref{demonstration}.
 \end{proof}
@@
 \begin{proof}
-This is a direct consequence of Theorems \ref{equal-NP} and \ref{equal-L}.
-\end{proof}
-
-\begin{theorem}
-$L = NP$.
-\end{theorem}
-
-\begin{proof}
-The $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$, because of every problem in $coNP$ can be actually logarithmic space reduced to $3UNSAT$ \cite{GJ79}.
-Certainly, every $coNP$ problem could be logarithmic space reduced to $UNSAT$ by the Cook's Theorem algorithm and $UNSAT$ can be indeed logarithmic space reduced to $3UNSAT$ \cite{GJ79}.
-Since we have that $L = NL = coNL$ is true, then the complexity class $L$ is equal to $NP$.
+This is a direct consequence of Theorems \ref{pos-implication} and \ref{result2}.
 \end{proof}
@@
 
-There are enormous positive consequences that will follow from rendering tractable many currently mathematically intractable problems.
+There are positive consequences that will follow from rendering tractable many currently mathematically intractable problems.
 For instance, many problems in operations research are $\textit{NP--complete}$, such as some types of integer programming and the traveling salesman problem \cite{GJ79}.
